### 2016-07-18 paper4.tex
20160718

\documentclass[Journal,letterpaper]{ascelike-new}
%% Please choose the appropriate document class option:
% "Journal" produces double-spaced manuscripts for ASCE journals.
% "NewProceedings" produces single-spaced manuscripts for ASCE conference proceedings.
% "Proceedings" produces older-style single-spaced manuscripts for ASCE conference proceedings.
%
%% For more details and options, please see the notes in the ascelike-new.cls file.

% Some useful packages...
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{graphicx}
%\usepackage[figurename=Fig.,labelfont=bf,labelsep=period]{caption}
\usepackage{subcaption}
%\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
%\usepackage{newtxtext,newtxmath}
\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
%

\usepackage{tipa}
\usepackage{amsmath}%math
\usepackage{amsthm}%proof
\usepackage{xcolor}%color
\usepackage{bm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{textcomp}
%\usepackage[colorlinks,linkcolor=black,anchorcolor=black,citecolor=black]{hyperref}
\usepackage{amsfonts,amssymb}
\usepackage{color,soul}
\usepackage{ulem}
\theoremstyle{plain}
\newtheorem{myas}{Assumption}
\newtheorem{mydef}{Definition}
\newtheorem{mylem}{Lemma}
\newtheorem{mythm}{Theorem}
\newtheorem{mypro}{Properties}
%\theoremstyle{remark}
\theoremstyle{remark}
\newtheorem{myrem}{Remark}

% Please add the first author's last name here for the footer:
\NameTag{AuthorOneLastName, \today}
% Note that this is not displayed if the NoPageNumbers option is used
% in the documentclass declaration.
%
\begin{document}

% You will need to make the title all-caps
\title{Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System}

\author[1]{Zhiqiang Ma}
\author[1]{Guanghui Sun}
\author[1]{Zhengkai Li}

\affil[1]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email. Email: guanghuisun@hit.edu.cn}
%\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}
%\affil[2]{Third affiliation address}

\maketitle

% Please include an abstract:
\begin{abstract}
This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system. The tethered satellite system is modelled based on Lagrangian mechanics theory, and to overcome the limited input of the dynamic model, a new scalable dimensionless transform and strictly bounded terms are designed to guarantee the existence of the ratio between limited input and command signal. The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain, and the stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation to guarantee that the asymptotically stability of the deployment dynamics. The numerical simulations are reported to verify the effectiveness of the proposed control laws.
\end{abstract}

\section{Introduction}
The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique makes it possible to develop various applications for space exploration and scientific research, such as space debris removal~\cite{zhao2014thrust}, space elevator~\cite{kojima2015mission}, satellite de-orbit~\cite{zhong2013dynamics,zhong2013long} and the tethered space robot~\cite{huang2014optimal}. Many international space research institutes have launched some orbital, suborbital and ground experiments in an effort, such as TSS-1R, SEDS, MAST and YES2, to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}. These experimental results make researchers proceed to advance mechanics, kinetic and control studies intensively, to tackle the challenges of requirements from space missions in the future~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line}.\par

Recent scientific researches on deployment of the tethered satellite focus on the stabilization of the dynamics, and have varying merit and outcomes, providing different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approach~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}. Among the deployment stabilization strategies, the hybrid tension and thruster control boosts to the new developments. Iki et al. implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and the thruster was used to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}. Aslanov et al. presented a thruster method driving the space tethered tug, and analyzed the dragging dynamics~\cite{aslanov2013dynamics}. Huang et al. investigated the attitude and deploying dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}. Jung et al. adopted thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}. Liu et al. equipped the thruster system, which consisted of four pairs of thrusters, in the subsatellite dedicating for regulation of the attitude and deployment dynamics~\cite{liu2014attitude}. Zakrzhevskii divided the deployment process into two stages, the first stage of which ejected the tether with thruster to position the tether at desired beginning point of the second stage, and the second stage continued to adjust the tether to the stable vertical configuration by using tension generated by friction~\cite{zakrzhevskii2016method}. Mantellato et al. reported the thrust-aided librating deployment of tape tethers, and the force acting on the tape tether included the tension and thruster force~\cite{mantellato2015thrust}. This hybrid strategy has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, thus is broadly utilized in reality compared with other control strategies.\par

There also exist some obstacles in the design of the hybrid control. Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical condition, i.e., the tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the space tether. Also, the thruster can not provide infinite force~\cite{martinez1998spacecraft}. Hence the tension and thruster force for the deployment/retrevial are both limited, and in the view of control theory, the phenomena usually causes the input limitation of a dynamic system. Substituting limited inputs into unmodified conventional control scheme designed for unlimited input system results in lost of control or poor performance, and theoretically, such kind of implement is unreasonable. Hence to cope with input limitation in the tethered satellite system (TSS), some scientific researchers spent much effort on restricting input, providing many solutions on satellite arrangements and deployments. Huang et al. addressed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect of constrained input by using specific auxiliary design systems~\cite{huang2015adaptive}. Wen et al. took into account the positive bounded tension constraint by designing the feedback control with special saturation technique~\cite{wen2016constrained}, and Wen also proposed some remarkable achievements using optimal control for deployment~\cite{wen2008optimal}. Liu et al. reported the variable structure scheme for the deployment with thruster control, where the thruster is used to guarantee the positive tension during the mission~\cite{yingying2012variable}. In summary, existed studies deal with the major issue about the deployment with restricted tension and thruster force in two ways, accordingly, the suitable physical compensation and the elaborate design of limited input. In aspect of designing elaborate limited inputs, as Wen et al. explained, the limited terms, including the tension and the state of the deployment, can be viewed as the solution of a nonlinear optimal control \cite{wen2015tension}. Hu reported an adaptive sliding mode control with saturated input by using reduced sliding dynamic design approach \cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits. In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the tethered satellite system is studied. For coping with the input saturation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function. Based on the feature of the saturated command, an adaptive rate is introduced into the controller design to remove the effect of the input limitation theoretically. In order to improve the performance of the sliding phase, the terminal attractor is incorporated into the design of the ideal sliding surface. Numerical simulations are performed to illustrate that the stabilization of the deployment is accomplished by the controller designed in spite of the input limitation.\par
The paper is organized as follows: Section \ref{sec:2} introduces the standard mathematical model of the deployment of the TSS. Section \ref{sec:3} designs the adaptive saturated sliding mode control laws with input limitation for the dynamics, and these simulations are exhibited in Section \ref{sec:4} to reveal the effectiveness and efficiency. The conclusion is given in Section \ref{sec:5}.
\section{Mathematical model}\label{sec:2}
Figure \ref{fig:1} shows all the elements of the TSS via the geometric representation. In the figure, it is apparent that $OXYZ$ denotes the inertial frame, the origin $O$ of which is arranged at the the earth's core. $OX$ and $OY$ are mutually perpendicular axes on the equatorial plane with $OX$ pointing to the spring equinox, and $OZ$ is perpendicular to the equatorial plane, bundling the axis of the earth upwards. The frame of $OXYZ$ fulfills the right-hand rule, hence the direction of axis $OY$ is identified. Orbital coordinate system is denoted as $O_2xyz$ with the origin $O_2$ located at the center of the TSS. $O_2x$ points to the orbital direction, meanwhile $O_2z$ is along the direction downwards towards to the core of the earth, generating the axis $O_2y$ by utilizing the right-hand rule. $\theta$ and $\phi$ stand for the in-plane and out-of-plane angle, respectively. Another coordinate system $O_2x'y'z'$ represents the TSS frame with $O_2z'$ pointing to the subsatellite along the tether, and $O_2x'y'z'$ can be obtained by rotating $O_2xyz$ around the fixed origin $O_2$. $\bm R_0$ denotes the position vector between $O_2$ and $O$.\par
In the analysis of the deployment of the TSS, there is a primary assumption that the movement of entire system is approximating to a ``rolling ball'' behavior with three DOFs modelled, and reasonably one can invoke the spherical coordinates to describe the behavior. During space mission, the mass of the tether is much smaller than that of the mother satellite, and hence it is always ignored sufficiently. Some other assumptions are obvious throughout the analysis, and listed in the following. A satellite is able to be regard as a particle under the condition that the length of the tether is large enough, and due to the tiny ratio of the mass between the satellites, the deployment of the subsatellite will not effect the motion of the mother satellite and keep the nominal orbit during the whole mission. The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
Before giving out the model, some preliminary symbols are exhibited. $R_0$ is a positive scaler meaning the radius of orbit without disturbance, and $\Omega = \sqrt{\mu_e/R_0^3}$ is the orbital angular velocity where $\mu_e$ is the coefficient of the Earth gravity field.\par
Based on the assumption above, the kinetic energy and the potential energy of the deployment dynamics can be described as:
\begin{figure}[http]
\centering
\includegraphics[width=0.7\textwidth]{paper4_fig1.eps}
\caption{TSS geometric representation}
\label{fig:1}
\end{figure}
\begin{align}
T_t
&= \frac{1}{2}\sum\limits_{s=1}^2 m_s\bm{R_s'\cdot R_s'}\notag\\
&= \frac{1}{2}m\bm{R_0'\cdot R_0'}+\frac{1}{2}\sum\limits_{s=1}^2 m_s\bm{r_s'\cdot r_s'}\notag\\
&= \frac{1}{2}m\Omega^2R_0^2+\frac{1}{2}\bar{m}l^2\begin{bmatrix}\phi'+(\theta'+\Omega)^2\end{bmatrix}+\frac{1}{2}\bar{m}l'^2\label{eq:Tt1}\\
V_g
&= -\mu_e\sum\limits_{s=1}^2\frac{m_s}{\vert \bm{R_0+r_s}\vert}\notag\\
&= -m\Omega^2R_0^2+\frac{\bar{m}\Omega^2l^2}{2}(1-3\cos{^2\theta}\cos^2\phi),\label{eq:Vg}
\end{align}
where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively. $(\cdot)'$ represents the differentiation with respective to time, and $l$ means the tether length connecting the satellites. $\theta$ and $\phi$ depict the rolling and pitching dynamics of the TSS. For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
Combining Eq.~(\ref{eq:Vg}) and Eq.~(\ref{eq:Tt1}) give rise to the Lagrange function:
\begin{align}
\begin{split}
L=&T_t-V_g\\
=&\frac{\bar ml^2}{2}\begin{pmatrix}\phi'^{2}+\cos^2\phi(\theta'+\Omega)^2\end{pmatrix}+\frac{\bar ml'^2}{2}\\
&-\frac{\bar m\Omega^2l^2}{2}\begin{pmatrix}1-3\cos^2\theta\cos^2\phi\end{pmatrix}+\frac{3m\Omega^2R_0^2}{2},
\end{split}
\end{align}
and utilize Lagrangian mechanics theory to obtain the following expression
\begin{align}
\begin{split}
&\bar m l''-\bar m l\begin{bmatrix}\phi'^2+(\theta'+\Omega)^2\cos^2\phi\end{bmatrix}+\bar m l\Omega^2(1-3\cos^2\phi\cos^2\theta)=-\tau_t\\
&\bar m l^2\cos^2\phi\theta''+2\bar m (\theta'+\Omega)l^2\cos^2\phi(l'/l-\phi'\tan\phi)+3\bar m \Omega^2l^2\sin\theta\cos\theta\cos^2\phi=\tau_\theta\\
&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\begin{bmatrix}(\theta'+\Omega)^2+3\bar m \Omega\cos^2\theta\end{bmatrix}=\tau_\phi.\label{eq:dynamics 1}
\end{split}
\end{align}
One can construct the dimensionless transformation:
\begin{align}
\begin{split}
&\lambda=l/L\\
&d()/dt=\Omega d()/dv\\
&\hat{\tau}_t=-\tau_t/(\bar{m}\Omega^2L)+\lambda\\
&\hat{\tau}_\theta=\tau_\theta/(\bar{m}\Omega^2L^2)\\
&\hat{\tau}_\phi = \tau_\phi/(\bar{m}\Omega^2L^2)\label{eq:varcon},
\end{split}
\end{align}
such that Eq.~(\ref{eq:dynamics 1}) is able to be converted into dimensionless Euler-Lagrange dynamical equation described as follows:
\begin{align}
H(q)\ddot {q}+C(q,\dot{q})\dot{q}+G(q) = \tau,\label{eq:dynamic model}
\end{align}
where
\begin{align}
\begin{split}
q&= \begin{pmatrix}\lambda&\theta&\phi\end{pmatrix}^T\\
\tau&=\begin{pmatrix}\hat\tau_t&\hat\tau_\theta&\hat\tau_\phi\end{pmatrix}^T\\
H(q) &= \begin{bmatrix}1 &0&0\\0 &\lambda^2\cos^2\phi&0\\0&0&\lambda^2\end{bmatrix}\\
C(q,\dot{q}) &=\begin{bmatrix}0 &-(\lambda\dot \theta+2\lambda)\cos^2\phi&-\lambda\dot\phi\\(2\lambda+\lambda\dot \theta)\cos^2\phi&\lambda\dot \lambda\cos^2\phi-\lambda^2\dot\phi\sin\phi\cos\phi&-(\dot\theta+2)\lambda^2\sin\phi\cos\phi\\ \lambda\dot\phi&\lambda^2(\dot\theta+2)\sin\phi\cos\phi&\lambda\dot \lambda\end{bmatrix}\\
G(q) &=\begin{bmatrix}-\lambda\cos^2\phi+2\lambda+3\lambda\cos ^2\theta\cos^2\phi\\3\lambda^2\cos\theta\sin\theta\cos^2\phi\\\lambda^2+3\lambda^2\cos^2\theta\sin\phi\cos\phi\end{bmatrix}.
\end{split}
\end{align}
Based on the expression above, one can find that $\dot H(q) - 2C(q,\dot{q})$ is skew-symmetric, namely,
\begin{align}
q^T(\dot H(q) - 2C(q,\dot{q}))q = 0.
\end{align}
\begin{myrem}

For the deployment or retrieval mission, the following expression exists,
\begin{align}
0<\lambda_{min}\le\lambda\le \lambda_{max}\label{eq:lambda}.
\end{align}
In reality, once $\lambda = 0$ establishes, the mother satellite and subsatellite collide with each other. Hence the minimum of the dimensionless length $\lambda_{min}$ is introduced to maintain the satellites in reasonably safe formation, and also guarantees the non-singularity of the dimensionless transformation~(\ref{eq:varcon}) theoretically. $\lambda_{max}$ stands for the maximum tether length ratio.\par
Tension in a tether is a positive scalar quantity during the deployment, since zero tension is slack, which is inconsistent with the fundamental assumption that the tether is stiff in the ``rolling ball'' model. $\tau_{tmax}$ denotes the maximum tensile tolerance of the tether, and $\tau_t>\tau_{tmax}$ may leads to the break of tether. Hence, $\tau_{tmin}$ can be a small value to guarantee the stiff tether, and reasonable $\tau_{tmax}$\ prevents fracture of tether.
\end{myrem}
At this point the deployment dynamics with input limitation has been established, and an adaptive saturated sliding mode  control will be presented in the subsequent section.
\section{Dynamic sliding mode control subject to input limitation}\label{sec:3}
Before declaring the controller design, some basic precondition is prepared for proceeding derivation.  The left side of Eq.~(\ref{eq:dynamic model}) is able to be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(q,\dot q,\ddot q)$ consists of known nonlinear functions. $\Theta$ denotes unknown but constant parameters, and particularly it is a constant vector in this dimensionless form. Reconstruct the parametrization $Y\Theta$ in terms of a reference $\dot q_r$:
\begin{align}
 Y_r\Theta\equiv H(q)\ddot q_r+C(q,\dot q)\dot q_r+G(q)\label{eq:dynamic model 1}
\end{align}
where $Y_r = Y_r(q,\dot q,\dot q_r,\ddot q_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $S_r$ is able to be obtained, as follows:
\begin{align}
H(q)\dot S_r+C(q,\dot q)S_r+G(q)=\tau - Y_r\Theta\label{eq:dynamic model 2}
\end{align}
where $S_r$ is defined as
\begin{align}
S_r=\dot q-\dot q_r.\label{eq:Sr1}
\end{align}
For deriving the control scheme, some properties should be given out in advance.
\begin{mypro}
Positive scalars $\Xi_i(i = 0,\ldots,5)$ always exist such that
\begin{align}
\begin{split}
\Vert H(q)\Vert & \ge \zeta_{min}(H(q))>\Xi_0>0\\
\Vert H(q)\Vert & \le \zeta_{max}(H(q))<\Xi_1<\infty\\
\Vert C(q,\dot q)\Vert & \le \Xi_2\Vert\dot q\Vert\\
\Vert G(q)\Vert & \le \Xi_3\\
\Vert \dot q_r\Vert & \le \Xi_4+\alpha\Vert\Delta q\Vert+\beta\Vert\sigma\Vert\\
\Vert \ddot q_r\Vert & \le \Xi_5+\alpha\Vert\Delta \dot q\Vert\\
\end{split}
\end{align}
where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively. Furthermore, one can have $Y_r\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta q,\Delta \dot q,\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi$, in which $\varphi$ is a positive scalar determined according to the system state~\cite{parra2003dynamic}.
\end{mypro}
\subsection{Saturated sliding mode control subject to input limitation}
The process above can frame a conventional dynamic sliding PID control scheme, exactly, a PD controller, which can regulate the dynamics of n-link robotic manipulator if extending the dimension in the derivation above \cite{parra2003dynamic}. However, it is not able to regulate the dynamics of the deployment as desired theoretically, because the input $\tau$ in the PID controller is not confined to the characteristics of the tension. For coping with the issue about the bounded input, we develop the dynamic sliding mode control with the experience of saturated manifold, which is also a popular technique in the control of Lagrangian system.\par
Before giving out main results, some routine lemmas emerge in advance to support the derivation.
\begin{mylem}\label{lemma:1}
Consider a quasi-saturated function as follows:
\begin{align}
Sine(x) =
\begin{cases}
sign(x)&\vert x\vert\ge\pi/2\\
sin(x)&\vert x\vert<\pi/2
\end{cases},
\end{align}
and it's notable that the function above is saturated or bounded and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$. The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-\Delta h,\Delta h]$, and once the function $y=Sine(x)+\Delta h$ settles, one can chose the function $y = x+arcsin(\Delta h)$ such that
\begin{align}
&\vert Sine(x)+\Delta h\vert\le\vert x+arcsin(\Delta h)\vert\\
&sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)), \forall x, \vert\Delta h\vert<1.
\end{align}
in which, the characteristics of the signum above can be obtained by check if the sign of $y=(x_1+x_2)(Sine(x_1)+Sine(x_2))$ is alwasys nonnegative.
\end{mylem}
\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{paper4_fig2.eps}
\caption{$y =Sine(x)$ and $y=Sine(x)+\Delta h$}
\label{fig:2}
\end{figure}
\begin{mylem}\label{lemma:2}
Consider a limited function owning the subsequent property:
\begin{align}
g(y) &= R(y)y\in[y_{min},y_{max}]\\
R(y)&=\begin{cases}
y_{max}/y&y>y_{max}\\
1&y_{min}\le y\le y_{max}\\
y_{min}/y&y<y_{min},
\end{cases}
\end{align}
where $y_{min}$ and $y_{max}$ stand for the minimum and maximum values of $g(y)$, respectively, and $y_{min}<0<y_{max}$. If $y$ is bounded, $^by_{min}\le y\le{^by_{max}}$, hence
\begin{align}
0<\min\{y_{min}/{^by_{min}},y_{max}/{^by_{max}}\}\le R(y)\le 1.
\end{align}
\end{mylem}
\begin{myrem}
As we know, compared with the tension limited in deployment mission, the generalized in-plane and out-of-plane forces are saturated but not regular, hence for avoiding confusion, we specify the following expression
\begin{align}
g(\tau) &= \begin{pmatrix}g(\hat\tau_t)\\g(\hat\tau_\theta)\end{pmatrix}\\
R(\tau) &= \begin{bmatrix}R(\hat\tau_t)&0\\0&R(\hat\tau_\theta)\end{bmatrix}.
\end{align}
and in order to design the saturated sliding mode  control for the dynamics of the deployment, the $Sine$ function for vectors is specified as:
\begin{align}
Sine(\Delta q)=\begin{pmatrix}Sine(\Delta \lambda)\\Sine(\Delta\theta)\end{pmatrix}.
\end{align}
\end{myrem}
The lemmas above introduce some properties about saturated functions, with which the dynamic sliding mode control subject to input limitation for Lagrangian system~(\ref{eq:dynamic model}) can be designed by using the subsequent theorem.
\begin{mythm}\label{thm:1}(Saturated sliding mode control)
Considering a nominal Lagrangian system~(\ref{eq:dynamic model}) expressing the dynamics of the deployment of the TSS, one can construct a saturated sliding mode control subject to input limitation, as follows:
\begin{align}
\tau = -g(\delta\varphi F(t) K_dsign(S_{r1})),\label{eq:slider control}
\end{align}
where
\begin{align}
\begin{split}
S_{r1} &= S_{q1}+\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\\
S_{q1} &= Sine(\Delta \dot q+\alpha\Delta q),
\end{split}
\end{align}
in which, $F(0)>0$, and the derivative of $F(t)$ has the characteristics:
\begin{align}
\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1K_de^{-2K_1^{-1}F^{-1}(t)}sign(S_{r2})
\end{align}
where $K_1\in R^{2\times 2}$ is a positive define diagonal matrix, which will be given out later, and if $K\in R^{2\times 2}$, define
\begin{align}
e^K=
\begin{bmatrix}
e^{K_{11}}&e^{K_{12}}\\
e^{K_{21}}&e^{K_{22}}
\end{bmatrix}.
\end{align}
$\gamma$ is a positive scalar, such that the deployment dynamics can be regulated as desired.
\end{mythm}
\begin{proof}
Consider dynamic coordinates change $S_{r2}$ with the regular error variable but not the $Sine$ form:
\begin{align}
\begin{split}
S_{r2} &= S_{q2}+arcsin(\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma)\\
S_{q2} &= \Delta \dot q+\alpha \Delta q,
\end{split}
\end{align}
It is obvious that $S_{q_1}$ is bounded, or exactly saturated, hence $S_{r_1}$ is also bounded if the dynamics can be controlled as desired. In addition, one can select a suitable positive scalar $\gamma$ such that $\gamma\int^t_{t_0}S_{q1}(\varsigma)^\varpi d\varsigma\in[-1,1]$.\par
According to Lemma~\ref{lemma:1}, it is apparent that $S_{r2}$ and $S_{r1}$ have the subsequent relation:
\begin{align}
&S_{r2}^T sign(S_{r2}) \ge  S_{r1}^T sign(S_{r1})\\
&sign(S_{r2})=sign(S_{r1}),
\end{align}
where
\begin{align}
sign(x) = \begin{pmatrix}sign(x_1),sign(x_2),\cdots,sign(x_n)\end{pmatrix}^T,
\end{align}
for a vector $x$. Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinates change $S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $S_{r2}$ holds results in the following expression:
\begin{align}
H(q)\dot S_{r2} = -g(\delta\varphi F(t) K_dsign(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.
\end{align}
Select the Lyapunov function candidate
\begin{align}
V=\frac{1}{2}S_{r2}^TH(q)S_{r2}+\frac{1}{2}v^2,
\end{align}
where $v=F(t)e^{K_1^{-1}F^{-1}(t)}$ and $\frac{1}{2}v^2$ is an auxiliary Lyapunov function with adaptive terms. Differentiating the Lyapunov function above
\begin{align}
\begin{split}
\dot V &= S_{r2}^TH(q)\dot S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}+v\dot v\\
&= -S_{r2}^Tg(\delta\varphi F(t) K_dsign(S_{r1}))-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
&= -S_{r2}^Tg(\delta\varphi F(t) K_dsign(S_{r1}))-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
&= -S_{r2}^Tg(\delta\varphi F(t) K_dsign(S_{r1}))-S_{r2}^TY_{r2}\Theta+v\dot v\\
&= -S_{r2}^TR(\delta\varphi F(t) K_dsign(S_{r1}))\delta\varphi F(t) K_dsign(S_{r1})-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}
\end{split}
\end{align}
Since the command $ -\delta\varphi F(t) K_dS_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$ and $c_2$ such that $0<c_1\le R(\hat\tau_t)<1$ and $0<c_2\le R(\hat\tau_\theta)<1$, and obtain a diagonal matrix as follows:
\begin{align}
K_1 = \begin{bmatrix}c_1&0\\0&c_2\end{bmatrix}.\label{eq:saturated ratio}
\end{align}
$v\dot v$ is able to be derived as follows:
\begin{align}
v\dot v =\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})sign(S_{r2}),
\end{align}
utilizing $sign(S_{r1})=sign(S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:
\begin{align}
\begin{split}\label{eq:V1_2}
\dot V&\le -S_{r2}^T\delta\varphi  K_1K_dF(t)sign(S_{r2})+S_{r2}^T\varphi sign(S_{r2})+\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})sign(S_{r2})\\
&\le \varphi S_{r2}^Tsign(S_{r2})-\varphi\delta S_{r2}^T K_dsign(S_{r2})
\end{split}
\end{align}
owing to the boundedness of the expression above, a large enough $\delta$ can be selected such that $\dot V \le 0$. According to the description of Barbalat’s lemmas, it implies that $S_{r2}$ asymptotically converges to zero with the set of suitable designer parameters.\par
Utilizing $S_{r2}=0$ leads to the equation
\begin{align}
S_{q2}=-arcsin(\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma),\label{eq:eqSq2}
\end{align}
and select a Lyapunov function candidate
\begin{align}
V_1 = \frac{1}{2}S_{q2}^TS_{q_2},
\end{align}
the derivative of which gives rise to
\begin{align}
\begin{split}
\dot V_1 &= S_{q2}^T\dot S_{q_2}\\
&=-\frac{\gamma S_{q2}^TS_{q1}}{\sqrt{1-\Vert\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert^2}}\\
&\le -\frac{\gamma \Vert S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert^2}}\le 0,
\end{split}
\end{align}
if and only if $S_{q1} = 0$, accordingly, $S_{q2} = 0$, one has $\dot V_1=0$. Hence the asymptotically stability of Eq.~(\ref{eq:eqSq2}) has been proved, and therefore $S_{q2}\rightarrow 0$ as $t\rightarrow \infty$ produces
\begin{align}
\Delta \dot q=-\alpha \Delta q.
\end{align}
Select the Lyapunov function candidate $V_2=\frac{1}{2}\Delta q^2$, the derivative of which follows
\begin{align}
\begin{split}
\dot V_2 &= \Delta q\Delta \dot q\\
&=-\alpha (\Delta q)^2\le 0,
\end{split}
\end{align}
if and only if $\Delta q = 0$, namely, $\Delta \dot q = 0$, one has $\dot V_2=0$. Hence asymptotically convergence of $\Delta q$ has been explained, namely, $\Delta q\rightarrow 0$ as $t\rightarrow \infty$. To conclude, the error state $\Delta q$ of the system~(\ref{eq:dynamics 1}) asymptotically converges to the origin with the limited input~(\ref{eq:slider control}). This completes the proof.
\end{proof}
\subsection{Quasi-saturated terminal sliding mode control subject to input limitation}
The design methodology of the saturated sliding mode control has been exhibited in last subsection, and the entire strict proof ensures that the dynamics of the deployment of the tethered satellite can be regulated with the limited tension control. Essentially, the method mentioned above is able to perform a limited sliding mode controller, since the order of the integrated error is one. If the order of the integrated error varies to become a fraction, the value of which is less than one, one establishes the terminal attractor like
\begin{align}
\dot Z = Z^{p/q},
\end{align}
where $0<p/q<1$ and $p$ and $q$ are both positive odd, and a shrewd formula
\begin{align}
\dot Z = \vert Z\vert^{\hat\alpha} sign(Z),
\end{align}
where $0<\hat \alpha<1$, performs the same behavior. Inducting the terminal attractor into the saturated sliding mode control yields a saturated slider-like scheme, and for adopting to the system subject to input limitation, an assumption is given firstly.
\begin{myas}\label{as:1}
For Eq.~(\ref{eq:dynamic model}), the length rate is thought to be bounded during the deployment, namely, $0<\epsilon\le\dot \lambda<\infty$, such that $\Delta \dot \lambda$ is bounded, either.
\end{myas}
\begin{mythm}\label{thm:2}(Quasi-saturated terminal sliding mode control)
Considering the dynamics of the deployment as described in Eq.~(\ref{eq:dynamic model}) with limited tension control, the quasi-saturated terminal sliding mode control input can be designed as follow:
\begin{align}
\tau = -g(\delta\varphi F(t) K_{d1}sign(S_{r3}))
\end{align}
where
\begin{align}
S_{r3} &= S_{q3}+\gamma\int^t_{t_0}\Vert S_{q3}(\varsigma)\Vert^{\hat\alpha}  sign(S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
S_{q3} &= \Delta \dot q+\alpha Sine(\xi\Delta q),\label{eq:Sq3}
\end{align}
where $0<\hat\alpha< 1$, such that the dynamics~(\ref{eq:dynamic model 2}) can be regulated as desired.
\end{mythm}
\begin{proof}
The proof is similar to Theorem~\ref{thm:1}, and omitted here.
\end{proof}
\begin{myrem}
If the designer parameter $\hat\alpha = 1$, the quasi-saturated terminal sliding mode control degenerates into the quasi-saturated sliding mode control. Compared with the saturated sliding mode control, $S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method. This is because the establishment of the equation $\dot S_{q3} = \gamma\Vert S_{q3}\Vert^{\hat\alpha}  sign(S_{q3})$.
\end{myrem}
\begin{myrem}
Assumption~\ref{as:1} guarantees that the input $\tau$ is bounded in Theorem~\ref{thm:2}, accordingly, a tiny positive scalar $c$ is able to be found such that $0<c\le R(\hat\tau_t)<1$ always exists. Admittedly, such kind of assumption is ''skillful'', but meaningful to arbitrary controllable dynamics in reality. It is reasonable to propose the terminal sliding mode control for the dynamics as follows:
\begin{align}
\tau = -g(\delta\varphi F(t) K_{d1}sign(S_{r4})),
\end{align}
where
\begin{align}
\begin{split}
S_{r4} &= S_{q4}+\gamma\int^t_{t_0}S_{q4}(\varsigma) d\varsigma\\
S_{q4} &= Sine(\Delta \dot q+\alpha\xi\Vert\Delta q\Vert^{\hat\alpha}sign(\Delta q)),\label{eq:Sr4}
\end{split}
\end{align}
such that the finite convergence of the system~(\ref{eq:Sr4}) can be ensured by using terminal sliding mode theory.
\end{myrem}
\section{Simulation studies}\label{sec:4}
In this section, the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively, the designer parameters of which are listed in Table \ref{tab:1}.\par
\begin{table}[!hbp]
\caption{Designer parameters}\label{tab:1}
\begin{center}
\begin{tabular}{ccccc}
\hline
 &S-SMC &ST-SMC &QST-SMC \\
\hline
$\delta$    & 1.1   & 1.1   & 1.1  \\
$\varphi$  & $1\times 10^{-3}$ & $1\times 10^{-3}$& $1\times 10^{-3}$ \\
$\gamma$    & 10    & 0.1     & 0.1     \\
$K_d(K_{*})$       & 1     & 1     & 1   \\
$\alpha$    & 0.8     & 0.8     & 1.2   \\
$\hat\alpha$ & *    & 0.6   & *      \\
\hline
\end{tabular}
\end{center}
\end{table}
Besides the designer parameter determined, the simulation initial and desired condition can be described as follows. The circular orbital altitude is selected around 260 $km$ approximately, and the orbital angular velocity is about $1.17\times 10^{-3}$ $rad/s$. At the initial ejection of the subsatellite, the true anomaly is assumed 0 $rad$. Meanwhile, the initial deployment velocity is about 3 $m/s$, and the subsatellite is going to be deployed at 3.5 $km$ vertically. The pitching and rolling dynamics is varying in a small range, and hence, without loss of generality, the numerical initial condition gives rise to: $\theta_0 = 0.1$, $\varphi_0 = 0.1$, $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$. Hence the dimensionless tether length is varying in $[0.02,1]$.\par
During the deployment, the dimensionless thruster forces which manage the in-plane angle and the out-of-plane angle are assumed to be saturated with $\vert\hat\tau_{\theta}\vert\le5 $ and $\vert\hat\tau_{\phi}\vert\le 5$. Also, the dimensionless tension $\hat\tau_t$ is limited, and from Eq.~(\ref{eq:varcon}), one can obtain
\begin{align}
\begin{split}
&0<\tau_{tmin}/(\bar{m}\Omega^2L)\le-\hat\tau_t+\lambda\le\tau_{tmax}/(\bar{m}\Omega^2L)\\
\Leftrightarrow
&\begin{cases}
\max\{-\hat\tau_t+\lambda\}\le\tau_{tmax}/(\bar{m}\Omega^2L)\\
\min\{-\hat\tau_t+\lambda\}\ge\tau_{tmin}/(\bar{m}\Omega^2L)
\end{cases}\\
\Leftrightarrow
&\begin{cases}
-\hat\tau_{tmin}+\lambda_{max}\le\tau_{tmax}/(\bar{m}\Omega^2L)\\
-\hat\tau_{tmax}+\lambda_{min}\ge\tau_{tmin}/(\bar{m}\Omega^2L).
\end{cases}
\end{split}
\end{align}
Hence, the limited dimensionless tension gives rise to
\begin{align}
-\tau_{tmax}/(\bar{m}\Omega^2L)+\lambda_{max}\le\hat\tau_{tmin}\le\hat\tau_t\le\hat\tau_{tmax}\le-\tau_{tmin}/(\bar{m}\Omega^2L)+\lambda_{min}.
\end{align}
Based on the expression above, one can obtain $\bar{m}\Omega^2L\approx 4.79\times 10^{-3}$, and suitable bounded values $\hat\tau_{tmin}$ and $\hat\tau_{tmax}$ can be chosen to make the dimensionless tension $\hat\tau_t$ fall in the region $[-3,0.01]$.\par
At this point, the simulations of the deployment dynamics of the TSS are able to be carried on, and the results are illustrated in Figure~\ref{fig:3} to~\ref{fig:6}. Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that the all the methods finish the deployment in aspect of the tether length. ST-SMC and QST-SMC complete the deployment at about 4 $rad$, and from Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, and hence the curves of the tether length climb more rapidly at the beginning. In contrary, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$. This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to origin more early than $S-SMC$ and $QST-SMC$.\par
The in-plane and out-of-plane angles reflect the swinging dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}. For ST-SMC, the in-plane dynamics is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time, and hence the coalition of the length and the swinging dynamics implies that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC. S-SMC makes the tether swing to desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) is exhibited in Figure~\ref{fig:6}, in which it is obvious that the limited situations occur frequently. Thanks to the scalable dimensionless transform determined conservatively, the tension exerted on the tether falls in the reasonable region.
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{paper4_fig3.eps}
\caption{Length dynamics of the deployment}
\label{fig:3}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{paper4_fig4.eps}
\caption{Length rate dynamics of the deployment}
\label{fig:4}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{paper4_fig5.eps}
\caption{Angle dynamics of the deployment}
\label{fig:5}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{paper4_fig6.eps}
\caption{Tension}
\label{fig:6}
\end{figure}
\section{Conclusion}\label{sec:5}
In this paper, the error dynamics of the deployment of the TSS provides the adaptive sliding mode control with a simplified solution for the reaching phase, which ignores the nonlinear nature of the model, and the new dimensionless transformation subject to the limited input guarantees the effectiveness of the auxiliary Lyapunov function with adaptive terms. The simulation results show that the proposed methods adjust the length of the tether and the swinging dynamics as desired, although there exists the input limitation during the deployment. According to the results mentioned above, combining error dynamics design approach, adaptive approach and nonlinear sliding mode surface design technology may provide a further insight into regulation of the dynamics of the deployment of the tethered satellite system.
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503101).
%
% Here's the list of references:
%
% \label{section:references}
%\bibliography{ascexmpl-new}
\bibliography{paper4_ref}
%

\end{document}

### 2016-07-18 paper4.tex
20160718

@@
 
-\author[1]{Zhiqiang Ma}
+\author[2]{Zhiqiang Ma}
 \author[1]{Guanghui Sun}
-\author[1]{Zhengkai Li}
+\author[2]{Zhengkai Li}
 
 \affil[1]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email. Email: guanghuisun@hit.edu.cn}
+\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email.}
 %\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}
@@
 \section{Simulation studies}\label{sec:4}
-In this section, the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively, the designer parameters of which are listed in Table \ref{tab:1}.\par
-\begin{table}[!hbp]
-\caption{Designer parameters}\label{tab:1}
-\begin{center}
-\begin{tabular}{ccccc}
-\hline
- &S-SMC &ST-SMC &QST-SMC \\
-\hline
-$\delta$    & 1.1   & 1.1   & 1.1  \\
-$\varphi$  & $1\times 10^{-3}$ & $1\times 10^{-3}$& $1\times 10^{-3}$ \\
-$\gamma$    & 10    & 0.1     & 0.1     \\
-$K_d(K_{*})$       & 1     & 1     & 1   \\
-$\alpha$    & 0.8     & 0.8     & 1.2   \\
-$\hat\alpha$ & *    & 0.6   & *      \\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
+In this section, the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively.
+The parameters of these controllers can selected as follows: $\delta=1.1$, $\varphi= 1\times 10^{-3}$, $\alpha = 0.8$, $K_d(K_{*})=1$, $\gamma = 0.1$ and $\hat\alpha=0.6$.\par
 Besides the designer parameter determined, the simulation initial and desired condition can be described as follows.

### 2016-08-05 manuscript.tex
201600805

--- 2016-07-18 paper4.tex
@@
-\documentclass[Journal,letterpaper]{ascelike-new}
-%% Please choose the appropriate document class option:
-% "Journal" produces double-spaced manuscripts for ASCE journals.
-% "NewProceedings" produces single-spaced manuscripts for ASCE conference proceedings.
-% "Proceedings" produces older-style single-spaced manuscripts for ASCE conference proceedings.
-%
-%% For more details and options, please see the notes in the ascelike-new.cls file.
-
-% Some useful packages...
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{lmodern}
-\usepackage{graphicx}
-%\usepackage[figurename=Fig.,labelfont=bf,labelsep=period]{caption}
-\usepackage{subcaption}
-%\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{amsbsy}
-%\usepackage{newtxtext,newtxmath}
-\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
-%
-
+%\documentclass[draftclsnofoot,onecolumn]{IEEEtran}
+\documentclass[3p]{elsarticle}
 \usepackage{tipa}
@@
 \usepackage{textcomp}
-%\usepackage[colorlinks,linkcolor=black,anchorcolor=black,citecolor=black]{hyperref}
+\usepackage[colorlinks,linkcolor=black,anchorcolor=black,citecolor=black]{hyperref}
 \usepackage{amsfonts,amssymb}
 \usepackage{color,soul}
-\usepackage{ulem}
 \theoremstyle{plain}
@@
 \newtheorem{myrem}{Remark}
+\begin{document}
+\begin{frontmatter}
+\title{Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System}
+\author{Zhiqiang Ma}
+\author{Guanghui Sun\corref{cor1}}
+{\author{Zhengkai Li\corref{cor2}}}
+\ead{guanghuisun@hit.edu.cn}
+\cortext[cor1]{Corresponding author}
+\address{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}
 
-% Please add the first author's last name here for the footer:
-\NameTag{AuthorOneLastName, \today}
-% Note that this is not displayed if the NoPageNumbers option is used
-% in the documentclass declaration.
-%
-\begin{document}
-
-% You will need to make the title all-caps
-\title{Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System}
-
-\author[2]{Zhiqiang Ma}
-\author[1]{Guanghui Sun}
-\author[2]{Zhengkai Li}
-
-\affil[1]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email. Email: guanghuisun@hit.edu.cn}
-\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email.}
-%\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}
-%\affil[2]{Third affiliation address}
-
-\maketitle
-
-% Please include an abstract:
 \begin{abstract}
@@
 \end{abstract}
-
+\begin{keyword}
+Tethered satellite;  Sliding mode control;  Input limitation; Adaptive control
+\end{keyword}
+\end{frontmatter}
 \section{Introduction}
-The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique makes it possible to develop various applications for space exploration and scientific research, such as space debris removal~\cite{zhao2014thrust}, space elevator~\cite{kojima2015mission}, satellite de-orbit~\cite{zhong2013dynamics,zhong2013long} and the tethered space robot~\cite{huang2014optimal}.
+The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique supports various applications for space exploration and scientific research, such as space debris removal~\cite{zhao2014thrust}, space elevator~\cite{kojima2015mission}, satellite de-orbit~\cite{zhong2013dynamics,zhong2013long} and the tethered space robot~\cite{huang2014optimal}.
 Many international space research institutes have launched some orbital, suborbital and ground experiments in an effort, such as TSS-1R, SEDS, MAST and YES2, to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
@@
 owing to the boundedness of the expression above, a large enough $\delta$ can be selected such that $\dot V \le 0$.
-According to the description of Barbalat’s lemmas, it implies that $S_{r2}$ asymptotically converges to zero with the set of suitable designer parameters.\par
+According to the description of Barbalat¡¯s lemmas, it implies that $S_{r2}$ asymptotically converges to zero with the set of suitable designer parameters.\par
 Utilizing $S_{r2}=0$ leads to the equation
@@
 This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503101).
-%
-% Here's the list of references:
-%
-% \label{section:references}
-%\bibliography{ascexmpl-new}
+\section{References}
 \bibliography{paper4_ref}
-%
-
+\bibliographystyle{elsarticle-num}
 \end{document}

### 2016-10-04 manuscript.tex
20161004

@@
 \begin{align}
-H(q)\dot S_r+C(q,\dot q)S_r+G(q)=\tau - Y_r\Theta\label{eq:dynamic model 2}
+H(q)\dot S_r+C(q,\dot q)S_r=\tau - Y_r\Theta\label{eq:dynamic model 2}
 \end{align}
@@
 \end{align}
-For deriving the control scheme, some properties should be given out in advance.
+We define the tracking error as $\Delta q=q-q_d$, in which $q_d$ is the reference trajectory with $q_d(t)\in C^2$. For deriving the control scheme, some properties should be given out in advance.
 \begin{mypro}
@@
 \Vert G(q)\Vert & \le \Xi_3\\
-\Vert \dot q_r\Vert & \le \Xi_4+\alpha\Vert\Delta q\Vert+\beta\Vert\sigma\Vert\\
+\Vert \dot q_r\Vert & \le \Xi_4+\alpha\Vert\Delta q\Vert+\gamma\Vert\sigma\Vert\\
 \Vert \ddot q_r\Vert & \le \Xi_5+\alpha\Vert\Delta \dot q\Vert\\
@@
 \end{align}
-where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively.
+where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively, and $\alpha$ and $\gamma$ are controller parameters which will be discussed later on.
 Furthermore, one can have $Y_r\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta q,\Delta \dot q,\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi$, in which $\varphi$ is a positive scalar determined according to the system state~\cite{parra2003dynamic}.
@@
 \end{align}
-in which, the characteristics of the signum above can be obtained by check if the sign of $y=(x_1+x_2)(Sine(x_1)+Sine(x_2))$ is alwasys nonnegative.
+in which, the characteristics of the signum above can be obtained by \textcolor{red}{checking} if the sign of $y=(x_1+x_2)(Sine(x_1)+Sine(x_2))$ is alwasys nonnegative.
 \end{mylem}
@@
 \begin{myrem}
-As we know, compared with the tension limited in deployment mission, the generalized in-plane and out-of-plane forces are saturated but not regular, hence for avoiding confusion, we specify the following expression
+As we know, \textcolor{red}{the tension, in-plane and out-of-plane thruster force are all limited during deployment mission, and we describe inputs by using the matrix and vector to predigest the following illation.}
 \begin{align}
-g(\tau) &= \begin{pmatrix}g(\hat\tau_t)\\g(\hat\tau_\theta)\end{pmatrix}\\
-R(\tau) &= \begin{bmatrix}R(\hat\tau_t)&0\\0&R(\hat\tau_\theta)\end{bmatrix}.
+\overrightarrow{g}(\tau) &= \left(g(\hat\tau_t),g(\hat\tau_\theta),g(\hat\tau_\phi)\right)^T\\
+R_M(\tau) &= \begin{bmatrix}R(\hat\tau_t)&0&0\\0&R(\hat\tau_\theta)&0\\0&0&R(\hat\tau_\phi)\end{bmatrix}.
 \end{align}
@@
 \begin{align}
-Sine(\Delta q)=\begin{pmatrix}Sine(\Delta \lambda)\\Sine(\Delta\theta)\end{pmatrix}.
+\overrightarrow{Sine}(q)=\begin{pmatrix}Sine(\lambda),Sine(\theta),Sine(\phi)\end{pmatrix}^T.
 \end{align}
@@
 \begin{align}
-\tau = -g(\delta\varphi F(t) K_dsign(S_{r1})),\label{eq:slider control}
+\tau = -\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1})),\label{eq:slider control}
 \end{align}
@@
 S_{r1} &= S_{q1}+\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\\
-S_{q1} &= Sine(\Delta \dot q+\alpha\Delta q),
+S_{q1} &= \overrightarrow{Sine}(\Delta \dot q+\alpha\Delta q),
 \end{split}
@@
 \begin{align}
-\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1K_de^{-2K_1^{-1}F^{-1}(t)}sign(S_{r2})
+\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1K_de^{-2K_1^{-1}F^{-1}(t)}\overrightarrow{sign}(S_{r2})
 \end{align}
@@
 $\gamma$ is a positive scalar, such that the deployment dynamics can be regulated as desired.
+\begin{align}
+\overrightarrow{sign}(x) = \begin{pmatrix}sign(x_1),sign(x_2),\cdots,sign(x_n)\end{pmatrix}^T,
+\end{align}
+for a vector $x=\left(x_1,x_2,,\cdots,x_n\right)^T$.
 \end{mythm}
@@
 It is obvious that $S_{q_1}$ is bounded, or exactly saturated, hence $S_{r_1}$ is also bounded if the dynamics can be controlled as desired.
-In addition, one can select a suitable positive scalar $\gamma$ such that $\gamma\int^t_{t_0}S_{q1}(\varsigma)^\varpi d\varsigma\in[-1,1]$.\par
+In addition, one can select a suitable positive scalar $\gamma$ such that $\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\in[-1,1]$.\par
 According to Lemma~\ref{lemma:1}, it is apparent that $S_{r2}$ and $S_{r1}$ have the subsequent relation:
 \begin{align}
-&S_{r2}^T sign(S_{r2}) \ge  S_{r1}^T sign(S_{r1})\\
-&sign(S_{r2})=sign(S_{r1}),
+&S_{r2}^T \overrightarrow{sign}(S_{r2}) \ge  S_{r1}^T \overrightarrow{sign}(S_{r1})\\
+&\overrightarrow{sign}(S_{r2})=\overrightarrow{sign}(S_{r1}),
 \end{align}
-where
-\begin{align}
-sign(x) = \begin{pmatrix}sign(x_1),sign(x_2),\cdots,sign(x_n)\end{pmatrix}^T,
-\end{align}
-for a vector $x$.
 Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinates change $S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $S_{r2}$ holds results in the following expression:
 \begin{align}
-H(q)\dot S_{r2} = -g(\delta\varphi F(t) K_dsign(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.
+H(q)\dot S_{r2} = -\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.
 \end{align}
@@
 \dot V &= S_{r2}^TH(q)\dot S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}+v\dot v\\
-&= -S_{r2}^Tg(\delta\varphi F(t) K_dsign(S_{r1}))-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -S_{r2}^Tg(\delta\varphi F(t) K_dsign(S_{r1}))-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
-&= -S_{r2}^Tg(\delta\varphi F(t) K_dsign(S_{r1}))-S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -S_{r2}^TR(\delta\varphi F(t) K_dsign(S_{r1}))\delta\varphi F(t) K_dsign(S_{r1})-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}
+&= -S_{r2}^T\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
+&= -S_{r2}^T\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
+&= -S_{r2}^T\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-S_{r2}^TY_{r2}\Theta+v\dot v\\
+&= -S_{r2}^TR_M(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1})-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}
 \end{split}
@@
 \begin{align}
-v\dot v =\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})sign(S_{r2}),
+v\dot v =\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\overrightarrow{sign}(S_{r2}),
 \end{align}
-utilizing $sign(S_{r1})=sign(S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:
+utilizing $\overrightarrow{sign}(S_{r1})=\overrightarrow{sign}(S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:
 \begin{align}
 \begin{split}\label{eq:V1_2}
-\dot V&\le -S_{r2}^T\delta\varphi  K_1K_dF(t)sign(S_{r2})+S_{r2}^T\varphi sign(S_{r2})+\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})sign(S_{r2})\\
-&\le \varphi S_{r2}^Tsign(S_{r2})-\varphi\delta S_{r2}^T K_dsign(S_{r2})
+\dot V&\le -S_{r2}^T\delta\varphi  K_1K_dF(t)\overrightarrow{sign}(S_{r2})+S_{r2}^T\varphi \overrightarrow{sign}(S_{r2})+\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\overrightarrow{sign}(S_{r2})\\
+&\le \varphi S_{r2}^T\overrightarrow{sign}(S_{r2})-\varphi\delta S_{r2}^T K_d\overrightarrow{sign}(S_{r2})
 \end{split}
@@
 \begin{align}
-\dot Z = \vert Z\vert^{\hat\alpha} sign(Z),
+\dot Z = \vert Z\vert^{\hat\alpha} \overrightarrow{sign}(Z),
 \end{align}
@@
 \begin{align}
-\tau = -g(\delta\varphi F(t) K_{d1}sign(S_{r3}))
+\tau = -\overrightarrow{g}(\delta\varphi F(t) K_{d1}\overrightarrow{sign}(S_{r3}))
 \end{align}
@@
 \begin{align}
-S_{r3} &= S_{q3}+\gamma\int^t_{t_0}\Vert S_{q3}(\varsigma)\Vert^{\hat\alpha}  sign(S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
-S_{q3} &= \Delta \dot q+\alpha Sine(\xi\Delta q),\label{eq:Sq3}
+S_{r3} &= S_{q3}+\gamma\int^t_{t_0}\Vert S_{q3}(\varsigma)\Vert^{\hat\alpha}  \overrightarrow{sign}(S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
+S_{q3} &= \Delta \dot q+\alpha \overrightarrow{Sine}(\xi\Delta q),\label{eq:Sq3}
 \end{align}
@@
 \begin{align}
-\tau = -g(\delta\varphi F(t) K_{d1}sign(S_{r4})),
+\tau = -\overrightarrow{g}(\delta\varphi F(t) K_{d1}\overrightarrow{sign}(S_{r4})),
 \end{align}
@@
 S_{r4} &= S_{q4}+\gamma\int^t_{t_0}S_{q4}(\varsigma) d\varsigma\\
-S_{q4} &= Sine(\Delta \dot q+\alpha\xi\Vert\Delta q\Vert^{\hat\alpha}sign(\Delta q)),\label{eq:Sr4}
+S_{q4} &= \overrightarrow{Sine}(\Delta \dot q+\alpha\xi\Vert\Delta q\Vert^{\hat\alpha}\overrightarrow{sign}(\Delta q)),\label{eq:Sr4}
 \end{split}

### 2016-10-18 manuscript.tex
20161018

@@
 \begin{align}
-H(q)\ddot {q}+C(q,\dot{q})\dot{q}+G(q) = \tau,\label{eq:dynamic model}
+H(\bm q)\ddot {\bm q}+C(\bm q,\dot{\bm q})\dot{\bm q}+G(\bm q) = \bm\tau,\label{eq:dynamic model}
 \end{align}
@@
 \begin{split}
-q&= \begin{pmatrix}\lambda&\theta&\phi\end{pmatrix}^T\\
-\tau&=\begin{pmatrix}\hat\tau_t&\hat\tau_\theta&\hat\tau_\phi\end{pmatrix}^T\\
-H(q) &= \begin{bmatrix}1 &0&0\\0 &\lambda^2\cos^2\phi&0\\0&0&\lambda^2\end{bmatrix}\\
-C(q,\dot{q}) &=\begin{bmatrix}0 &-(\lambda\dot \theta+2\lambda)\cos^2\phi&-\lambda\dot\phi\\(2\lambda+\lambda\dot \theta)\cos^2\phi&\lambda\dot \lambda\cos^2\phi-\lambda^2\dot\phi\sin\phi\cos\phi&-(\dot\theta+2)\lambda^2\sin\phi\cos\phi\\ \lambda\dot\phi&\lambda^2(\dot\theta+2)\sin\phi\cos\phi&\lambda\dot \lambda\end{bmatrix}\\
-G(q) &=\begin{bmatrix}-\lambda\cos^2\phi+2\lambda+3\lambda\cos ^2\theta\cos^2\phi\\3\lambda^2\cos\theta\sin\theta\cos^2\phi\\\lambda^2+3\lambda^2\cos^2\theta\sin\phi\cos\phi\end{bmatrix}.
+\bm q&= \begin{pmatrix}\lambda&\theta&\phi\end{pmatrix}^T\\
+\bm \tau&=\begin{pmatrix}\hat\tau_t&\hat\tau_\theta&\hat\tau_\phi\end{pmatrix}^T\\
+H(\bm q) &= \begin{bmatrix}1 &0&0\\0 &\lambda^2\cos^2\phi&0\\0&0&\lambda^2\end{bmatrix}\\
+C(\bm q,\dot{\bm q}) &=\begin{bmatrix}0 &-(\lambda\dot \theta+2\lambda)\cos^2\phi&-\lambda\dot\phi\\(2\lambda+\lambda\dot \theta)\cos^2\phi&\lambda\dot \lambda\cos^2\phi-\lambda^2\dot\phi\sin\phi\cos\phi&-(\dot\theta+2)\lambda^2\sin\phi\cos\phi\\ \lambda\dot\phi&\lambda^2(\dot\theta+2)\sin\phi\cos\phi&\lambda\dot \lambda\end{bmatrix}\\
+G(\bm q) &=\begin{bmatrix}-\lambda\cos^2\phi+2\lambda+3\lambda\cos ^2\theta\cos^2\phi\\3\lambda^2\cos\theta\sin\theta\cos^2\phi\\\lambda^2+3\lambda^2\cos^2\theta\sin\phi\cos\phi\end{bmatrix}.
 \end{split}
 \end{align}
-Based on the expression above, one can find that $\dot H(q) - 2C(q,\dot{q})$ is skew-symmetric, namely,
+Based on the expression above, one can find that $\dot H(\bm q) - 2C(\bm q,\dot{\bm q})$ is skew-symmetric, namely,
 \begin{align}
-q^T(\dot H(q) - 2C(q,\dot{q}))q = 0.
+\bm q^T(\dot H(\bm q) - 2C(\bm q,\dot{\bm q}))\bm q = 0.
 \end{align}
@@
 Before declaring the controller design, some basic precondition is prepared for proceeding derivation.
-The left side of Eq.~(\ref{eq:dynamic model}) is able to be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(q,\dot q,\ddot q)$ consists of known nonlinear functions.
+The left side of Eq.~(\ref{eq:dynamic model}) is able to be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(\bm q,\dot {\bm q},\ddot {\bm q})$ consists of known nonlinear functions.
 $\Theta$ denotes unknown but constant parameters, and particularly it is a constant vector in this dimensionless form.
-Reconstruct the parametrization $Y\Theta$ in terms of a reference $\dot q_r$:
+Reconstruct the parametrization $Y\Theta$ in terms of a reference $\dot{\bm q}_r$:
 \begin{align}
- Y_r\Theta\equiv H(q)\ddot q_r+C(q,\dot q)\dot q_r+G(q)\label{eq:dynamic model 1}
+ Y_r\Theta\equiv H(\bm q)\ddot {\bm q}_r+C(\bm q,\dot {\bm q})\dot {\bm q}_r+G(\bm q)\label{eq:dynamic model 1}
 \end{align}
-where $Y_r = Y_r(q,\dot q,\dot q_r,\ddot q_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $S_r$ is able to be obtained, as follows:
+where $Y_r = Y_r(\bm q,\dot{\bm q},\dot{\bm q}_r,\ddot{\bm q}_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $S_r$ is able to be obtained, as follows:
 \begin{align}
-H(q)\dot S_r+C(q,\dot q)S_r=\tau - Y_r\Theta\label{eq:dynamic model 2}
+H(\bm q)\dot S_r+C(\bm q,\dot{\bm q})S_r=\bm\tau - Y_r\Theta\label{eq:dynamic model 2}
 \end{align}
@@
 \begin{align}
-S_r=\dot q-\dot q_r.\label{eq:Sr1}
+S_r=\dot {\bm q}-\dot {\bm q}_r.\label{eq:Sr1}
 \end{align}
-We define the tracking error as $\Delta q=q-q_d$, in which $q_d$ is the reference trajectory with $q_d(t)\in C^2$. For deriving the control scheme, some properties should be given out in advance.
-\begin{mypro}
-Positive scalars $\Xi_i(i = 0,\ldots,5)$ always exist such that
+We define the tracking error as $\Delta \bm q=\bm q-\bm q_d$, in which $\bm q_d$ is the reference trajectory with $\bm q_d(t)\in C^2$.
+For deriving the control scheme, some properties should be given out in advance.
+\begin{mypro}\cite{parra2003dynamic}
+Positive scalars $\Xi_i(i = 0,\ldots,6)$ always exist such that
 \begin{align}
 \begin{split}
-\Vert H(q)\Vert & \ge \zeta_{min}(H(q))>\Xi_0>0\\
-\Vert H(q)\Vert & \le \zeta_{max}(H(q))<\Xi_1<\infty\\
-\Vert C(q,\dot q)\Vert & \le \Xi_2\Vert\dot q\Vert\\
-\Vert G(q)\Vert & \le \Xi_3\\
-\Vert \dot q_r\Vert & \le \Xi_4+\alpha\Vert\Delta q\Vert+\gamma\Vert\sigma\Vert\\
-\Vert \ddot q_r\Vert & \le \Xi_5+\alpha\Vert\Delta \dot q\Vert\\
+\Vert H(\bm q)\Vert & \ge \zeta_{min}(H(\bm q))>\Xi_0>0\\
+\Vert H(\bm q)\Vert & \le \zeta_{max}(H(\bm q))<\Xi_1<\infty\\
+\Vert C(\bm q,\dot {\bm q})\Vert & \le \Xi_2\Vert\dot {\bm q}\Vert+\Xi_3\\
+\Vert G(\bm q)\Vert & \le \Xi_4\\
+\Vert \dot {\bm q}_r\Vert & \le \Xi_5+\alpha\Vert\Delta \bm q\Vert+\gamma\Vert\sigma\Vert\\
+\Vert \ddot {\bm q}_r\Vert & \le \Xi_6+\alpha\Vert\Delta \dot {\bm q}\Vert\\
 \end{split}
@@
 where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively, and $\alpha$ and $\gamma$ are controller parameters which will be discussed later on.
-Furthermore, one can have $Y_r\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta q,\Delta \dot q,\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi$, in which $\varphi$ is a positive scalar determined according to the system state~\cite{parra2003dynamic}.
+Furthermore, one can have $Y_r\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta \bm q,\Delta \dot {\bm q},\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi$, in which $\varphi$ is a positive scalar determined according to the system state.
 \end{mypro}
@@
 \begin{align}
-\overrightarrow{g}(\tau) &= \left(g(\hat\tau_t),g(\hat\tau_\theta),g(\hat\tau_\phi)\right)^T\\
+\bm{g}(\tau) &= \left(g(\hat\tau_t),g(\hat\tau_\theta),g(\hat\tau_\phi)\right)^T\\
 R_M(\tau) &= \begin{bmatrix}R(\hat\tau_t)&0&0\\0&R(\hat\tau_\theta)&0\\0&0&R(\hat\tau_\phi)\end{bmatrix}.
@@
 \begin{align}
-\overrightarrow{Sine}(q)=\begin{pmatrix}Sine(\lambda),Sine(\theta),Sine(\phi)\end{pmatrix}^T.
+\bm{Sine}(\bm q)=\begin{pmatrix}Sine(\lambda),Sine(\theta),Sine(\phi)\end{pmatrix}^T.
 \end{align}
@@
 \begin{align}
-\tau = -\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1})),\label{eq:slider control}
+\bm\tau = -\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1})),\label{eq:slider control}
 \end{align}
@@
 S_{r1} &= S_{q1}+\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\\
-S_{q1} &= \overrightarrow{Sine}(\Delta \dot q+\alpha\Delta q),
+S_{q1} &= \bm{Sine}(\Delta \dot {\bm q}+\alpha\Delta\bm q),
 \end{split}
@@
 \begin{align}
-\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1K_de^{-2K_1^{-1}F^{-1}(t)}\overrightarrow{sign}(S_{r2})
+\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1K_de^{-2K_1^{-1}F^{-1}(t)}\bm{sign}(S_{r2})
 \end{align}
@@
 \begin{align}
-\overrightarrow{sign}(x) = \begin{pmatrix}sign(x_1),sign(x_2),\cdots,sign(x_n)\end{pmatrix}^T,
+\bm{sign}(\bm x) = \left(sign(x_1),sign(x_2),\cdots,sign(x_n)\right)^T,
 \end{align}
-for a vector $x=\left(x_1,x_2,,\cdots,x_n\right)^T$.
+for a vector $\bm x=\left(x_1,x_2,,\cdots,x_n\right)^T$.
 \end{mythm}
@@
 S_{r2} &= S_{q2}+arcsin(\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma)\\
-S_{q2} &= \Delta \dot q+\alpha \Delta q,
+S_{q2} &= \Delta \dot {\bm q}+\alpha \Delta \bm q,
 \end{split}
@@
 \begin{align}
-&S_{r2}^T \overrightarrow{sign}(S_{r2}) \ge  S_{r1}^T \overrightarrow{sign}(S_{r1})\\
-&\overrightarrow{sign}(S_{r2})=\overrightarrow{sign}(S_{r1}),
+&S_{r2}^T \bm{sign}(S_{r2}) \ge  S_{r1}^T \bm{sign}(S_{r1})\\
+&\bm{sign}(S_{r2})=\bm{sign}(S_{r1}),
 \end{align}
@@
 \begin{align}
-H(q)\dot S_{r2} = -\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.
+H(q)\dot S_{r2} = -\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.
 \end{align}
@@
 \dot V &= S_{r2}^TH(q)\dot S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}+v\dot v\\
-&= -S_{r2}^T\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -S_{r2}^T\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
-&= -S_{r2}^T\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -S_{r2}^TR_M(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1})-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}
+&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
+&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
+&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))-S_{r2}^TY_{r2}\Theta+v\dot v\\
+&= -S_{r2}^TR_M(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))\delta\varphi F(t) K_d\bm{sign}(S_{r1})-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}
 \end{split}
@@
 \begin{align}
-v\dot v =\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\overrightarrow{sign}(S_{r2}),
+v\dot v =\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\bm{sign}(S_{r2}),
 \end{align}
-utilizing $\overrightarrow{sign}(S_{r1})=\overrightarrow{sign}(S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:
+utilizing $\bm{sign}(S_{r1})=\bm{sign}(S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:
 \begin{align}
 \begin{split}\label{eq:V1_2}
-\dot V&\le -S_{r2}^T\delta\varphi  K_1K_dF(t)\overrightarrow{sign}(S_{r2})+S_{r2}^T\varphi \overrightarrow{sign}(S_{r2})+\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\overrightarrow{sign}(S_{r2})\\
-&\le \varphi S_{r2}^T\overrightarrow{sign}(S_{r2})-\varphi\delta S_{r2}^T K_d\overrightarrow{sign}(S_{r2})
+\dot V&\le -S_{r2}^T\delta\varphi  K_1K_dF(t)\bm{sign}(S_{r2})+S_{r2}^T\varphi \bm{sign}(S_{r2})+\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\bm{sign}(S_{r2})\\
+&\le \varphi S_{r2}^T\bm{sign}(S_{r2})-\varphi\delta S_{r2}^T K_d\bm{sign}(S_{r2})
 \end{split}
@@
 \begin{align}
-\Delta \dot q=-\alpha \Delta q.
+\Delta \dot {\bm q}=-\alpha \Delta \bm q.
 \end{align}
-Select the Lyapunov function candidate $V_2=\frac{1}{2}\Delta q^2$, the derivative of which follows
+Select the Lyapunov function candidate $V_2=\frac{1}{2}\Delta \bm q^T\Delta\bm q$, the derivative of which follows
 \begin{align}
 \begin{split}
-\dot V_2 &= \Delta q\Delta \dot q\\
-&=-\alpha (\Delta q)^2\le 0,
+\dot V_2 &= \Delta\bm q^T\Delta \dot{\bm q}\\
+&=-\alpha \Delta \bm q^T\Delta \bm q\le 0,
 \end{split}
 \end{align}
-if and only if $\Delta q = 0$, namely, $\Delta \dot q = 0$, one has $\dot V_2=0$.
-Hence asymptotically convergence of $\Delta q$ has been explained, namely, $\Delta q\rightarrow 0$ as $t\rightarrow \infty$.
-To conclude, the error state $\Delta q$ of the system~(\ref{eq:dynamics 1}) asymptotically converges to the origin with the limited input~(\ref{eq:slider control}).
+if and only if $\Delta \bm q = 0$, namely, $\Delta \dot {\bm q} = 0$, one has $\dot V_2=0$.
+Hence asymptotically convergence of $\Delta \bm q$ has been explained, namely, $\Delta \bm q\rightarrow 0$ as $t\rightarrow \infty$.
+To conclude, the error state $\Delta \bm q$ of the system~(\ref{eq:dynamics 1}) asymptotically converges to the origin with the limited input~(\ref{eq:slider control}).
 This completes the proof.
@@
 \begin{align}
-\dot Z = \vert Z\vert^{\hat\alpha} \overrightarrow{sign}(Z),
+\dot Z = \vert Z\vert^{\hat\alpha} \bm{sign}(Z),
 \end{align}
@@
 \begin{align}
-\tau = -\overrightarrow{g}(\delta\varphi F(t) K_{d1}\overrightarrow{sign}(S_{r3}))
+\tau = -\bm{g}(\delta\varphi F(t) K_{d1}\bm{sign}(S_{r3}))
 \end{align}
@@
 \begin{align}
-S_{r3} &= S_{q3}+\gamma\int^t_{t_0}\Vert S_{q3}(\varsigma)\Vert^{\hat\alpha}  \overrightarrow{sign}(S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
-S_{q3} &= \Delta \dot q+\alpha \overrightarrow{Sine}(\xi\Delta q),\label{eq:Sq3}
+S_{r3} &= S_{q3}+\gamma\int^t_{t_0}\Vert S_{q3}(\varsigma)\Vert^{\hat\alpha}  \bm{sign}(S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
+S_{q3} &= \Delta \dot q+\alpha \bm{Sine}(\xi\Delta q),\label{eq:Sq3}
 \end{align}
@@
 Compared with the saturated sliding mode control, $S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method.
-This is because the establishment of the equation $\dot S_{q3} = \gamma\Vert S_{q3}\Vert^{\hat\alpha}  sign(S_{q3})$.
+This is because the establishment of the equation $\dot S_{q3} = \gamma\Vert S_{q3}\Vert^{\hat\alpha} \bm{ sign}(S_{q3})$.
 \end{myrem}
@@
 \begin{align}
-\tau = -\overrightarrow{g}(\delta\varphi F(t) K_{d1}\overrightarrow{sign}(S_{r4})),
+\tau = -\bm{g}(\delta\varphi F(t) K_{d1}\bm{sign}(S_{r4})),
 \end{align}
@@
 S_{r4} &= S_{q4}+\gamma\int^t_{t_0}S_{q4}(\varsigma) d\varsigma\\
-S_{q4} &= \overrightarrow{Sine}(\Delta \dot q+\alpha\xi\Vert\Delta q\Vert^{\hat\alpha}\overrightarrow{sign}(\Delta q)),\label{eq:Sr4}
+S_{q4} &= \bm{Sine}(\Delta \dot q+\alpha\xi\Vert\Delta q\Vert^{\hat\alpha}\bm{sign}(\Delta q)),\label{eq:Sr4}
 \end{split}

### 2016-10-19 manuscript.tex
20161019

@@
 \begin{split}
-&\bar m l''-\bar m l\begin{bmatrix}\phi'^2+(\theta'+\Omega)^2\cos^2\phi\end{bmatrix}+\bar m l\Omega^2(1-3\cos^2\phi\cos^2\theta)=-\tau_t\\
-&\bar m l^2\cos^2\phi\theta''+2\bar m (\theta'+\Omega)l^2\cos^2\phi(l'/l-\phi'\tan\phi)+3\bar m \Omega^2l^2\sin\theta\cos\theta\cos^2\phi=\tau_\theta\\
-&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\begin{bmatrix}(\theta'+\Omega)^2+3\bar m \Omega\cos^2\theta\end{bmatrix}=\tau_\phi.\label{eq:dynamics 1}
+&\bar m l''-\bar m l\begin{bmatrix}\phi'^2+(\theta'+\Omega)^2\cos^2\phi\end{bmatrix}+\bar m l\Omega^2(1-3\cos^2\phi\cos^2\theta)=-\tau_t+\tau_{td}\\
+&\bar m l^2\cos^2\phi\theta''+2\bar m (\theta'+\Omega)l^2\cos^2\phi(l'/l-\phi'\tan\phi)+3\bar m \Omega^2l^2\sin\theta\cos\theta\cos^2\phi=\tau_\theta+\tau_{\theta d}\\
+&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\begin{bmatrix}(\theta'+\Omega)^2+3\bar m \Omega\cos^2\theta\end{bmatrix}=\tau_\phi+\tau_{\phi d},\label{eq:dynamics 1}
 \end{split}
 \end{align}
-One can construct the dimensionless transformation:
+\textcolor{red}{where $\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster and the out-of-plane thruster, respectively, and $\tau_t d$, $\tau_\theta d$ and $\tau_\phi d$ stand for the bounded external disturbances.
+Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
+\begin{align}
+\begin{split}
+&\lambda=l/L\\
+&d()/dt=\Omega d()/dv\\
+&\hat{\tau}_{t0}=-\tau_t/(\bar{m}\Omega^2L)\\
+&\hat{\tau}_\theta=\tau_\theta/(\bar{m}\Omega^2L^2)\\
+&\hat{\tau}_\phi = \tau_\phi/(\bar{m}\Omega^2L^2)\\
+&\hat{\tau}_{td}=\tau_{td}/(\bar{m}\Omega^2L)\\
+&\hat{\tau}_{\theta d}=\tau_{\theta d}/(\bar{m}\Omega^2L^2)\\
+&\hat{\tau}_{\phi d}= \tau_{\phi d}/(\bar{m}\Omega^2L^2)\label{eq:varcon0}.
+\end{split}
+\end{align}
+From~(\ref{eq:varcon0}), it is easy to find that the boundedness of $\hat{\tau}_{t0}$ is different from $\hat{\tau}_\theta$'s and $\hat{\tau}_\phi$'s, since $\hat{\tau}_{t0}$ just owns the negative boundedness due to positive $\tau_t$.
+However, this issue doesn't conform to conventional hypotheses about input saturation, i.e., for adaptive sliding mode controller design, $\hat{\tau}_{t0}$ doesn't fulfil the requirement of transformation of limited inputs, leading to the nonrigorous stability analysis~\cite{Hu2008552,6060930}.
+To cope better with the missing positive boundedness, we initiatively introduce the dimensionless length $\lambda$ into the dimensionless tension to establish a reasonable positive boundedness, and hence general limited inputs are produced by the novel dimensionless transformations:
 \begin{align}
@@
 &\hat{\tau}_\theta=\tau_\theta/(\bar{m}\Omega^2L^2)\\
-&\hat{\tau}_\phi = \tau_\phi/(\bar{m}\Omega^2L^2)\label{eq:varcon},
+&\hat{\tau}_\phi = \tau_\phi/(\bar{m}\Omega^2L^2)\\
+&\hat{\tau}_{td}=\tau_{td}/(\bar{m}\Omega^2L)\\
+&\hat{\tau}_{\theta d}=\tau_{\theta d}/(\bar{m}\Omega^2L^2)\\
+&\hat{\tau}_{\phi d}= \tau_{\phi d}/(\bar{m}\Omega^2L^2)\label{eq:varcon}.
 \end{split}
 \end{align}
-such that Eq.~(\ref{eq:dynamics 1}) is able to be converted into dimensionless Euler-Lagrange dynamical equation described as follows:
+The obvious benefits of these transformations are that all the inputs own the positive and negative boundedness and hence satisfy the assumption about limited inputs of existing control laws~\cite{Hu2008552,6060930}.
+The obtained inputs also guarantee the rigorous stability analysis of the proposed sliding mode control in this paper.
+Based on the novel dimensionless transformations, Eq.~(\ref{eq:dynamics 1}) can be converted into dimensionless Euler-Lagrange dynamical equation described as follows:}
 \begin{align}
-H(\bm q)\ddot {\bm q}+C(\bm q,\dot{\bm q})\dot{\bm q}+G(\bm q) = \bm\tau,\label{eq:dynamic model}
+H(\bm q)\ddot {\bm q}+C(\bm q,\dot{\bm q})\dot{\bm q}+G(\bm q) = \bm\tau+\bm\tau_d,\label{eq:dynamic model}
 \end{align}
@@
 \bm \tau&=\begin{pmatrix}\hat\tau_t&\hat\tau_\theta&\hat\tau_\phi\end{pmatrix}^T\\
+\bm\tau_d&=\begin{pmatrix}\hat\tau_{td}&\hat\tau_{\theta d}&\hat\tau_{\phi d}\end{pmatrix}^T\\
 H(\bm q) &= \begin{bmatrix}1 &0&0\\0 &\lambda^2\cos^2\phi&0\\0&0&\lambda^2\end{bmatrix}\\
@@
 \begin{align}
-H(\bm q)\dot S_r+C(\bm q,\dot{\bm q})S_r=\bm\tau - Y_r\Theta\label{eq:dynamic model 2}
+H(\bm q)\dot S_r+C(\bm q,\dot{\bm q})S_r=\bm\tau +\bm\tau_d- Y_r\Theta\label{eq:dynamic model 2}
 \end{align}
@@
 \end{align}
-We define the tracking error as $\Delta \bm q=\bm q-\bm q_d$, in which $\bm q_d$ is the reference trajectory with $\bm q_d(t)\in C^2$.
-For deriving the control scheme, some properties should be given out in advance.
-\begin{mypro}\cite{parra2003dynamic}
-Positive scalars $\Xi_i(i = 0,\ldots,6)$ always exist such that
+\textcolor{red}{For the system~(\ref{eq:dynamic model 2}) with ignoring the input limitation, the author in \cite{parra2003dynamic} has designed a nonlinear dynamic sliding PID controller with the zero initial condition:
+\begin{align}\begin{split}
+\dot {\bm q}_r&=\dot{\bm q}_d-\alpha\Delta\bm q-\gamma\bm\sigma\\
+\dot{\bm\sigma}&=\bm{sign}(S)\\
+S&=\Delta\dot{\bm q}+\alpha\Delta\bm q\label{eq:pid controller}
+\end{split}\end{align}
+where
+\begin{align}
+\bm{sign}(\bm x) = \left(sign(x_1),sign(x_2),\cdots,sign(x_n)\right)^T
+\end{align}
+for a vector $\bm x=\left(x_1,x_2,,\cdots,x_n\right)^T$.
+$\alpha$ and $\gamma$ are controller parameters which will be discussed in the controller design.
+Define the tracking error as $\Delta \bm q=\bm q-\bm q_d$, in which $\bm q_d$ is the desired trajectory with $\bm q_d(t)\in C^2$.
+However, the PID controller~(\ref{eq:pid controller}) can not be directly applied to the system~(\ref{eq:dynamic model 2}) with the input limitation, and in the subsequent section, we will utilize the saturated sliding mode technique to modify the PID controller~(\ref{eq:pid controller}) for the system~(\ref{eq:dynamic model 2}).} For deriving the proposed control scheme, some properties should be given out in advance.
+\begin{mypro}\cite{parra2003dynamic}\label{pro:1}
+\textcolor{red}{Positive scalars $\Xi_i(i = 0,\ldots,6)$ always exist such that
 \begin{align}
@@
 \Vert G(\bm q)\Vert & \le \Xi_4\\
-\Vert \dot {\bm q}_r\Vert & \le \Xi_5+\alpha\Vert\Delta \bm q\Vert+\gamma\Vert\sigma\Vert\\
+\Vert \dot {\bm q}_r\Vert & \le \Xi_5+\alpha\Vert\Delta \bm q\Vert+\gamma\Vert\bm\sigma\Vert\\
 \Vert \ddot {\bm q}_r\Vert & \le \Xi_6+\alpha\Vert\Delta \dot {\bm q}\Vert\\
@@
 \end{align}
-where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively, and $\alpha$ and $\gamma$ are controller parameters which will be discussed later on.
-Furthermore, one can have $Y_r\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta \bm q,\Delta \dot {\bm q},\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi$, in which $\varphi$ is a positive scalar determined according to the system state.
+where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively.
+Furthermore, one can have $Y_r\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta \bm q,\Delta \dot {\bm q},\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi_0$, in which $\varphi_0$ is a positive scalar determined according to the system state.}
 \end{mypro}
+
+\begin{myas}
+\textcolor{red}{
+In the low orbit altitude, the external disturbance $\bm\tau_d$ contains gravity gradient torque, aerodynamic interference and solar radiation pressure torque.
+According to existing studies, the values of the solar radiation pressure and the aerodynamic torque are about $1\times10^{-5}$ Nm, and meanwhile the gradient torque is in the range of $1\times10^{-5}$ Nm.
+Typically, the space perturbation can be regarded as the periodic function in this paper, and the period equals the orbital period $5000$ s~\cite{Inamori2015192}.
+Hence, the external disturbance can be described by the following expression
+\begin{align}
+\bm\tau_d=\left(0.05\sin(2\pi t/5000),0.05\sin(2\pi t/5000),0.05\sin(2\pi t/5000)\right)^T.
+\end{align}
+Therefore, the bounded external disturbance satisfy
+\begin{align}
+\Vert\bm\tau_d\Vert\le\varphi_1<\infty,
+\end{align}
+where $\varphi_1$ is a positive scalar.
+}
+\end{myas}
 \subsection{Saturated sliding mode control subject to input limitation}
-The process above can frame a conventional dynamic sliding PID control scheme, exactly, a PD controller, which can regulate the dynamics of n-link robotic manipulator if extending the dimension in the derivation above \cite{parra2003dynamic}.
+The process above can frame a conventional dynamic sliding PID control scheme, which can regulate the dynamics of n-link robotic manipulator if extending the dimension in the derivation above \cite{parra2003dynamic}.
 However, it is not able to regulate the dynamics of the deployment as desired theoretically, because the input $\tau$ in the PID controller is not confined to the characteristics of the tension.
@@
 \begin{align}
-\bm{Sine}(\bm q)=\begin{pmatrix}Sine(\lambda),Sine(\theta),Sine(\phi)\end{pmatrix}^T.
+\bm{Sine}(\bm x)=\begin{pmatrix}Sine(x_1),Sine(x_2),\cdots,Sine(x_n)\end{pmatrix}^T.
 \end{align}
@@
 \end{align}
-where $K_1\in R^{2\times 2}$ is a positive define diagonal matrix, which will be given out later, and if $K\in R^{2\times 2}$, define
+where $K_1\in R^{3\times 3}$ is a positive define diagonal matrix, which will be given out later, and if $K\in R^{3\times 3}$, define
 \begin{align}
@@
 \begin{bmatrix}
-e^{K_{11}}&e^{K_{12}}\\
-e^{K_{21}}&e^{K_{22}}
+e^{K_{11}}&e^{K_{12}}&e^{K_{13}}\\
+e^{K_{21}}&e^{K_{22}}&e^{K_{23}}\\
+e^{K_{31}}&e^{K_{32}}&e^{K_{33}}
 \end{bmatrix}.
 \end{align}
-$\gamma$ is a positive scalar, such that the deployment dynamics can be regulated as desired.
-\begin{align}
-\bm{sign}(\bm x) = \left(sign(x_1),sign(x_2),\cdots,sign(x_n)\right)^T,
-\end{align}
-for a vector $\bm x=\left(x_1,x_2,,\cdots,x_n\right)^T$.
+$\gamma$ is a positive scalar, such that the deployment dynamics can be regulated as desired. $\varphi$ is the boundedness of the lumped uncertainty.
 \end{mythm}
@@
 \end{align}
+Similar to Properties~\ref{pro:1}, one can find a positive scalar $\varphi_2$ such that $\Vert Y_{r2}\Theta\Vert\le\varphi_2$, and moreover the boundedness of the lumped uncertainty $\varphi$ satisfies $\varphi>\varphi_1+\varphi_2$.
+
 Select the Lyapunov function candidate
@@
 \dot V &= S_{r2}^TH(q)\dot S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}+v\dot v\\
-&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
-&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))-S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -S_{r2}^TR_M(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))\delta\varphi F(t) K_d\bm{sign}(S_{r1})-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}
+&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
+&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
+&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+v\dot v\\
+&= -S_{r2}^TR_M(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))\delta\varphi F(t) K_d\bm{sign}(S_{r1})+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}
 \end{split}
@@
 \begin{split}\label{eq:V1_2}
-\dot V&\le -S_{r2}^T\delta\varphi  K_1K_dF(t)\bm{sign}(S_{r2})+S_{r2}^T\varphi \bm{sign}(S_{r2})+\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\bm{sign}(S_{r2})\\
+\dot V&\le -S_{r2}^T\delta\varphi  K_1K_dF(t)\bm{sign}(S_{r2})+S_{r2}^T(\varphi_1+\varphi_2) \bm{sign}(S_{r2})+\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\bm{sign}(S_{r2})\\
 &\le \varphi S_{r2}^T\bm{sign}(S_{r2})-\varphi\delta S_{r2}^T K_d\bm{sign}(S_{r2})
@@
 where $0<\hat\alpha< 1$, such that the dynamics~(\ref{eq:dynamic model 2}) can be regulated as desired.
+$\varphi$ is the boundedness of the lumped uncertainty, and can be obtained by referring to Theorem~\ref{thm:1}.
 \end{mythm}
@@
 such that the finite convergence of the system~(\ref{eq:Sr4}) can be ensured by using terminal sliding mode theory.
+$\varphi$ is the boundedness of the lumped uncertainty, and can be obtained by referring to Theorem~\ref{thm:1}.
 \end{myrem}

### 2016-10-21 manuscript.tex
20161021

@@
 \begin{align}
-&\vert Sine(x)+\Delta h\vert\le\vert x+arcsin(\Delta h)\vert\\
-&sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)), \forall x, \vert\Delta h\vert<1.
+&\vert Sine(x)+\Delta h\vert\le\vert x+arcsin(\Delta h)\vert\label{eq:lem11}\\
+&sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)), \forall x, \vert\Delta h\vert<1\label{eq:lem12}.
 \end{align}
-in which, the characteristics of the signum above can be obtained by \textcolor{red}{checking} if the sign of $y=(x_1+x_2)(Sine(x_1)+Sine(x_2))$ is alwasys nonnegative.
 \end{mylem}
+\begin{proof}
+For relation~(\ref{eq:lem11}), let $y=Sine(x)+\Delta h-x-arcsin(\Delta h)$, and we can get its derivative
+\begin{align}
+\begin{cases}
+y' = -1,&x\ge\pi/2,x\le-\pi/2\\
+y' = \cos x - 1,&\vert x\vert<\pi/2,
+\end{cases}
+\end{align}
+where $y'<0$ means $y$ is a monotone decreasing function. As $x=-arcsin(\Delta h)$, $y=0$, according to the definition of $Sine(x)$, we proceed to get
+$$\left.
+\begin{aligned}
+x\ge-arcsin(\Delta h), y\le0&\Rightarrow 0\le Sine(x)+\Delta h\le x+arcsin(\Delta h)\\
+x<-arcsin(\Delta h), y>0&\Rightarrow 0> Sine(x)+\Delta h>x+arcsin(\Delta h)\end{aligned}\right\}\\\\
+\Rightarrow\vert Sine(x)+\Delta h\vert\le\vert x+arcsin(\Delta h)\vert.
+$$
+For Eq.~(\ref{eq:lem12}), considering the case $Sine(x)+\Delta h>0$, when $\vert x\vert<\pi/2$, $Sine(x)+\Delta h>0$ becomes
+\begin{align}
+sin(x)+\Delta h>0&\Rightarrow x>-arcsin(\Delta h)\\
+&\Rightarrow x+arcsin(\Delta h)>0,
+\end{align}
+since $y=arcsin(x)$ is a monotone increasing function.
+We only need to consider $x\ge\pi/2$ instead of $\vert x\vert\ge\pi/2$ for $x\le-\pi/2$ is meaningless in the case $Sine(x)+\Delta h>0$.
+It is obvious that $x+arcsin(\Delta h)>0$ due to $\vert arcsin(\Delta h)\vert<\pi/2$.
+Therefore, we can get
+\begin{align}
+sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)),Sine(x)+\Delta h>0,
+\end{align}
+and similarly the following equation is reasonable:
+\begin{align}
+sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)),Sine(x)+\Delta h\le0.
+\end{align}
+\end{proof}
 \begin{figure}
@@
 \end{figure}
-\begin{mylem}\label{lemma:2}
+\begin{mylem}\cite{Hu2008552}\label{lemma:2}
 Consider a limited function owning the subsequent property:
@@
 \end{align}
-$\gamma$ is a positive scalar, such that the deployment dynamics can be regulated as desired. $\varphi$ is the boundedness of the lumped uncertainty.
+\textcolor{red}{$\varphi$ is the boundedness of the lumped uncertainty.
+$\gamma$ is a small or  time-varying positive scalar, $\varphi>1$ and $K_d$ is the designer parameter, such that the deployment dynamics can be regulated as desired.}
 \end{mythm}

### 2016-10-26 manuscript.tex
20161026

@@
 \begin{align}
-\bm\tau = -\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1})),\label{eq:slider control}
+\bm\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1})),\label{eq:slider control}
 \end{align}
@@
 \begin{align}
-\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1K_de^{-2K_1^{-1}F^{-1}(t)}\bm{sign}(S_{r2})
+\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1e^{-2K_1^{-1}F^{-1}(t)}\bm{sign}(S_{r2})
 \end{align}
@@
 \textcolor{red}{$\varphi$ is the boundedness of the lumped uncertainty.
-$\gamma$ is a small or  time-varying positive scalar, $\varphi>1$ and $K_d$ is the designer parameter, such that the deployment dynamics can be regulated as desired.}
+$\gamma$ is designed as a time-varying positive scalar, $\varphi>1$ is the designer parameter, such that the deployment dynamics can be regulated as desired.}
 \end{mythm}
@@
 It is obvious that $S_{q_1}$ is bounded, or exactly saturated, hence $S_{r_1}$ is also bounded if the dynamics can be controlled as desired.
-In addition, one can select a suitable positive scalar $\gamma$ such that $\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\in[-1,1]$.\par
+\textcolor{red}{In addition, for guaranteeing that $x=\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma$ always falls in the field of definition of $y=arcsin(x)$, $\gamma$ can be designed as a time-varying parameter
+    \begin{align}
+    \gamma=\begin{cases}
+    \gamma_0&\Vert\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert\le 1\\
+    \gamma_0\left[\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\right]^{-1}&\Vert\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert> 1,
+    \end{cases}
+    \end{align}
+    where $\gamma_0$ can be selected as $\gamma_0=0.1$, such that $\gamma\int_{t_0}^tS_{q1}d\varsigma$ is guaranteed to satisfy $\gamma\int_{t_0}^tS_{q1}d\varsigma\in[-1,1]$.}\par
 According to Lemma~\ref{lemma:1}, it is apparent that $S_{r2}$ and $S_{r1}$ have the subsequent relation:
@@
 \begin{align}
-H(q)\dot S_{r2} = -\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.
+H(q)\dot S_{r2} = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.
 \end{align}
@@
 \dot V &= S_{r2}^TH(q)\dot S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}+v\dot v\\
-&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
-&= -S_{r2}^T\bm{g}(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -S_{r2}^TR_M(\delta\varphi F(t) K_d\bm{sign}(S_{r1}))\delta\varphi F(t) K_d\bm{sign}(S_{r1})+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}
+&= -S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
+&= -S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
+&= -S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+v\dot v\\
+&= -S_{r2}^TR_M(\delta\varphi F(t) \bm{sign}(S_{r1}))\delta\varphi F(t) \bm{sign}(S_{r1})+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}
 \end{split}
 \end{align}
-Since the command $ -\delta\varphi F(t) K_dS_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$ and $c_2$ such that $0<c_1\le R(\hat\tau_t)<1$ and $0<c_2\le R(\hat\tau_\theta)<1$, and obtain a diagonal matrix as follows:
+Since the command $ -\delta\varphi F(t) S_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ such that $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain a diagonal matrix as follows:
 \begin{align}
-K_1 = \begin{bmatrix}c_1&0\\0&c_2\end{bmatrix}.\label{eq:saturated ratio}
+K_1 = \begin{bmatrix}c_1&0&0\\0&c_2&0\\0&0&c_3\end{bmatrix}.\label{eq:saturated ratio}
 \end{align}
@@
 \begin{align}
-v\dot v =\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\bm{sign}(S_{r2}),
+v\dot v =\varphi\delta S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(S_{r2}),
 \end{align}
@@
 \begin{split}\label{eq:V1_2}
-\dot V&\le -S_{r2}^T\delta\varphi  K_1K_dF(t)\bm{sign}(S_{r2})+S_{r2}^T(\varphi_1+\varphi_2) \bm{sign}(S_{r2})+\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\bm{sign}(S_{r2})\\
-&\le \varphi S_{r2}^T\bm{sign}(S_{r2})-\varphi\delta S_{r2}^T K_d\bm{sign}(S_{r2})
+\dot V&\le -S_{r2}^T\delta\varphi  K_1F(t)\bm{sign}(S_{r2})+S_{r2}^T(\varphi_1+\varphi_2) \bm{sign}(S_{r2})+\varphi\delta S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(S_{r2})\\
+&\le \varphi S_{r2}^T\bm{sign}(S_{r2})-\varphi\delta S_{r2}^T \bm{sign}(S_{r2})\\
+&\le\varphi(1-\delta)S_{r2}^T\bm{sign}(S_{r2})\le 0
 \end{split}
 \end{align}
-owing to the boundedness of the expression above, a large enough $\delta$ can be selected such that $\dot V \le 0$.
-According to the description of Barbalat¡¯s lemmas, it implies that $S_{r2}$ asymptotically converges to zero with the set of suitable designer parameters.\par
-Utilizing $S_{r2}=0$ leads to the equation
+\textcolor{red}{
+where a large enough $\delta>1$ can be selected such that $\dot V \le 0$.
+According to the description of Barbalat¡¯s lemmas, it implies that $S_{r2}$ asymptotically converges to origin.
+Also, the finite convergent time of desired sliding surface can be calculated by referring to~\cite{Ma201667}.}\par
+\textcolor{red}{Utilizing $S_{r2}=0$ leads to the equation
 \begin{align}
@@
 \end{align}
-and select a Lyapunov function candidate
+and for employing Lyapunov second method to analyse the stabilities of $S_{q2}$ and $\Delta\bm q$, we firstly select a Lyapunov function candidate
 \begin{align}
@@
 if and only if $S_{q1} = 0$, accordingly, $S_{q2} = 0$, one has $\dot V_1=0$.
-Hence the asymptotically stability of Eq.~(\ref{eq:eqSq2}) has been proved, and therefore $S_{q2}\rightarrow 0$ as $t\rightarrow \infty$ produces
+Hence the asymptotically stability of Eq.~(\ref{eq:eqSq2}) has been proved, and therefore $S_{q2}\rightarrow 0$ as $t\rightarrow \infty$ induces
 \begin{align}
@@
 \end{align}
-Select the Lyapunov function candidate $V_2=\frac{1}{2}\Delta \bm q^T\Delta\bm q$, the derivative of which follows
+We proceed to select the Lyapunov function candidate $V_2=\frac{1}{2}\Delta \bm q^T\Delta\bm q$ for deriving the asymptotically stability by using Lyapunov second method, and the derivative of $V_2$ follows
 \begin{align}
@@
 Hence asymptotically convergence of $\Delta \bm q$ has been explained, namely, $\Delta \bm q\rightarrow 0$ as $t\rightarrow \infty$.
-To conclude, the error state $\Delta \bm q$ of the system~(\ref{eq:dynamics 1}) asymptotically converges to the origin with the limited input~(\ref{eq:slider control}).
+To conclude, the error state $\Delta \bm q$ of the system~(\ref{eq:dynamics 1}) asymptotically converges to the origin with the limited input~(\ref{eq:slider control})}.
 This completes the proof.
@@
 \begin{align}
-\tau = -\bm{g}(\delta\varphi F(t) K_{d1}\bm{sign}(S_{r3}))
+\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r3}))
 \end{align}
@@
 \begin{align}
-\tau = -\bm{g}(\delta\varphi F(t) K_{d1}\bm{sign}(S_{r4})),
+\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r4})),
 \end{align}
@@
 In this section, the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively.
-The parameters of these controllers can selected as follows: $\delta=1.1$, $\varphi= 1\times 10^{-3}$, $\alpha = 0.8$, $K_d(K_{*})=1$, $\gamma = 0.1$ and $\hat\alpha=0.6$.\par
+The parameters of these controllers can selected as follows: $\delta=1.1$, $\varphi= 1\times 10^{-3}$, $\alpha = 0.8$, $\gamma = 0.1$ and $\hat\alpha=0.6$.\par
 Besides the designer parameter determined, the simulation initial and desired condition can be described as follows.
@@
 Meanwhile, the initial deployment velocity is about 3 $m/s$, and the subsatellite is going to be deployed at 3.5 $km$ vertically.
-The pitching and rolling dynamics is varying in a small range, and hence, without loss of generality, the numerical initial condition gives rise to: $\theta_0 = 0.1$, $\varphi_0 = 0.1$, $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$.
+The pitching and rolling dynamics is varying in a small range, and hence, without loss of generality, the numerical initial condition gives rise to: $\theta_0 = 0.1$, $\phi_0 = 0.1$, $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$.
 Hence the dimensionless tether length is varying in $[0.02,1]$.\par
@@
 Based on the expression above, one can obtain $\bar{m}\Omega^2L\approx 4.79\times 10^{-3}$, and suitable bounded values $\hat\tau_{tmin}$ and $\hat\tau_{tmax}$ can be chosen to make the dimensionless tension $\hat\tau_t$ fall in the region $[-3,0.01]$.\par
-At this point, the simulations of the deployment dynamics of the TSS are able to be carried on, and the results are illustrated in Figure~\ref{fig:3} to~\ref{fig:6}.
-Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that the all the methods finish the deployment in aspect of the tether length.
+At this point, the simulations of the deployment dynamics of the TSS are able to be carried on.
+\textcolor{red}{We firstly conduct the simulation about the pure deployment dynamics without any uncertainties to verify the effectiveness of the proposed control laws, and the results are illustrated in Figure~\ref{fig:3} to~\ref{fig:6}.} Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that the all the methods finish the deployment in aspect of the tether length.
 ST-SMC and QST-SMC complete the deployment at about 4 $rad$, and from Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, and hence the curves of the tether length climb more rapidly at the beginning.
 In contrary, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$.
-This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to origin more early than $S-SMC$ and $QST-SMC$.\par
+This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to origin more early than S-SMC and QST-SMC.\par
 The in-plane and out-of-plane angles reflect the swinging dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}.
@@
 The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) is exhibited in Figure~\ref{fig:6}, in which it is obvious that the limited situations occur frequently.
-Thanks to the scalable dimensionless transform determined conservatively, the tension exerted on the tether falls in the reasonable region.
+Thanks to the scalable dimensionless transform determined conservatively, the tension exerted on the tether falls in the reasonable region.\par
 \begin{figure}
@@
 \end{figure}
+\textcolor{red}{So far, the proposed control laws have been verified in the undisturbed environment.
+However, space perturbations and parameter uncertainties usually occur during the deployment of the tethered satellite system in engineering application.
+For checking the robustness of the proposed control laws, based on the dynamics~(\ref{eq:dynamics 1}), we have the following assumptions about uncertainties and disturbances:
+\begin{align}\begin{split}
+\frac{1}{2}&\le\frac{\hat{\bar m}}{\bar m}\le 2\\
+\frac{1}{2}&\le\frac{\hat L}{L}\le 2\\
+\frac{1}{2}&\le\frac{\hat \Omega}{\Omega}\le 2\\
+\bm\tau_d&=\left(0.05\sin(2\pi t/5000),0.05\sin(2\pi t/5000),0.05\sin(2\pi t/5000)\right)^T,
+\end{split}\end{align}
+where $\hat\bullet$ stands for the measurement of the term $\bullet$ with uncertainties, and $\bm\tau_d$ is the external disturbance meaning  space perturbations, such as gravity gradient torque, aerodynamic interference and solar radiation pressure torque.
+In this simulation, the measured terms can be specified as: $\hat{\bar m}=1.1\bar m$ may mean some space debris affixed to the subsatellite; $\bar L=1.02L$ and $\bar \Omega=0.98\Omega$ mean some measurement errors happening to the total length and the orbital angular velocity.
+In Fig~\ref{fig:6}, although the dynamics has been already stable, the tension is switching in the high frequency.
+It is commonplace in sliding mode controller design, called chattering, since the signum function is used in the input, which may cause unmodelled high frequency dynamics, and for removing chattering, the boundary layer technique is introduced into the proposed control laws through replacing $sign(x)$ by $sat(x/\nu)$, where
+\begin{align}
+sat(x/\nu)=
+\begin{cases}
+x/\nu,&\vert x\vert <\nu\\
+sign(x),&\vert x\vert\ge\nu
+\end{cases}
+\end{align}
+and $\nu$ is the thickness of the boundary layer specified as a positive scalar $\nu=1\times 10^{-4}$ in this simulation.}\par
+\textcolor{red}{
+The simulation results of the deployment dynamics subjected to uncertainties are shown from Fig~\ref{fig:7} to Fig~\ref{fig:10}.
+In Fig~\ref{fig:7}, although there exist the parameter uncertainties, QST-SMC still performs the best deployment among the three methods, and the tethers are deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}.
+In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is eliminated by utilizing the boundary layer technique.
+Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to uncertainties and disturbances.}
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{paper4_fig7_20161025.eps}
+\caption{Length dynamics of the deployment subjected to uncertainties and disturbances}
+\label{fig:7}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{paper4_fig8_20161025.eps}
+\caption{Length rate dynamics of the deployment subjected to uncertainties and disturbances}
+\label{fig:8}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{paper4_fig9_20161025.eps}
+\caption{Angle dynamics of the deployment subjected to uncertainties and disturbances}
+\label{fig:9}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{paper4_fig10_20161025.eps}
+\caption{Tension produced by utilizing boundary layer technique}
+\label{fig:10}
+\end{figure}
 \section{Conclusion}\label{sec:5}

### 2016-10-26 paper4.tex
20161026

@@
 %\usepackage{newtxtext,newtxmath}
-\usepackage[colorlinks=true,citecolor=red,linkcolor=black]{hyperref}
+\usepackage[colorlinks=true,citecolor=black,linkcolor=black]{hyperref}
 %
@@
 
-\author[2]{Zhiqiang Ma}
-\author[1]{Guanghui Sun}
-\author[2]{Zhengkai Li}
+\author[1]{Zhiqiang Ma}
+\author[2]{Guanghui Sun}
+\author[3]{Zhengkai Li}
+\affil[1]{Ph.D. Candidate, Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, Email: zhiqiangma@hit.edu.cn}
+\affil[2]{Associate Professor, Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, Email: guanghuisun@hit.edu.cn}
 
-\affil[1]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email. Email: guanghuisun@hit.edu.cn}
-\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email.}
+\affil[3]{Ph.D. Candidate, Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, Email: lizhengkai1@126.com}
 %\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}
@@
 \end{figure}
+\begin{figure}
+\centering
 \section{Conclusion}\label{sec:5}

### 2016-10-28 manuscript.tex
20161028

@@
 Aslanov et al.
-presented a thruster method driving the space tethered tug, and analyzed the dragging dynamics~\cite{aslanov2013dynamics}.
+presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system is excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}.
 Huang et al.
@@
 $R_0$ is a positive scaler meaning the radius of orbit without disturbance, and $\Omega = \sqrt{\mu_e/R_0^3}$ is the orbital angular velocity where $\mu_e$ is the coefficient of the Earth gravity field.\par
-Based on the assumption above, the kinetic energy and the potential energy of the deployment dynamics can be described as:
+Based on the assumption above, the kinetic energy and the potential energy of the deployment dynamics can be described as~\cite{Mantellato2015}:
 \begin{figure}[http]
@@
 For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
-Combining Eq.~(\ref{eq:Vg}) and Eq.~(\ref{eq:Tt1}) give rise to the Lagrange function:
+Combining Eq.~(\ref{eq:Vg}) and Eq.~(\ref{eq:Tt1}) give rise to the Lagrange function~\cite{Mantellato2015}:
 \begin{align}
@@
 \end{align}
-and utilize Lagrangian mechanics theory to obtain the following expression
+and utilize Lagrangian mechanics theory to obtain the following expression\cite{Sun2014304,Mantellato2015}
 \begin{align}
@@
 $\Theta$ denotes unknown but constant parameters, and particularly it is a constant vector in this dimensionless form.
-Reconstruct the parametrization $Y\Theta$ in terms of a reference $\dot{\bm q}_r$:
+Reconstruct the parametrization $Y\Theta$ in terms of a reference $\dot{\bm q}_r$~\cite{parra2003dynamic}:
 \begin{align}
@@
 \textcolor{red}{So far, the proposed control laws have been verified in the undisturbed environment.
-However, space perturbations and parameter uncertainties usually occur during the deployment of the tethered satellite system in engineering application.
+However, space perturbations and parametric uncertainties usually occur during the deployment of the tethered satellite system in engineering application.
 For checking the robustness of the proposed control laws, based on the dynamics~(\ref{eq:dynamics 1}), we have the following assumptions about uncertainties and disturbances:
@@
 \begin{cases}
-x/\nu,&\vert x\vert <\nu\\
+x,&\vert x\vert <\nu\\
 sign(x),&\vert x\vert\ge\nu
@@
 \textcolor{red}{
-The simulation results of the deployment dynamics subjected to uncertainties are shown from Fig~\ref{fig:7} to Fig~\ref{fig:10}.
-In Fig~\ref{fig:7}, although there exist the parameter uncertainties, QST-SMC still performs the best deployment among the three methods, and the tethers are deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}.
+The simulation results of the deployment dynamics subjected to uncertainties are exhibited from Fig~\ref{fig:7} to Fig~\ref{fig:10}.
+In Fig~\ref{fig:7}, although there exist parametric uncertainties compared with Figs~\ref{fig:3}-\ref{fig:6}, QST-SMC still performs the deployment with the shortest rise time and the minimum overshoot among the three methods, and the tethers are deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}.
 In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is eliminated by utilizing the boundary layer technique.

### 2016-10-30 manuscript.tex
20161030

@@
 This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system.
-The tethered satellite system is modelled based on Lagrangian mechanics theory, and to overcome the limited input of the dynamic model, a new scalable dimensionless transform and strictly bounded terms are designed to guarantee the existence of the ratio between limited input and command signal.
+To overcome the limited input of the dynamic model, a new scalable dimensionless transform and strictly bounded terms are designed to guarantee the existence of the ratio between limited input and command signal.
 The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain, and the stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation to guarantee that the asymptotically stability of the deployment dynamics.
@@
 \section{Introduction}
-The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique supports various applications for space exploration and scientific research, such as space debris removal~\cite{zhao2014thrust}, space elevator~\cite{kojima2015mission}, satellite de-orbit~\cite{zhong2013dynamics,zhong2013long} and the tethered space robot~\cite{huang2014optimal}.
+The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique supports various applications for space exploration and scientific research, such as space debris removal, space elevator, satellite de-orbit and the tethered space robot~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}.
 Many international space research institutes have launched some orbital, suborbital and ground experiments in an effort, such as TSS-1R, SEDS, MAST and YES2, to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
-These experimental results make researchers proceed to advance mechanics, kinetic and control studies intensively, to tackle the challenges of requirements from space missions in the future~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line}.\par
+These experimental results make researchers proceed to advance mechanics, kinetic and control studies intensively, to tackle the challenges of requirements from space missions in the future~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.\par
 
@@
 implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and the thruster was used to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}.
-Aslanov et al.
-presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system is excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}.
-Huang et al.
+\textcolor{red}{Aslanov et al.
+presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system is excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}.} Huang et al.
 investigated the attitude and deploying dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}.
@@
 $R_0$ is a positive scaler meaning the radius of orbit without disturbance, and $\Omega = \sqrt{\mu_e/R_0^3}$ is the orbital angular velocity where $\mu_e$ is the coefficient of the Earth gravity field.\par
-Based on the assumption above, the kinetic energy and the potential energy of the deployment dynamics can be described as~\cite{Mantellato2015}:
+%Based on the assumption above, the kinetic energy and the potential energy of the deployment dynamics can be described as~\cite{Mantellato2015}:
 \begin{figure}[http]
@@
 \end{figure}
-\begin{align}
-T_t
-&= \frac{1}{2}\sum\limits_{s=1}^2 m_s\bm{R_s'\cdot R_s'}\notag\\
-&= \frac{1}{2}m\bm{R_0'\cdot R_0'}+\frac{1}{2}\sum\limits_{s=1}^2 m_s\bm{r_s'\cdot r_s'}\notag\\
-&= \frac{1}{2}m\Omega^2R_0^2+\frac{1}{2}\bar{m}l^2\begin{bmatrix}\phi'+(\theta'+\Omega)^2\end{bmatrix}+\frac{1}{2}\bar{m}l'^2\label{eq:Tt1}\\
-V_g
-&= -\mu_e\sum\limits_{s=1}^2\frac{m_s}{\vert \bm{R_0+r_s}\vert}\notag\\
-&= -m\Omega^2R_0^2+\frac{\bar{m}\Omega^2l^2}{2}(1-3\cos{^2\theta}\cos^2\phi),\label{eq:Vg}
-\end{align}
-where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively.
+%\begin{align}
+%T_t
+%&= \frac{1}{2}\sum\limits_{s=1}^2 m_s\bm{R_s'\cdot R_s'}\notag\\
+%&= \frac{1}{2}m\bm{R_0'\cdot R_0'}+\frac{1}{2}\sum\limits_{s=1}^2 m_s\bm{r_s'\cdot r_s'}\notag\\
+%&= \frac{1}{2}m\Omega^2R_0^2+\frac{1}{2}\bar{m}l^2\begin{bmatrix}\phi'+(\theta'+\Omega)^2\end{bmatrix}+\frac{1}{2}\bar{m}l'^2\label{eq:Tt1}\\
+%V_g
+%&= -\mu_e\sum\limits_{s=1}^2\frac{m_s}{\vert \bm{R_0+r_s}\vert}\notag\\
+%&= -m\Omega^2R_0^2+\frac{\bar{m}\Omega^2l^2}{2}(1-3\cos{^2\theta}\cos^2\phi),\label{eq:Vg}
+%\end{align}
+%where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively.
 $(\cdot)'$ represents the differentiation with respective to time, and $l$ means the tether length connecting the satellites.
@@
 For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
-Combining Eq.~(\ref{eq:Vg}) and Eq.~(\ref{eq:Tt1}) give rise to the Lagrange function~\cite{Mantellato2015}:
-\begin{align}
-\begin{split}
-L=&T_t-V_g\\
-=&\frac{\bar ml^2}{2}\begin{pmatrix}\phi'^{2}+\cos^2\phi(\theta'+\Omega)^2\end{pmatrix}+\frac{\bar ml'^2}{2}\\
-&-\frac{\bar m\Omega^2l^2}{2}\begin{pmatrix}1-3\cos^2\theta\cos^2\phi\end{pmatrix}+\frac{3m\Omega^2R_0^2}{2},
-\end{split}
-\end{align}
-and utilize Lagrangian mechanics theory to obtain the following expression\cite{Sun2014304,Mantellato2015}
+%Combining Eq.~(\ref{eq:Vg}) and Eq.~(\ref{eq:Tt1}) give rise to the Lagrange function~\cite{Mantellato2015}:
+%\begin{align}
+%\begin{split}
+%L=&T_t-V_g\\
+%=&\frac{\bar ml^2}{2}\begin{pmatrix}\phi'^{2}+\cos^2\phi(\theta'+\Omega)^2\end{pmatrix}+\frac{\bar ml'^2}{2}\\
+%&-\frac{\bar m\Omega^2l^2}{2}\begin{pmatrix}1-3\cos^2\theta\cos^2\phi\end{pmatrix}+\frac{3m\Omega^2R_0^2}{2},
+%\end{split}
+%\end{align}
+Based on the assumption above and Lagrangian mechanics theory, we can directly obtain the following expression for the tethered satellite system~\cite{Sun2014304,Mantellato2015}
 \begin{align}
@@
 \end{align}
-\textcolor{red}{where $\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster and the out-of-plane thruster, respectively, and $\tau_t d$, $\tau_\theta d$ and $\tau_\phi d$ stand for the bounded external disturbances.
+\textcolor{red}{where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively.
+$(\cdot)'$ represents the differentiation with respective to time, and $l$ means the tether length connecting the satellites.
+$\theta$ and $\phi$ depict the rolling and pitching dynamics of the TSS.
+For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
+$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster and the out-of-plane thruster, respectively, and $\tau_t d$, $\tau_\theta d$ and $\tau_\phi d$ stand for the bounded external disturbances.
 Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
@@
 \end{align}
-where $Y_r = Y_r(\bm q,\dot{\bm q},\dot{\bm q}_r,\ddot{\bm q}_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $S_r$ is able to be obtained, as follows:
+where $Y_r = Y_r(\bm q,\dot{\bm q},\dot{\bm q}_r,\ddot{\bm q}_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $\bm S_r$ is able to be obtained, as follows:
 \begin{align}
-H(\bm q)\dot S_r+C(\bm q,\dot{\bm q})S_r=\bm\tau +\bm\tau_d- Y_r\Theta\label{eq:dynamic model 2}
+H(\bm q)\dot {\bm S}_r+C(\bm q,\dot{\bm q})\bm S_r=\bm\tau +\bm\tau_d- Y_r\Theta\label{eq:dynamic model 2}
 \end{align}
-where $S_r$ is defined as
+where $\bm S_r$ is defined as
 \begin{align}
-S_r=\dot {\bm q}-\dot {\bm q}_r.\label{eq:Sr1}
+\bm S_r=\dot {\bm q}-\dot {\bm q}_r.\label{eq:Sr1}
 \end{align}
@@
 \dot {\bm q}_r&=\dot{\bm q}_d-\alpha\Delta\bm q-\gamma\bm\sigma\\
-\dot{\bm\sigma}&=\bm{sign}(S)\\
-S&=\Delta\dot{\bm q}+\alpha\Delta\bm q\label{eq:pid controller}
+\dot{\bm\sigma}&=\bm{sign}(\bm S)\\
+\bm S&=\Delta\dot{\bm q}+\alpha\Delta\bm q\label{eq:pid controller}
 \end{split}\end{align}
@@
 \end{align}
-and it's notable that the function above is saturated or bounded and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$.
+and it's notable that the function above is saturated and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$.
 The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-\Delta h,\Delta h]$, and once the function $y=Sine(x)+\Delta h$ settles, one can chose the function $y = x+arcsin(\Delta h)$ such that
@@
 \end{proof}
+\begin{myrem}\textcolor{red}{Moreover, we think that a quantity $y$ or vector $\bm y$ is saturated iff it is produced directly by the saturated function $y=Sine(x)$ or $\bm y=\bm{Sine(x)}$.
+Otherwise, the bounded quantity is different from the saturated one since it does not own the standard formulation like $y=Sine(x)$, i.e., a quantity can just be said a bounded quantity if its boundary is $[a,b]$ with $a\neq -1$ or $b\neq 1$.}
+\end{myrem}
 \begin{figure}
@@
 \begin{split}
-S_{r1} &= S_{q1}+\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\\
-S_{q1} &= \bm{Sine}(\Delta \dot {\bm q}+\alpha\Delta\bm q),
+\bm S_{r1} &= \bm S_{q1}+\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\\
+\bm S_{q1} &= \bm{Sine}(\Delta \dot {\bm q}+\alpha\Delta\bm q),
 \end{split}
@@
 \begin{align}
-\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1e^{-2K_1^{-1}F^{-1}(t)}\bm{sign}(S_{r2})
+\frac{d}{dt}F(t) = \delta\varphi \bm S_{r2}^T K_1e^{-2K_1^{-1}F^{-1}(t)}\bm{sign}(\bm S_{r2})
 \end{align}
@@
 \begin{proof}
-Consider dynamic coordinates change $S_{r2}$ with the regular error variable but not the $Sine$ form:
+Consider dynamic coordinates change $\bm S_{r2}$ with the regular error variable but not the $Sine$ form:
 \begin{align}
 \begin{split}
-S_{r2} &= S_{q2}+arcsin(\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma)\\
-S_{q2} &= \Delta \dot {\bm q}+\alpha \Delta \bm q,
+\bm S_{r2} &= \bm S_{q2}+\bm{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma)\\
+\bm S_{q2} &= \Delta \dot {\bm q}+\alpha \Delta \bm q,
 \end{split}
 \end{align}
-It is obvious that $S_{q_1}$ is bounded, or exactly saturated, hence $S_{r_1}$ is also bounded if the dynamics can be controlled as desired.
-\textcolor{red}{In addition, for guaranteeing that $x=\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma$ always falls in the field of definition of $y=arcsin(x)$, $\gamma$ can be designed as a time-varying parameter
+where $\bm y=\bm{arcsin}(\bm x)$ is the vector function with
+\begin{align}
+\bm{arcsin}(\bm x) = \left(arcsin(x_1),arcsin(x_2),\cdots,arcsin(x_n)\right)^T
+\end{align}
+for a vector $\bm x=\left(x_1,x_2,\cdot,x_n\right)^T$.
+It is obvious that $\bm S_{q_1}$ is bounded, or exactly saturated, hence $\bm S_{r_1}$ is also bounded if the dynamics can be controlled as desired.
+\textcolor{red}{In addition, for guaranteeing that $\bm x=\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma$ always falls in the field of definition of $\bm y=arcsin(\bm x)$, $\gamma$ can be designed as a time-varying parameter
     \begin{align}
     \gamma=\begin{cases}
-    \gamma_0&\Vert\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert\le 1\\
-    \gamma_0\left[\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\right]^{-1}&\Vert\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert> 1,
+    \gamma_0&\Vert\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert\le 1\\
+    \gamma_0\Vert\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert^{-1}&\Vert\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert> 1,
     \end{cases}
     \end{align}
-    where $\gamma_0$ can be selected as $\gamma_0=0.1$, such that $\gamma\int_{t_0}^tS_{q1}d\varsigma$ is guaranteed to satisfy $\gamma\int_{t_0}^tS_{q1}d\varsigma\in[-1,1]$.}\par
-According to Lemma~\ref{lemma:1}, it is apparent that $S_{r2}$ and $S_{r1}$ have the subsequent relation:
+    where $\gamma_0$ can be selected as $\gamma_0=0.1$, such that $\gamma\int_{t_0}^t\bm S_{q1}d\varsigma$ is guaranteed to satisfy $\gamma\int_{t_0}^t\bm S_{q1}d\varsigma\in[-1,1]$.}\par
+According to Lemma~\ref{lemma:1}, it is apparent that $\bm S_{r2}$ and $\bm S_{r1}$ have the subsequent relation:
 \begin{align}
-&S_{r2}^T \bm{sign}(S_{r2}) \ge  S_{r1}^T \bm{sign}(S_{r1})\\
-&\bm{sign}(S_{r2})=\bm{sign}(S_{r1}),
+&\bm S_{r2}^T \bm{sign}(\bm S_{r2}) \ge  \bm S_{r1}^T \bm{sign}(\bm S_{r1})\\
+&\bm{sign}(\bm S_{r2})=\bm{sign}(\bm S_{r1}),
 \end{align}
-Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinates change $S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $S_{r2}$ holds results in the following expression:
+Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinates change $\bm S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $\bm S_{r2}$ holds results in the following expression:
 \begin{align}
-H(q)\dot S_{r2} = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.
+H(q)\dot {\bm S}_{r2} = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))-C(q,\dot q)\bm S_{r2}-Y_{r2}\Theta.
 \end{align}
@@
 \begin{align}
-V=\frac{1}{2}S_{r2}^TH(q)S_{r2}+\frac{1}{2}v^2,
+V=\frac{1}{2}\bm S_{r2}^TH(q)\bm S_{r2}+\frac{1}{2}v^2,
 \end{align}
@@
 \begin{split}
-\dot V &= S_{r2}^TH(q)\dot S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}+v\dot v\\
-&= -S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
-&= -S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1}))+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -S_{r2}^TR_M(\delta\varphi F(t) \bm{sign}(S_{r1}))\delta\varphi F(t) \bm{sign}(S_{r1})+S_{r2}^T\bm\tau_d-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}
+\dot V &= \bm S_{r2}^TH(q)\dot {\bm S}_{r2}+\frac{1}{2}\bm S_{r2}^T\dot H(q)\bm S_{r2}+v\dot v\\
+&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TC(q,\dot q)\bm S_{r2}+\frac{1}{2}\bm S_{r2}^T\dot H(q)\bm S_{r2}-\bm S_{r2}^TY_{r2}\Theta+v\dot v\\
+&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\Theta+\frac{1}{2}\bm S_{r2}^T(\dot H(q)-2C(q,\dot q))\bm S_{r2}+v\dot v\\
+&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\Theta+v\dot v\\
+&= -\bm S_{r2}^TR_M(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))\delta\varphi F(t) \bm{sign}(\bm S_{r1})+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{\bm r2}\Theta+v\dot v.\label{eq:V1_1}
 \end{split}
 \end{align}
-Since the command $ -\delta\varphi F(t) S_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ such that $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain a diagonal matrix as follows:
+Since the command $ -\delta\varphi F(t) \bm S_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ such that $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain a diagonal matrix as follows:
 \begin{align}
@@
 \begin{align}
-v\dot v =\varphi\delta S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(S_{r2}),
+v\dot v =\varphi\delta \bm S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(\bm S_{r2}),
 \end{align}
-utilizing $\bm{sign}(S_{r1})=\bm{sign}(S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:
+utilizing $\bm{sign}(\bm S_{r1})=\bm{sign}(\bm S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:
 \begin{align}
 \begin{split}\label{eq:V1_2}
-\dot V&\le -S_{r2}^T\delta\varphi  K_1F(t)\bm{sign}(S_{r2})+S_{r2}^T(\varphi_1+\varphi_2) \bm{sign}(S_{r2})+\varphi\delta S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(S_{r2})\\
-&\le \varphi S_{r2}^T\bm{sign}(S_{r2})-\varphi\delta S_{r2}^T \bm{sign}(S_{r2})\\
-&\le\varphi(1-\delta)S_{r2}^T\bm{sign}(S_{r2})\le 0
+\dot V&\le -\bm S_{r2}^T\delta\varphi  K_1F(t)\bm{sign}(\bm S_{r2})+\bm S_{r2}^T(\varphi_1+\varphi_2) \bm{sign}(\bm S_{r2})+\varphi\delta \bm S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(\bm S_{r2})\\
+&\le \varphi \bm S_{r2}^T\bm{sign}(\bm S_{r2})-\varphi\delta \bm S_{r2}^T \bm{sign}(\bm S_{r2})\\
+&\le\varphi(1-\delta)\bm S_{r2}^T\bm{sign}(\bm S_{r2})\le 0
 \end{split}
@@
 where a large enough $\delta>1$ can be selected such that $\dot V \le 0$.
-According to the description of Barbalat¡¯s lemmas, it implies that $S_{r2}$ asymptotically converges to origin.
+According to the description of Barbalat¡¯s lemmas, it implies that $\bm S_{r2}$ asymptotically converges to origin.
 Also, the finite convergent time of desired sliding surface can be calculated by referring to~\cite{Ma201667}.}\par
-\textcolor{red}{Utilizing $S_{r2}=0$ leads to the equation
+\textcolor{red}{Utilizing $\bm S_{r2}=0$ leads to the equation
 \begin{align}
-S_{q2}=-arcsin(\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma),\label{eq:eqSq2}
+\bm S_{q2}=-\bm{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma),\label{eq:eqSq2}
 \end{align}
-and for employing Lyapunov second method to analyse the stabilities of $S_{q2}$ and $\Delta\bm q$, we firstly select a Lyapunov function candidate
+and for employing Lyapunov second method to analyse the stabilities of $\bm S_{q2}$ and $\Delta\bm q$, we firstly select a Lyapunov function candidate
 \begin{align}
-V_1 = \frac{1}{2}S_{q2}^TS_{q_2},
+V_1 = \frac{1}{2}\bm S_{q2}^T\bm S_{q_2},
 \end{align}
@@
 \begin{split}
-\dot V_1 &= S_{q2}^T\dot S_{q_2}\\
-&=-\frac{\gamma S_{q2}^TS_{q1}}{\sqrt{1-\Vert\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert^2}}\\
-&\le -\frac{\gamma \Vert S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\Vert^2}}\le 0,
+\dot V_1 &= \bm S_{q2}^T\dot {\bm S}_{q_2}\\
+&=-\frac{\gamma \bm S_{q2}^TS_{q1}}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert^2}}\\
+&\le -\frac{\gamma \Vert \bm S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert^2}}\le 0,
 \end{split}
 \end{align}
-if and only if $S_{q1} = 0$, accordingly, $S_{q2} = 0$, one has $\dot V_1=0$.
-Hence the asymptotically stability of Eq.~(\ref{eq:eqSq2}) has been proved, and therefore $S_{q2}\rightarrow 0$ as $t\rightarrow \infty$ induces
+if and only if $\bm S_{q1} = 0$, accordingly, $\bm S_{q2} = 0$, one has $\dot V_1=0$.
+Hence the asymptotically stability of Eq.~(\ref{eq:eqSq2}) has been proved, and therefore $\bm S_{q2}\rightarrow 0$ as $t\rightarrow \infty$ induces
 \begin{align}
@@
 \begin{align}
-\dot Z = \vert Z\vert^{\hat\alpha} \bm{sign}(Z),
+\dot Z = \vert Z\vert^{\hat\alpha} {sign}(Z),
 \end{align}
@@
 \begin{align}
-\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r3}))
+\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r3}))
 \end{align}
@@
 \begin{align}
-S_{r3} &= S_{q3}+\gamma\int^t_{t_0}\Vert S_{q3}(\varsigma)\Vert^{\hat\alpha}  \bm{sign}(S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
-S_{q3} &= \Delta \dot q+\alpha \bm{Sine}(\xi\Delta q),\label{eq:Sq3}
+\bm S_{r3} &= \bm S_{q3}+\gamma\int^t_{t_0}\vert \bm S_{q3}(\varsigma)\vert^{\hat\alpha}  \bm{sign}(\bm S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
+\bm S_{q3} &= \Delta \dot {\bm q}+\alpha \bm{Sine}(\xi\Delta \bm q),\label{eq:Sq3}
 \end{align}
 where $0<\hat\alpha< 1$, such that the dynamics~(\ref{eq:dynamic model 2}) can be regulated as desired.
+$\bm y=\vert \bm x\vert^{\hat\alpha}$ is defined as $\vert \bm x\vert^{\hat\alpha} =\left(\vert x_1\vert^{\hat\alpha},\vert x_2\vert^{\hat\alpha},\cdots,\vert x_n\vert^{\hat\alpha}\right)^T$.
 $\varphi$ is the boundedness of the lumped uncertainty, and can be obtained by referring to Theorem~\ref{thm:1}.
@@
 If the designer parameter $\hat\alpha = 1$, the quasi-saturated terminal sliding mode control degenerates into the quasi-saturated sliding mode control.
-Compared with the saturated sliding mode control, $S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method.
-This is because the establishment of the equation $\dot S_{q3} = \gamma\Vert S_{q3}\Vert^{\hat\alpha} \bm{ sign}(S_{q3})$.
+Compared with the saturated sliding mode control, $\bm S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method.
+This is because the establishment of the equation $\dot {\bm S}_{q3} = \gamma\vert \bm S_{q3}\vert^{\hat\alpha} \bm{ sign}(\bm S_{q3})$.
 \end{myrem}
@@
 \begin{align}
-\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r4})),
+\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r4})),
 \end{align}
@@
 \begin{split}
-S_{r4} &= S_{q4}+\gamma\int^t_{t_0}S_{q4}(\varsigma) d\varsigma\\
-S_{q4} &= \bm{Sine}(\Delta \dot q+\alpha\xi\Vert\Delta q\Vert^{\hat\alpha}\bm{sign}(\Delta q)),\label{eq:Sr4}
+\bm S_{r4} &= \bm S_{q4}+\gamma\int^t_{t_0}\bm S_{q4}(\varsigma) d\varsigma\\
+\bm S_{q4} &= \bm{Sine}(\Delta \dot {\bm q}+\alpha\xi\vert\Delta \bm q\vert^{\hat\alpha}\bm{sign}(\Delta \bm q)),\label{eq:Sr4}
 \end{split}

### 2016-10-31 manuscript.tex
20161031

@@
 \end{proof}
+\begin{myrem}
+\textcolor{red}{For the adaptive sliding mode control with input limitation, the adaptive update rate $\frac{d}{dt}F(t)$ always helps to remove the side-effect of the input limitation during the stability analysis by using Lyapunov second method, and moreover, the actual examples of $F(t)$ are unhelpful to the theoretical derivation and the controller design~\cite{Hu2008552,6060930}.
+This is because we can search the actual value of $F(t)$  by the way of state updating from the initial condition $F(0)=0$, for instance, in our simulations, we applied ode45 technique to update states of the overall system including this adaptive update rate.}
+\end{myrem}
 \subsection{Quasi-saturated terminal sliding mode control subject to input limitation}
@@
 The simulation results of the deployment dynamics subjected to uncertainties are exhibited from Fig~\ref{fig:7} to Fig~\ref{fig:10}.
-In Fig~\ref{fig:7}, although there exist parametric uncertainties compared with Figs~\ref{fig:3}-\ref{fig:6}, QST-SMC still performs the deployment with the shortest rise time and the minimum overshoot among the three methods, and the tethers are deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}.
+In Fig~\ref{fig:7}, although there exist parametric uncertainties compared with Figs~\ref{fig:7}-\ref{fig:9}, QST-SMC still performs the deployment with the shortest rise time and the minimum overshoot among the three methods, and the tethers are deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}.
 In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is eliminated by utilizing the boundary layer technique.

### 2016-11-01 manuscript.tex
20161101

@@
 This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system.
-To overcome the limited input of the dynamic model, a new scalable dimensionless transform and strictly bounded terms are designed to guarantee the existence of the ratio between limited input and command signal.
-The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain, and the stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation to guarantee that the asymptotically stability of the deployment dynamics.
-The numerical simulations are reported to verify the effectiveness of the proposed control laws.
+\textcolor{red}{To overcome the limited inputs of the dynamic model, a new scalable dimensionless transformation and strictly bounded terms are designed, which guarantee the existence of the ratio between limited inputs and command signals.} The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain.
+The stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation and guarantee the asymptotically stability of the deployment dynamics.
+\textcolor{red}{Finally, numerical simulations are presented to verify the effectiveness of the proposed control laws.}
 \end{abstract}
@@
 \section{Introduction}
-The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, and this technique supports various applications for space exploration and scientific research, such as space debris removal, space elevator, satellite de-orbit and the tethered space robot~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}.
-Many international space research institutes have launched some orbital, suborbital and ground experiments in an effort, such as TSS-1R, SEDS, MAST and YES2, to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
-These experimental results make researchers proceed to advance mechanics, kinetic and control studies intensively, to tackle the challenges of requirements from space missions in the future~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.\par
+The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space exploration and scientific research, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}.
+\textcolor{red}{Many international space research institutes have launched some orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
+These experimental results intensively help researchers proceed to promote advanced mechanics, kinetic and control studies, to tackle the future challenges of space activities~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.}\par
 
-Recent scientific researches on deployment of the tethered satellite focus on the stabilization of the dynamics, and have varying merit and outcomes, providing different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approach~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.
-Among the deployment stabilization strategies, the hybrid tension and thruster control boosts to the new developments.
+\textcolor{red}{Recent scientific researches about deployment of the tethered satellite system focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.} Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the tethered satellite system.
 Iki et al.
-implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and the thruster was used to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}.
+implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and utilized the thruster to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}.
 \textcolor{red}{Aslanov et al.
-presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system is excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}.} Huang et al.
-investigated the attitude and deploying dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}.
+presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}.} Huang et al.
+investigated the attitude and deployment dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}.
 Jung et al.
 adopted thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}.
-Liu et al.
-equipped the thruster system, which consisted of four pairs of thrusters, in the subsatellite dedicating for regulation of the attitude and deployment dynamics~\cite{liu2014attitude}.
-Zakrzhevskii divided the deployment process into two stages, the first stage of which ejected the tether with thruster to position the tether at desired beginning point of the second stage, and the second stage continued to adjust the tether to the stable vertical configuration by using tension generated by friction~\cite{zakrzhevskii2016method}.
+\textcolor{red}{Liu et al.
+equipped the subsatellite with the thruster system, consisting of four pairs of thrusters, in order to regulate the attitude and deployment dynamics~\cite{liu2014attitude}.
+Zakrzhevskii divided the deployment process into two stages: in the first stage, the thruster was used to eject to the desired starting point of the next stage, and in the second stage, the tether was adjusted to the stable vertical configuration using tension generated by friction~\cite{zakrzhevskii2016method}.
 Mantellato et al.
-reported the thrust-aided librating deployment of tape tethers, and the force acting on the tape tether included the tension and thruster force~\cite{mantellato2015thrust}.
-This hybrid strategy has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, thus is broadly utilized in reality compared with other control strategies.\par
+reported the thrust-aided deployment of tape tethers driven by both the tension and thruster force~\cite{mantellato2015thrust}.
+These hybrid strategies has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, and thus is broadly utilized in engineering applications compared with other control strategies.}\par
 
-There also exist some obstacles in the design of the hybrid control.
-Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical condition, i.e., the tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the space tether.
+There also exist some obstacles in the hybrid control design.
+Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical conditions, i.e., the tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the space tether.
 Also, the thruster can not provide infinite force~\cite{martinez1998spacecraft}.
-Hence the tension and thruster force for the deployment/retrevial are both limited, and in the view of control theory, the phenomena usually causes the input limitation of a dynamic system.
-Substituting limited inputs into unmodified conventional control scheme designed for unlimited input system results in lost of control or poor performance, and theoretically, such kind of implement is unreasonable.
-Hence to cope with input limitation in the tethered satellite system (TSS), some scientific researchers spent much effort on restricting input, providing many solutions on satellite arrangements and deployments.
+Hence the tension and thruster force for the deployment/retrievial are both limited, and in the view of control theory, the phenomena usually causes the input limitation of a dynamic system.
+Substituting limited inputs into unmodified conventional control scheme designed for systems with unlimited inputs results in poor performance or instability, and theoretically, such kind of implement is unreasonable.
+Hence to cope with input limitation in the tethered satellite system (TSS), many scientific researchers spent much effort on restricting input, providing many solutions on satellite arrangements and deployments.
 Huang et al.
-addressed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect of constrained input by using specific auxiliary design systems~\cite{huang2015adaptive}.
+proposed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect of constrained input by using specific auxiliary design systems~\cite{huang2015adaptive}.
 Wen et al.
@@
 reported the variable structure scheme for the deployment with thruster control, where the thruster is used to guarantee the positive tension during the mission~\cite{yingying2012variable}.
-In summary, existed studies deal with the major issue about the deployment with restricted tension and thruster force in two ways, accordingly, the suitable physical compensation and the elaborate design of limited input.
+In summary, existing studies deal with the major issue about the deployment with restricted tension and thruster force in two ways, accordingly, the suitable physical compensation and the elaborate design of limited input.
 In aspect of designing elaborate limited inputs, as Wen et al.
-explained, the limited terms, including the tension and the state of the deployment, can be viewed as the solution of a nonlinear optimal control \cite{wen2015tension}.
-Hu reported an adaptive sliding mode control with saturated input by using reduced sliding dynamic design approach \cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.
-In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the tethered satellite system is studied.
+explained, the limited terms, including the tension and the states of deployment dynamics, can be viewed as the solution of a nonlinear optimal control issue~\cite{wen2015tension}.
+\textcolor{red}{Hu reported an adaptive sliding mode control law with saturated input by using reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the tethered satellite system is studied.
 For coping with the input saturation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function.
@@
 In order to improve the performance of the sliding phase, the terminal attractor is incorporated into the design of the ideal sliding surface.
-Numerical simulations are performed to illustrate that the stabilization of the deployment is accomplished by the controller designed in spite of the input limitation.\par
-The paper is organized as follows: Section \ref{sec:2} introduces the standard mathematical model of the deployment of the TSS.
-Section \ref{sec:3} designs the adaptive saturated sliding mode control laws with input limitation for the dynamics, and these simulations are exhibited in Section \ref{sec:4} to reveal the effectiveness and efficiency.
-The conclusion is given in Section \ref{sec:5}.
+We perform numerical simulations to illustrate that the stabilization of the deployment is accomplished by the controller designed in spite of the input limitation.\par
+The paper is organized as follows: Section~\ref{sec:2} introduces the standard mathematical model of the deployment of the TSS.
+Section~\ref{sec:3} designs the adaptive saturated sliding mode control laws with input limitation for the dynamics, and these simulations are exhibited in Section~\ref{sec:4} to reveal the effectiveness and efficiency.
+The conclusion is given in Section~\ref{sec:5}.
 \section{Mathematical model}\label{sec:2}
@@
 $\bm R_0$ denotes the position vector between $O_2$ and $O$.\par
-In the analysis of the deployment of the TSS, there is a primary assumption that the movement of entire system is approximating to a ``rolling ball'' behavior with three DOFs modelled, and reasonably one can invoke the spherical coordinates to describe the behavior.
-During space mission, the mass of the tether is much smaller than that of the mother satellite, and hence it is always ignored sufficiently.
-Some other assumptions are obvious throughout the analysis, and listed in the following.
-A satellite is able to be regard as a particle under the condition that the length of the tether is large enough, and due to the tiny ratio of the mass between the satellites, the deployment of the subsatellite will not effect the motion of the mother satellite and keep the nominal orbit during the whole mission.
-The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
-Before giving out the model, some preliminary symbols are exhibited.
+\textcolor{red}{In the analysis of the deployment of the TSS, there is a primary assumption that the movement of entire system is similar to a ``rolling ball'' behavior with three DOFs modelled, and it is reasonable to invoke the spherical coordinates to describe the behavior.} During space mission, the mass of the tether is much smaller than that of the mother satellite, and hence it is always ignored sufficiently.
+Some other assumptions are obvious and as follows.
+\textcolor{red}{The sizes of satellites are small compared with the length of the tether, and hence a satellite can be regard as a particle if the tether is long enough.
+Typically, the mass ration between mother satellite and subsatellite, i.e., in YES2, the mother satellite mass is 6530~$kg$, and the subsatellite mass is 12~$kg$~\cite{Williams2008}.
+Due to the tiny mass ratio between the satellites, the deployment of the subsatellite will not affect the motion of the mother satellite and keep the nominal orbit during the whole mission.} The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
+Symbols used in the model are defined as follows.
 $R_0$ is a positive scaler meaning the radius of orbit without disturbance, and $\Omega = \sqrt{\mu_e/R_0^3}$ is the orbital angular velocity where $\mu_e$ is the coefficient of the Earth gravity field.\par
@@
 \textcolor{red}{where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively.
-$(\cdot)'$ represents the differentiation with respective to time, and $l$ means the tether length connecting the satellites.
-$\theta$ and $\phi$ depict the rolling and pitching dynamics of the TSS.
+\textcolor{red}{$(\cdot)'$ represents a first derivative with respect to time, and $l$ means the tether length connecting the satellites.
+$\theta$ and $\phi$ depict the roll and pitch dynamics of the TSS.
 For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
-$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster and the out-of-plane thruster, respectively, and $\tau_t d$, $\tau_\theta d$ and $\tau_\phi d$ stand for the bounded external disturbances.
-Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
+$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster and the out-of-plane thruster, respectively, and $\tau_t d$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
 \begin{align}
@@
 \end{align}
-In reality, once $\lambda = 0$ establishes, the mother satellite and subsatellite collide with each other.
-Hence the minimum of the dimensionless length $\lambda_{min}$ is introduced to maintain the satellites in reasonably safe formation, and also guarantees the non-singularity of the dimensionless transformation~(\ref{eq:varcon}) theoretically.
-$\lambda_{max}$ stands for the maximum tether length ratio.\par
-Tension in a tether is a positive scalar quantity during the deployment, since zero tension is slack, which is inconsistent with the fundamental assumption that the tether is stiff in the ``rolling ball'' model.
+\textcolor{red}{In reality, once $\lambda = 0$ is satisfied, the mother satellite and subsatellite will collide with each other.
+Hence the minimum of the dimensionless length $\lambda_{min}$ is introduced to maintain the reasonably safe formation of the satellites, and also guarantees the non-singularity of the dimensionless transformation~(\ref{eq:varcon}) theoretically.} $\lambda_{max}$ stands for the maximum tether length ratio.\par
+Tension in a tether is a positive scalar quantity during the deployment, since zero tension means slack, which is inconsistent with the fundamental assumption that the tether is stiff in the ``rolling ball'' model.
 $\tau_{tmax}$ denotes the maximum tensile tolerance of the tether, and $\tau_t>\tau_{tmax}$ may leads to the break of tether.
@@
 \end{myrem}
-At this point the deployment dynamics with input limitation has been established, and an adaptive saturated sliding mode  control will be presented in the subsequent section.
+This section have established the deployment dynamics with input limitation and an adaptive saturated sliding mode  control will be presented in the subsequent section.
 \section{Dynamic sliding mode control subject to input limitation}\label{sec:3}
 Before declaring the controller design, some basic precondition is prepared for proceeding derivation.
-The left side of Eq.~(\ref{eq:dynamic model}) is able to be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(\bm q,\dot {\bm q},\ddot {\bm q})$ consists of known nonlinear functions.
+The left side of Eq.~(\ref{eq:dynamic model}) can be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(\bm q,\dot {\bm q},\ddot {\bm q})$ consists of known nonlinear functions.
 $\Theta$ denotes unknown but constant parameters, and particularly it is a constant vector in this dimensionless form.
@@
 \end{align}
-where $Y_r = Y_r(\bm q,\dot{\bm q},\dot{\bm q}_r,\ddot{\bm q}_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $\bm S_r$ is able to be obtained, as follows:
+where $Y_r = Y_r(\bm q,\dot{\bm q},\dot{\bm q}_r,\ddot{\bm q}_r)$. Based on results mentioned above, the open-loop error dynamics expressed by $\bm S_r$ can be obtained, as follows:
 \begin{align}
@@
 \subsection{Saturated sliding mode control subject to input limitation}
-The process above can frame a conventional dynamic sliding PID control scheme, which can regulate the dynamics of n-link robotic manipulator if extending the dimension in the derivation above \cite{parra2003dynamic}.
-However, it is not able to regulate the dynamics of the deployment as desired theoretically, because the input $\tau$ in the PID controller is not confined to the characteristics of the tension.
-For coping with the issue about the bounded input, we develop the dynamic sliding mode control with the experience of saturated manifold, which is also a popular technique in the control of Lagrangian system.\par
+The process above can frame a conventional dynamic sliding PID control scheme, which can regulate the dynamics of n-link robotic manipulator if the dimension in the derivation above is extended~\cite{parra2003dynamic}.
+However, it is not possible to regulate the dynamics of the deployment as desired theoretically, because the input $\tau$ in the PID controller is not confined to the characteristics of the tension.
+To cope with the issue about the bounded input, we develop the dynamic sliding mode control with the experience of saturated manifold, which is also a popular technique in the control of Lagrangian system.\par
 Before giving out main results, some routine lemmas emerge in advance to support the derivation.
@@
 \begin{align}
-\bm\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(S_{r1})),\label{eq:slider control}
+\bm\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1})),\label{eq:slider control}
 \end{align}
@@
 \end{align}
-where $K_1\in R^{3\times 3}$ is a positive define diagonal matrix, which will be given out later, and if $K\in R^{3\times 3}$, define
+\textcolor{red}{where $K_1\in R^{3\times 3}$ is a positive definite diagonal matrix, which will be given out later, and if $K\in R^{3\times 3}$, define}
 \begin{align}
@@
 \textcolor{red}{$\varphi$ is the boundedness of the lumped uncertainty.
-$\gamma$ is designed as a time-varying positive scalar, $\varphi>1$ is the designer parameter, such that the deployment dynamics can be regulated as desired.}
+$\gamma$ is designed as a time-varying positive scalar and $\varphi>1$ is the design parameter, so that the deployment dynamics can be regulated as desired.}
 \end{mythm}
@@
     \end{align}
-    where $\gamma_0$ can be selected as $\gamma_0=0.1$, such that $\gamma\int_{t_0}^t\bm S_{q1}d\varsigma$ is guaranteed to satisfy $\gamma\int_{t_0}^t\bm S_{q1}d\varsigma\in[-1,1]$.}\par
+    where $\gamma_0$ can be selected as $\gamma_0=0.1$.}\par
 According to Lemma~\ref{lemma:1}, it is apparent that $\bm S_{r2}$ and $\bm S_{r1}$ have the subsequent relation:
@@
 \end{align}
-Since the command $ -\delta\varphi F(t) \bm S_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ such that $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain a diagonal matrix as follows:
+\textcolor{red}{Since the command $ -\delta\varphi F(t) \bm S_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ which satisfy $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain a diagonal matrix as follows:}
 \begin{align}
@@
 \end{align}
-$v\dot v$ is able to be derived as follows:
+\textcolor{red}{$v\dot v$ can be derived as follows:
 \begin{align}
@@
 \end{align}
-utilizing $\bm{sign}(\bm S_{r1})=\bm{sign}(\bm S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:
+considering $\bm{sign}(\bm S_{r1})=\bm{sign}(\bm S_{r2})$ and $K_1$, we can proceed to rewrite Eq.~(\ref{eq:V1_1}) as:
 \begin{align}
@@
 \end{split}
-\end{align}
+\end{align}}
 \textcolor{red}{
-where a large enough $\delta>1$ can be selected such that $\dot V \le 0$.
-According to the description of Barbalat¡¯s lemmas, it implies that $\bm S_{r2}$ asymptotically converges to origin.
+where a large enough $\delta>1$ can be selected to satisfy $\dot V \le 0$.
+According to the description of Barbalat¡¯s lemmas, we can conclude  that $\bm S_{r2}$ asymptotically converges to origin.
 Also, the finite convergent time of desired sliding surface can be calculated by referring to~\cite{Ma201667}.}\par
@@
 \end{align}
-and for employing Lyapunov second method to analyse the stabilities of $\bm S_{q2}$ and $\Delta\bm q$, we firstly select a Lyapunov function candidate
+and for employing Lyapunov second method to analyse the stabilities of $\bm S_{q2}$ and $\Delta\bm q$, we firstly select a Lyapunov candidate function
 \begin{align}
@@
 \end{align}
-where $0<p/q<1$ and $p$ and $q$ are both positive odd, and a shrewd formula
+\textcolor{red}{where $0<p/q<1$ while $p$ and $q$ are both positive odd, and a equivalent formula}
 \begin{align}
@@
 \end{align}
-where $0<\hat \alpha<1$, performs the same behavior.
-Inducting the terminal attractor into the saturated sliding mode control yields a saturated slider-like scheme, and for adopting to the system subject to input limitation, an assumption is given firstly.
+\textcolor{red}{where $0<\hat \alpha<1$, performs the same behavior.
+Putting the terminal attractor into the saturated sliding mode control yields a saturated slider-like scheme, and before introducing the input limitation into the system, an assumption is given firstly.}
 \begin{myas}\label{as:1}
@@
 \begin{myrem}
-If the designer parameter $\hat\alpha = 1$, the quasi-saturated terminal sliding mode control degenerates into the quasi-saturated sliding mode control.
+If the design parameter $\hat\alpha = 1$, the quasi-saturated terminal sliding mode control degenerates into the quasi-saturated sliding mode control.
 Compared with the saturated sliding mode control, $\bm S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method.
@@
 \begin{myrem}
-Assumption~\ref{as:1} guarantees that the input $\tau$ is bounded in Theorem~\ref{thm:2}, accordingly, a tiny positive scalar $c$ is able to be found such that $0<c\le R(\hat\tau_t)<1$ always exists.
-Admittedly, such kind of assumption is ''skillful'', but meaningful to arbitrary controllable dynamics in reality.
+\textcolor{red}{Assumption~\ref{as:1} guarantees that the input $\tau$ is bounded in Theorem~\ref{thm:2}, accordingly, a tiny positive scalar $c$ can be found to ensure that $0<c\le R(\hat\tau_t)<1$ always exists.} Admittedly, such kind of assumption is ''skillful'', but meaningful to arbitrary controllable dynamics in reality.
 It is reasonable to propose the terminal sliding mode control for the dynamics as follows:
@@
 \end{align}
-such that the finite convergence of the system~(\ref{eq:Sr4}) can be ensured by using terminal sliding mode theory.
+so that the finite convergence of the system~(\ref{eq:Sr4}) can be ensured by using terminal sliding mode theory.
 $\varphi$ is the boundedness of the lumped uncertainty, and can be obtained by referring to Theorem~\ref{thm:1}.
@@
 \section{Simulation studies}\label{sec:4}
-In this section, the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively.
-The parameters of these controllers can selected as follows: $\delta=1.1$, $\varphi= 1\times 10^{-3}$, $\alpha = 0.8$, $\gamma = 0.1$ and $\hat\alpha=0.6$.\par
-Besides the designer parameter determined, the simulation initial and desired condition can be described as follows.
+This section presents the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively.
+The parameters of these controllers can be selected as follows: $\delta=1.1$, $\varphi= 1\times 10^{-3}$, $\alpha = 0.8$, $\gamma = 0.1$ and $\hat\alpha=0.6$.\par
+Besides the design parameter determined, the simulation initial and desired condition can be described as follows.
 The circular orbital altitude is selected around 260 $km$ approximately, and the orbital angular velocity is about $1.17\times 10^{-3}$ $rad/s$.
-At the initial ejection of the subsatellite, the true anomaly is assumed 0 $rad$.
+At the initial ejection of the subsatellite, the true anomaly is assumed to be 0 $rad$.
 Meanwhile, the initial deployment velocity is about 3 $m/s$, and the subsatellite is going to be deployed at 3.5 $km$ vertically.
-The pitching and rolling dynamics is varying in a small range, and hence, without loss of generality, the numerical initial condition gives rise to: $\theta_0 = 0.1$, $\phi_0 = 0.1$, $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$.
-Hence the dimensionless tether length is varying in $[0.02,1]$.\par
+\textcolor{red}{The pitch and roll dynamics is varying in a small range, and hence, without loss of generality, the numerical initial condition gives rise to: $\theta_0 = 0.1$, $\phi_0 = 0.1$, $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$.
+Hence the dimensionless tether length is in the range of $[0.02,1]$.}\par
 During the deployment, the dimensionless thruster forces which manage the in-plane angle and the out-of-plane angle are assumed to be saturated with $\vert\hat\tau_{\theta}\vert\le5 $ and $\vert\hat\tau_{\phi}\vert\le 5$.
@@
 \end{align}
-Based on the expression above, one can obtain $\bar{m}\Omega^2L\approx 4.79\times 10^{-3}$, and suitable bounded values $\hat\tau_{tmin}$ and $\hat\tau_{tmax}$ can be chosen to make the dimensionless tension $\hat\tau_t$ fall in the region $[-3,0.01]$.\par
-At this point, the simulations of the deployment dynamics of the TSS are able to be carried on.
-\textcolor{red}{We firstly conduct the simulation about the pure deployment dynamics without any uncertainties to verify the effectiveness of the proposed control laws, and the results are illustrated in Figure~\ref{fig:3} to~\ref{fig:6}.} Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that the all the methods finish the deployment in aspect of the tether length.
-ST-SMC and QST-SMC complete the deployment at about 4 $rad$, and from Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, and hence the curves of the tether length climb more rapidly at the beginning.
-In contrary, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$.
-This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to origin more early than S-SMC and QST-SMC.\par
-The in-plane and out-of-plane angles reflect the swinging dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}.
-For ST-SMC, the in-plane dynamics is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time, and hence the coalition of the length and the swinging dynamics implies that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC.
-S-SMC makes the tether swing to desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
+Based on the expression above, one can obtain $\bar{m}\Omega^2L\approx 4.79\times 10^{-3}$, and suitable boundary values $\hat\tau_{tmin}$ and $\hat\tau_{tmax}$ can be chosen to make the dimensionless tension $\hat\tau_t$ fall in the region $[-3,0.01]$.\par
+At this point, the simulations of the deployment dynamics of the TSS can be carried on.
+\textcolor{red}{We firstly conduct the simulation about the pure deployment dynamics without any uncertainties to verify the effectiveness of the proposed control laws, and the results are illustrated in Figure~\ref{fig:3} to~\ref{fig:6}.
+Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that all the methods can realize the deployment in aspect of the tether length.} ST-SMC and QST-SMC complete the deployment at about 4 $rad$.
+\textcolor{red}{As shown in Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, indicating the curves of the tether length climb more rapidly at the beginning.} However, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$.
+This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to origin earlier than S-SMC and QST-SMC.\par
+\textcolor{red}{The in-plane and out-of-plane angles reflect the swing dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}.} For ST-SMC, the in-plane dynamics is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time.
+\textcolor{red}{Hence the coalition of the length and the swing dynamics implies that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC.} S-SMC makes the tether swing to desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
 The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) is exhibited in Figure~\ref{fig:6}, in which it is obvious that the limited situations occur frequently.
-Thanks to the scalable dimensionless transform determined conservatively, the tension exerted on the tether falls in the reasonable region.\par
+Thanks to the scalable dimensionless transformation determined conservatively, the tension exerted on the tether falls in the reasonable region.\par
 \begin{figure}

### 2016-11-02 manuscript.tex
20161102

@@
 \begin{keyword}
-Tethered satellite;  Sliding mode control;  Input limitation; Adaptive control
+Tethered satellite system;  Sliding mode control;  Input limitation; Adaptive control
 \end{keyword}
@@
 \section{Introduction}
-The deployment is the key technology of the space tethered satellite system~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space exploration and scientific research, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}.
-\textcolor{red}{Many international space research institutes have launched some orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation design for the deployment of the tethered satellite system~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
+The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space exploration and scientific research, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}.
+\textcolor{red}{Many international space research institutes have launched some orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation design for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
 These experimental results intensively help researchers proceed to promote advanced mechanics, kinetic and control studies, to tackle the future challenges of space activities~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.}\par
 
-\textcolor{red}{Recent scientific researches about deployment of the tethered satellite system focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.} Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the tethered satellite system.
+\textcolor{red}{Recent scientific researches about deployment of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.} Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the TSS.
 Iki et al.
@@
 \textcolor{red}{Aslanov et al.
-presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thrust force acting on the tug~\cite{aslanov2013dynamics}.} Huang et al.
+presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thruster force acting on the tug~\cite{aslanov2013dynamics}.} Huang et al.
 investigated the attitude and deployment dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}.
@@
 Mantellato et al.
-reported the thrust-aided deployment of tape tethers driven by both the tension and thruster force~\cite{mantellato2015thrust}.
+reported the thruster-aided deployment of tape tethers driven by both the tension and thruster force~\cite{mantellato2015thrust}.
 These hybrid strategies has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, and thus is broadly utilized in engineering applications compared with other control strategies.}\par
@@
 Substituting limited inputs into unmodified conventional control scheme designed for systems with unlimited inputs results in poor performance or instability, and theoretically, such kind of implement is unreasonable.
-Hence to cope with input limitation in the tethered satellite system (TSS), many scientific researchers spent much effort on restricting input, providing many solutions on satellite arrangements and deployments.
+Hence to cope with input limitation in the TSS, many scientific researchers spent much effort on restricting input, providing many solutions on satellite arrangements and deployments.
 Huang et al.
@@
 explained, the limited terms, including the tension and the states of deployment dynamics, can be viewed as the solution of a nonlinear optimal control issue~\cite{wen2015tension}.
-\textcolor{red}{Hu reported an adaptive sliding mode control law with saturated input by using reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the tethered satellite system is studied.
+\textcolor{red}{Hu reported an adaptive sliding mode control law with saturated input by using reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the TSS is studied.
 For coping with the input saturation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function.
@@
 \section{Mathematical model}\label{sec:2}
-Figure \ref{fig:1} shows all the elements of the TSS via the geometric representation.
-In the figure, it is apparent that $OXYZ$ denotes the inertial frame, the origin $O$ of which is arranged at the the earth's core.
+\textcolor{red}{Figure \ref{fig:1} shows all the elements of the TSS via the geometric representation.
+In the figure, the axes of the coordinate frame of $OXYZ$ passes through the center of the earth.
 $OX$ and $OY$ are mutually perpendicular axes on the equatorial plane with $OX$ pointing to the spring equinox, and $OZ$ is perpendicular to the equatorial plane, bundling the axis of the earth upwards.
-The frame of $OXYZ$ fulfills the right-hand rule, hence the direction of axis $OY$ is identified.
-Orbital coordinate system is denoted as $O_2xyz$ with the origin $O_2$ located at the center of the TSS.
-$O_2x$ points to the orbital direction, meanwhile $O_2z$ is along the direction downwards towards to the core of the earth, generating the axis $O_2y$ by utilizing the right-hand rule.
-$\theta$ and $\phi$ stand for the in-plane and out-of-plane angle, respectively.
-Another coordinate system $O_2x'y'z'$ represents the TSS frame with $O_2z'$ pointing to the subsatellite along the tether, and $O_2x'y'z'$ can be obtained by rotating $O_2xyz$ around the fixed origin $O_2$.
-$\bm R_0$ denotes the position vector between $O_2$ and $O$.\par
-\textcolor{red}{In the analysis of the deployment of the TSS, there is a primary assumption that the movement of entire system is similar to a ``rolling ball'' behavior with three DOFs modelled, and it is reasonable to invoke the spherical coordinates to describe the behavior.} During space mission, the mass of the tether is much smaller than that of the mother satellite, and hence it is always ignored sufficiently.
+The axis $OY$ completes the right-hand triad.
+The orbital coordinate frame is denoted as $O_2xyz$ with the origin $O_2$ located at the mass center of the TSS.
+$O_2x$ is directed in the direction of orbital velocity, meanwhile $O_2z$ is defined to point towards the center of the earth, generating the axis $O_2y$ by utilizing the right-hand triad.
+The origin of the TSS coordinate frame $O_2x'y'z'$ is also fixed at the mass center of the TSS, and the axis $O_2z'$ is directed along the tether and points to the subsatellite.
+The orientation of $O_2xyz$ relative to the coordinate frame $O_2x'y'z'$ indicates the in-plane and out-of-plane dynamics, where $\theta$ and $\phi$ stand for the in-plane angle and out-of-plane angle, respectively.
+$\bm R_0$ denotes the position vector between $O_2$ and $O$.}\par
+\textcolor{red}{In the analysis of the deployment of the TSS, there is a primary assumption that the movement of entire system is similar to a ``rolling ball'' behavior with three DOFs modelled, and it is reasonable to invoke the spherical coordinates to describe the behavior~\cite{Williams2008}.} During space mission, the mass of the tether is much smaller than that of the mother satellite, and hence it is always ignored sufficiently.
 Some other assumptions are obvious and as follows.
 \textcolor{red}{The sizes of satellites are small compared with the length of the tether, and hence a satellite can be regard as a particle if the tether is long enough.
-Typically, the mass ration between mother satellite and subsatellite, i.e., in YES2, the mother satellite mass is 6530~$kg$, and the subsatellite mass is 12~$kg$~\cite{Williams2008}.
-Due to the tiny mass ratio between the satellites, the deployment of the subsatellite will not affect the motion of the mother satellite and keep the nominal orbit during the whole mission.} The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
+Actually, the mass ratio between the subsatellite and the mother satellite is tiny, i.e., in YES2, the mother satellite mass is 6530~$kg$, and the subsatellite mass is 12~$kg$~\cite{Williams2008}.
+The deployment of the subsatellite will not affect the motion of the mother satellite due to the tiny mass ratio between the satellites and will keep the nominal orbit during the whole mission.} The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
 Symbols used in the model are defined as follows.
-$R_0$ is a positive scaler meaning the radius of orbit without disturbance, and $\Omega = \sqrt{\mu_e/R_0^3}$ is the orbital angular velocity where $\mu_e$ is the coefficient of the Earth gravity field.\par
+$R_0$ is a positive scaler meaning the radius of orbit, and $\Omega = \sqrt{\mu_e/R_0^3}$ is the orbital angular velocity where $\mu_e$ is the coefficient of the earth gravity field.\par
 %Based on the assumption above, the kinetic energy and the potential energy of the deployment dynamics can be described as~\cite{Mantellato2015}:
@@
 %\end{align}
-Based on the assumption above and Lagrangian mechanics theory, we can directly obtain the following expression for the tethered satellite system~\cite{Sun2014304,Mantellato2015}
+Based on the assumption above and Lagrangian mechanics theory, we can directly obtain the following expression for the TSS~\cite{Sun2014304,Mantellato2015}
 \begin{align}
@@
 For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
-$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster and the out-of-plane thruster, respectively, and $\tau_t d$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
+$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster force and the out-of-plane thruster force, respectively, and $\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
 \begin{align}
@@
 The obvious benefits of these transformations are that all the inputs own the positive and negative boundedness and hence satisfy the assumption about limited inputs of existing control laws~\cite{Hu2008552,6060930}.
-The obtained inputs also guarantee the rigorous stability analysis of the proposed sliding mode control in this paper.
-Based on the novel dimensionless transformations, Eq.~(\ref{eq:dynamics 1}) can be converted into dimensionless Euler-Lagrange dynamical equation described as follows:}
+The obtained inputs also essentially guarantee the rigorous stability analysis of the proposed sliding mode control in this paper.
+Based on the novel dimensionless transformations, Eq.~(\ref{eq:dynamics 1}) can be converted into the dimensionless Euler-Lagrange dynamical equation described as follows:}
 \begin{align}
@@
 
-For the deployment or retrieval mission, the following expression exists,
+For the deployment or retrieval mission, the following expression always exists,
 \begin{align}
@@
 \textcolor{red}{In reality, once $\lambda = 0$ is satisfied, the mother satellite and subsatellite will collide with each other.
-Hence the minimum of the dimensionless length $\lambda_{min}$ is introduced to maintain the reasonably safe formation of the satellites, and also guarantees the non-singularity of the dimensionless transformation~(\ref{eq:varcon}) theoretically.} $\lambda_{max}$ stands for the maximum tether length ratio.\par
-Tension in a tether is a positive scalar quantity during the deployment, since zero tension means slack, which is inconsistent with the fundamental assumption that the tether is stiff in the ``rolling ball'' model.
-$\tau_{tmax}$ denotes the maximum tensile tolerance of the tether, and $\tau_t>\tau_{tmax}$ may leads to the break of tether.
-Hence, $\tau_{tmin}$ can be a small value to guarantee the stiff tether, and reasonable $\tau_{tmax}$\ prevents fracture of tether.
+Hence the minimum of the dimensionless length $\lambda_{min}$ is introduced to maintain the reasonably safe formation of the satellites, and also guarantees the non-singularity of the dimensionless transformation~(\ref{eq:dynamics 1}) theoretically.} $\lambda_{max}$ stands for the maximum tether length ratio.\par
+The tension acting on the space tether is a positive scalar during the deployment, since zero tension means slack, which is inconsistent with the fundamental assumption that the tether is stiff in the ``rolling ball'' model.
+$\tau_{tmax}$ denotes the maximum tensile tolerance of the tether, and $\tau_t>\tau_{tmax}$ may leads to the break of the tether.
+Hence, $\tau_{tmin}$ can be a small value to guarantee the stiff tether, and reasonable $\tau_{tmax}$\ prevents the fracture of the tether.
 \end{myrem}
 This section have established the deployment dynamics with input limitation and an adaptive saturated sliding mode  control will be presented in the subsequent section.
-\section{Dynamic sliding mode control subject to input limitation}\label{sec:3}
-Before declaring the controller design, some basic precondition is prepared for proceeding derivation.
+\section{Dynamic sliding mode control subjected to input limitation}\label{sec:3}
+Before declaring the controller design, some basic preconditions are prepared for proceeding derivation.
 The left side of Eq.~(\ref{eq:dynamic model}) can be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(\bm q,\dot {\bm q},\ddot {\bm q})$ consists of known nonlinear functions.
-$\Theta$ denotes unknown but constant parameters, and particularly it is a constant vector in this dimensionless form.
-Reconstruct the parametrization $Y\Theta$ in terms of a reference $\dot{\bm q}_r$~\cite{parra2003dynamic}:
+$\bm\Theta$ denotes unknown but constant parameters, and particularly it is a constant vector in this dimensionless form.
+Reconstruct the parametrization $Y\bm\Theta$ in terms of a reference $\dot{\bm q}_r$~\cite{parra2003dynamic}:
 \begin{align}
- Y_r\Theta\equiv H(\bm q)\ddot {\bm q}_r+C(\bm q,\dot {\bm q})\dot {\bm q}_r+G(\bm q)\label{eq:dynamic model 1}
+ Y_r\bm\Theta\equiv H(\bm q)\ddot {\bm q}_r+C(\bm q,\dot {\bm q})\dot {\bm q}_r+G(\bm q)\label{eq:dynamic model 1}
 \end{align}
@@
 \begin{align}
-H(\bm q)\dot {\bm S}_r+C(\bm q,\dot{\bm q})\bm S_r=\bm\tau +\bm\tau_d- Y_r\Theta\label{eq:dynamic model 2}
+H(\bm q)\dot {\bm S}_r+C(\bm q,\dot{\bm q})\bm S_r=\bm\tau +\bm\tau_d- Y_r\bm\Theta\label{eq:dynamic model 2}
 \end{align}
@@
 Define the tracking error as $\Delta \bm q=\bm q-\bm q_d$, in which $\bm q_d$ is the desired trajectory with $\bm q_d(t)\in C^2$.
-However, the PID controller~(\ref{eq:pid controller}) can not be directly applied to the system~(\ref{eq:dynamic model 2}) with the input limitation, and in the subsequent section, we will utilize the saturated sliding mode technique to modify the PID controller~(\ref{eq:pid controller}) for the system~(\ref{eq:dynamic model 2}).} For deriving the proposed control scheme, some properties should be given out in advance.
+However, the PID controller~(\ref{eq:pid controller}) can not be directly applied to the system~(\ref{eq:dynamic model 2}) with the input limitation, and in the subsequent section, we will utilize the saturated sliding mode technique to modify the controller~(\ref{eq:pid controller}) for the system~(\ref{eq:dynamic model 2}).} For deriving the proposed control scheme, some properties should be given out in advance.
 \begin{mypro}\cite{parra2003dynamic}\label{pro:1}
@@
 where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively.
-Furthermore, one can have $Y_r\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta \bm q,\Delta \dot {\bm q},\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi_0$, in which $\varphi_0$ is a positive scalar determined according to the system state.}
+Furthermore, one can have $Y_r\bm\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta \bm q,\Delta \dot {\bm q},\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\bm\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi_0$, in which $\varphi_0$ is a positive scalar determined according to the system states.}
 \end{mypro}
@@
 According to existing studies, the values of the solar radiation pressure and the aerodynamic torque are about $1\times10^{-5}$ Nm, and meanwhile the gradient torque is in the range of $1\times10^{-5}$ Nm.
-Typically, the space perturbation can be regarded as the periodic function in this paper, and the period equals the orbital period $5000$ s~\cite{Inamori2015192}.
+The space perturbation can be specifically regarded as the periodic function in this paper, and the period equals the orbital period $5000$ s~\cite{Inamori2015192}.
 Hence, the external disturbance can be described by the following expression
@@
 \end{align}
-where $\varphi_1$ is a positive scalar.
+where $\varphi_1$ can be selected as a positive scalar $\varphi_1=1$.
 }
 \end{myas}
-\subsection{Saturated sliding mode control subject to input limitation}
+\subsection{Saturated sliding mode control subjected to input limitation}
 The process above can frame a conventional dynamic sliding PID control scheme, which can regulate the dynamics of n-link robotic manipulator if the dimension in the derivation above is extended~\cite{parra2003dynamic}.
 However, it is not possible to regulate the dynamics of the deployment as desired theoretically, because the input $\tau$ in the PID controller is not confined to the characteristics of the tension.
-To cope with the issue about the bounded input, we develop the dynamic sliding mode control with the experience of saturated manifold, which is also a popular technique in the control of Lagrangian system.\par
-Before giving out main results, some routine lemmas emerge in advance to support the derivation.
+To cope with the issue about bounded inputs, we develop the dynamic sliding mode control with the experience of the saturated manifold, which is also a popular technique in the control of Lagrangian system.\par
+Before giving out main results, some routine lemmas emerge in advance to support proceeding derivations.
 \begin{mylem}\label{lemma:1}
@@
 and it's notable that the function above is saturated and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$.
-The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-\Delta h,\Delta h]$, and once the function $y=Sine(x)+\Delta h$ settles, one can chose the function $y = x+arcsin(\Delta h)$ such that
+The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-\Delta h,\Delta h]$ with $\vert \Delta h \vert< 1$, and once the function $y=Sine(x)+\Delta h$ settles, one can chose the function $y = x+arcsin(\Delta h)$ such that
 \begin{align}
@@
 \begin{myrem}\textcolor{red}{Moreover, we think that a quantity $y$ or vector $\bm y$ is saturated iff it is produced directly by the saturated function $y=Sine(x)$ or $\bm y=\bm{Sine(x)}$.
-Otherwise, the bounded quantity is different from the saturated one since it does not own the standard formulation like $y=Sine(x)$, i.e., a quantity can just be said a bounded quantity if its boundary is $[a,b]$ with $a\neq -1$ or $b\neq 1$.}
+Otherwise, the bounded quantity is different from the saturated one since it does not own the standard formulation like $y=Sine(x)$, i.e., a quantity can just be referred to as a bounded quantity if its boundary is $[a,b]$ with $a\neq -1$ or $b\neq 1$.}
 \end{myrem}
@@
 \begin{mylem}\cite{Hu2008552}\label{lemma:2}
-Consider a limited function owning the subsequent property:
+Consider a bounded function owning the subsequent property:
 \begin{align}
@@
 \begin{myrem}
-As we know, \textcolor{red}{the tension, in-plane and out-of-plane thruster force are all limited during deployment mission, and we describe inputs by using the matrix and vector to predigest the following illation.}
+As we know, \textcolor{red}{the tension, in-plane and out-of-plane thruster force are all limited during the deployment mission, and we describe these inputs by using the matrix and vector to predigest the following illation.}
 \begin{align}
@@
 \end{myrem}
-The lemmas above introduce some properties about saturated functions, with which the dynamic sliding mode control subject to input limitation for Lagrangian system~(\ref{eq:dynamic model}) can be designed by using the subsequent theorem.
+The lemmas above introduce some properties about saturated functions, with which the dynamic sliding mode control subjected to input limitation for Lagrangian system~(\ref{eq:dynamic model}) can be designed by using the subsequent theorem.
 \begin{mythm}\label{thm:1}(Saturated sliding mode control)
-Considering a nominal Lagrangian system~(\ref{eq:dynamic model}) expressing the dynamics of the deployment of the TSS, one can construct a saturated sliding mode control subject to input limitation, as follows:
+Considering a nominal Lagrangian system~(\ref{eq:dynamic model}) expressing the dynamics of the deployment of the TSS, one can construct a saturated sliding mode control law subjected to the input limitation, as follows:
 \begin{align}
@@
 \textcolor{red}{$\varphi$ is the boundedness of the lumped uncertainty.
-$\gamma$ is designed as a time-varying positive scalar and $\varphi>1$ is the design parameter, so that the deployment dynamics can be regulated as desired.}
+$\gamma$ is designed as a time-varying positive scalar and $\delta>1$ is the design parameter, so that the deployment dynamics can be regulated as desired.}
 \end{mythm}
 \begin{proof}
-Consider dynamic coordinates change $\bm S_{r2}$ with the regular error variable but not the $Sine$ form:
+Consider the dynamic coordinate change $\bm S_{r2}$ with regular error vectors $\Delta \bm q$ and $\Delta\dot{\bm q}$:
 \begin{align}
@@
 \end{align}
-for a vector $\bm x=\left(x_1,x_2,\cdot,x_n\right)^T$.
+for a vector $\bm x=\left(x_1,x_2,\cdots,x_n\right)^T$.
 It is obvious that $\bm S_{q_1}$ is bounded, or exactly saturated, hence $\bm S_{r_1}$ is also bounded if the dynamics can be controlled as desired.
-\textcolor{red}{In addition, for guaranteeing that $\bm x=\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma$ always falls in the field of definition of $\bm y=arcsin(\bm x)$, $\gamma$ can be designed as a time-varying parameter
+\textcolor{red}{In addition, for guaranteeing that $\bm x=\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma$ always falls in the field of definition of $\bm y=\bm{arcsin}(\bm x)$, $\gamma$ can be designed as a time-varying parameter
     \begin{align}
@@
 \end{align}
-Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinates change $\bm S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $\bm S_{r2}$ holds results in the following expression:
+Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinate change $\bm S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $\bm S_{r2}$ holds results in the following expression:
 \begin{align}
-H(q)\dot {\bm S}_{r2} = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))-C(q,\dot q)\bm S_{r2}-Y_{r2}\Theta.
+H(q)\dot {\bm S}_{r2} = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm\tau_d-C(q,\dot q)\bm S_{r2}-Y_{r2}\bm\Theta.
 \end{align}
-Similar to Properties~\ref{pro:1}, one can find a positive scalar $\varphi_2$ such that $\Vert Y_{r2}\Theta\Vert\le\varphi_2$, and moreover the boundedness of the lumped uncertainty $\varphi$ satisfies $\varphi>\varphi_1+\varphi_2$.
+Similar to Properties~\ref{pro:1}, one can find a positive scalar $\varphi_2$ such that $\Vert Y_{r2}\bm\Theta\Vert\le\varphi_2$, and moreover the boundedness of the lumped uncertainty $\varphi$ satisfies $\varphi>\varphi_1+\varphi_2$.
 
@@
 \end{align}
-where $v=F(t)e^{K_1^{-1}F^{-1}(t)}$ and $\frac{1}{2}v^2$ is an auxiliary Lyapunov function with adaptive terms. Differentiating the Lyapunov function above
+where $v=F(t)e^{K_1^{-1}F^{-1}(t)}$ and $\frac{1}{2}v^2$ is an auxiliary Lyapunov function with adaptive terms. Differentiating the Lyapunov function above gives rise to
 \begin{align}
@@
 \dot V &= \bm S_{r2}^TH(q)\dot {\bm S}_{r2}+\frac{1}{2}\bm S_{r2}^T\dot H(q)\bm S_{r2}+v\dot v\\
-&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TC(q,\dot q)\bm S_{r2}+\frac{1}{2}\bm S_{r2}^T\dot H(q)\bm S_{r2}-\bm S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\Theta+\frac{1}{2}\bm S_{r2}^T(\dot H(q)-2C(q,\dot q))\bm S_{r2}+v\dot v\\
-&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\Theta+v\dot v\\
-&= -\bm S_{r2}^TR_M(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))\delta\varphi F(t) \bm{sign}(\bm S_{r1})+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{\bm r2}\Theta+v\dot v.\label{eq:V1_1}
+&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TC(q,\dot q)\bm S_{r2}+\frac{1}{2}\bm S_{r2}^T\dot H(q)\bm S_{r2}-\bm S_{r2}^TY_{r2}\bm\Theta+v\dot v\\
+&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\bm\Theta+\frac{1}{2}\bm S_{r2}^T(\dot H(q)-2C(q,\dot q))\bm S_{r2}+v\dot v\\
+&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\bm\Theta+v\dot v\\
+&= -\bm S_{r2}^TR_M(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))\delta\varphi F(t) \bm{sign}(\bm S_{r1})+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{\bm r2}\bm\Theta+v\dot v.\label{eq:V1_1}
 \end{split}
 \end{align}
-\textcolor{red}{Since the command $ -\delta\varphi F(t) \bm S_{r1}$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ which satisfy $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain a diagonal matrix as follows:}
+\textcolor{red}{Since the command input $ -\delta\varphi F(t) \bm {sign}(\bm{S}_{r1})$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ which satisfy $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain the diagonal matrix $K_1$ as follows:}
 \begin{align}
@@
 where a large enough $\delta>1$ can be selected to satisfy $\dot V \le 0$.
-According to the description of Barbalat¡¯s lemmas, we can conclude  that $\bm S_{r2}$ asymptotically converges to origin.
-Also, the finite convergent time of desired sliding surface can be calculated by referring to~\cite{Ma201667}.}\par
+According to the description of Barbalat's lemmas, we can conclude  that $\bm S_{r2}$ asymptotically converges to the origin.
+Also, the finite reaching time can be calculated by referring to~\cite{Ma201667}.}\par
 \textcolor{red}{Utilizing $\bm S_{r2}=0$ leads to the equation
@@
 \end{align}
-the derivative of which gives rise to
+and the derivative of which gives rise to
 \begin{align}
@@
 \textcolor{red}{For the adaptive sliding mode control with input limitation, the adaptive update rate $\frac{d}{dt}F(t)$ always helps to remove the side-effect of the input limitation during the stability analysis by using Lyapunov second method, and moreover, the actual examples of $F(t)$ are unhelpful to the theoretical derivation and the controller design~\cite{Hu2008552,6060930}.
-This is because we can search the actual value of $F(t)$  by the way of state updating from the initial condition $F(0)=0$, for instance, in our simulations, we applied ode45 technique to update states of the overall system including this adaptive update rate.}
+This is because we can search the actual value of $F(t)$  by the way of state updating from the initial condition $F(0)=0$, for instance, in our simulations, we apply Ode45 technique to update states of the overall system including this adaptive update rate.}
 \end{myrem}
-\subsection{Quasi-saturated terminal sliding mode control subject to input limitation}
-The design methodology of the saturated sliding mode control has been exhibited in last subsection, and the entire strict proof ensures that the dynamics of the deployment of the tethered satellite can be regulated with the limited tension control.
-Essentially, the method mentioned above is able to perform a limited sliding mode controller, since the order of the integrated error is one.
-If the order of the integrated error varies to become a fraction, the value of which is less than one, one establishes the terminal attractor like
+\subsection{Quasi-saturated terminal sliding mode control subjected to input limitation}
+The design methodology of the saturated sliding mode control has been exhibited in last subsection, and the entire strict proof ensures that the deployment dynamics of the TSS can be regulated with the limited tension control.
+If the order of the integrated error becomes a fraction, the value of which is less than one, we obtain the terminal attractor like
 \begin{align}
@@
 \begin{mythm}\label{thm:2}(Quasi-saturated terminal sliding mode control)
-Considering the dynamics of the deployment as described in Eq.~(\ref{eq:dynamic model}) with limited tension control, the quasi-saturated terminal sliding mode control input can be designed as follow:
+Considering the deployment dynamics of the TSS as described in Eq.~(\ref{eq:dynamic model}) with limited tension control, the quasi-saturated terminal sliding mode control input can be designed as follow:
 \begin{align}
@@
 \section{Simulation studies}\label{sec:4}
-This section presents the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively.
-The parameters of these controllers can be selected as follows: $\delta=1.1$, $\varphi= 1\times 10^{-3}$, $\alpha = 0.8$, $\gamma = 0.1$ and $\hat\alpha=0.6$.\par
-Besides the design parameter determined, the simulation initial and desired condition can be described as follows.
+This section presents the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control laws, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively.
+The parameters of these controllers can be selected as follows: $\delta=1.1$, $\varphi= 4$, $\varphi_1 = 1$, $\varphi_2= 2$, $\alpha = 0.8$ and $\hat\alpha=0.6$.\par
+Besides the design parameter determined, the simulation initial and desired conditions can be described as follows.
 The circular orbital altitude is selected around 260 $km$ approximately, and the orbital angular velocity is about $1.17\times 10^{-3}$ $rad/s$.
@@
 \textcolor{red}{As shown in Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, indicating the curves of the tether length climb more rapidly at the beginning.} However, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$.
-This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to origin earlier than S-SMC and QST-SMC.\par
+This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to the origin earlier than S-SMC and QST-SMC.\par
 \textcolor{red}{The in-plane and out-of-plane angles reflect the swing dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}.} For ST-SMC, the in-plane dynamics is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time.
-\textcolor{red}{Hence the coalition of the length and the swing dynamics implies that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC.} S-SMC makes the tether swing to desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
+\textcolor{red}{Hence the coalition of the length and the swing dynamics implies that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC.} S-SMC makes the tether swing to the desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
 The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) is exhibited in Figure~\ref{fig:6}, in which it is obvious that the limited situations occur frequently.
@@
 \textcolor{red}{So far, the proposed control laws have been verified in the undisturbed environment.
-However, space perturbations and parametric uncertainties usually occur during the deployment of the tethered satellite system in engineering application.
+However, space perturbations and parametric uncertainties usually occur during the deployment of the TSS in engineering application.
 For checking the robustness of the proposed control laws, based on the dynamics~(\ref{eq:dynamics 1}), we have the following assumptions about uncertainties and disturbances:
@@
 \section{Conclusion}\label{sec:5}
-In this paper, the error dynamics of the deployment of the TSS provides the adaptive sliding mode control with a simplified solution for the reaching phase, which ignores the nonlinear nature of the model, and the new dimensionless transformation subject to the limited input guarantees the effectiveness of the auxiliary Lyapunov function with adaptive terms.
-The simulation results show that the proposed methods adjust the length of the tether and the swinging dynamics as desired, although there exists the input limitation during the deployment.
-According to the results mentioned above, combining error dynamics design approach, adaptive approach and nonlinear sliding mode surface design technology may provide a further insight into regulation of the dynamics of the deployment of the tethered satellite system.
+In this paper, the error dynamics of the deployment of the TSS provides the adaptive sliding mode control with a simplified solution for the reaching phase, which ignores the nonlinear nature of the model, and the new dimensionless transformation subjected to the limited input guarantees the effectiveness of the auxiliary Lyapunov function with adaptive terms.
+The simulation results show that the proposed methods adjust the length of the tether and the swing dynamics as desired, although there exists the input limitation during the deployment.
+Also, the robustness to parametric uncertainties and external disturbances is verified reasonably.
+According to the results mentioned above, combining error dynamics design approach, adaptive approach and nonlinear sliding mode surface design technology may provide a further insight into regulation of the deployment dynamics of the TSS.
 \section{Acknowledgment}

### 2016-11-03 manuscript.tex
20161103

@@
 \section{Introduction}
-The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space exploration and scientific research, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}.
-\textcolor{red}{Many international space research institutes have launched some orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation design for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
+The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space explorations and scientific researches, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}.
+\textcolor{red}{Many international space research institutes have launched orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation schemes for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
 These experimental results intensively help researchers proceed to promote advanced mechanics, kinetic and control studies, to tackle the future challenges of space activities~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.}\par
 
-\textcolor{red}{Recent scientific researches about deployment of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.} Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the TSS.
+\textcolor{red}{Recent scientific researches about deployments of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.} Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the TSS.
 Iki et al.
-implemented the ground experiment of an electrodynamic tether deployment from a spool-type reel, and utilized the thruster to guarantee the deployment of kilometers-length space tether~\cite{iki2014experiments}.
+implemented the ground deployment experiment, and utilized the thruster to conduct the deployment of a kilometers-length electrodynamic tether from a special spool-type reel~\cite{iki2014experiments}.
 \textcolor{red}{Aslanov et al.
-presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thruster force acting on the tug~\cite{aslanov2013dynamics}.} Huang et al.
+presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thruster force acting on the tug~\cite{aslanov2013dynamics}.} Huang~et~al.
 investigated the attitude and deployment dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}.
 Jung et al.
-adopted thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}.
+adopted the thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}.
 \textcolor{red}{Liu et al.
 equipped the subsatellite with the thruster system, consisting of four pairs of thrusters, in order to regulate the attitude and deployment dynamics~\cite{liu2014attitude}.
-Zakrzhevskii divided the deployment process into two stages: in the first stage, the thruster was used to eject to the desired starting point of the next stage, and in the second stage, the tether was adjusted to the stable vertical configuration using tension generated by friction~\cite{zakrzhevskii2016method}.
+Zakrzhevskii divided the deployment process into two stages: in the first stage, the thruster was used to propel the subsatellite to the desired starting point of the next stage, and in the second stage, the tether was adjusted to the stable vertical configuration using tension generated by friction~\cite{zakrzhevskii2016method}.
 Mantellato et al.
-reported the thruster-aided deployment of tape tethers driven by both the tension and thruster force~\cite{mantellato2015thrust}.
+reported the thruster-aided deployment of tape tethers driven by both the tension and thruster forces~\cite{mantellato2015thrust}.
 These hybrid strategies has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, and thus is broadly utilized in engineering applications compared with other control strategies.}\par
 
-There also exist some obstacles in the hybrid control design.
+However, there also exist some obstacles in the hybrid control design.
 Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical conditions, i.e., the tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the space tether.
-Also, the thruster can not provide infinite force~\cite{martinez1998spacecraft}.
-Hence the tension and thruster force for the deployment/retrievial are both limited, and in the view of control theory, the phenomena usually causes the input limitation of a dynamic system.
+Also, the thruster can not provide the infinite propelling force~\cite{martinez1998spacecraft}.
+In simpler terms, the tension and thruster force for the tether deployment are both limited, and the view of control theory, the phenomena usually causes the input limitation of a dynamic system.
 Substituting limited inputs into unmodified conventional control scheme designed for systems with unlimited inputs results in poor performance or instability, and theoretically, such kind of implement is unreasonable.
-Hence to cope with input limitation in the TSS, many scientific researchers spent much effort on restricting input, providing many solutions on satellite arrangements and deployments.
+Hence to cope with the issues mentioned above, many scientific researchers spent much effort on the issue about input limitation of the TSS, providing many solutions on satellite arrangements and deployments.
 Huang et al.
-proposed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect of constrained input by using specific auxiliary design systems~\cite{huang2015adaptive}.
+proposed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect from constrained inputs by using specific auxiliary design systems~\cite{huang2015adaptive}.
 Wen et al.
-took into account the positive bounded tension constraint by designing the feedback control with special saturation technique~\cite{wen2016constrained}, and Wen also proposed some remarkable achievements using optimal control for deployment~\cite{wen2008optimal}.
+took into account the positive tension constraint by designing the feedback control with special saturation technique~\cite{wen2016constrained}, and Wen also proposed some remarkable achievements using optimal control for deployment~\cite{wen2008optimal}.
 Liu et al.

### 2016-11-03 manuscript.tex
20161104

@@
 However, there also exist some obstacles in the hybrid control design.
-Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical conditions, i.e., the tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the space tether.
+Particularly, it's a prime problem that tension actuators and thrusters are both constrained by physical and chemical conditions, i.e., the space tether is not available to be repressed like the stick, and meanwhile too big tether length rate might break the tether.
 Also, the thruster can not provide the infinite propelling force~\cite{martinez1998spacecraft}.
-In simpler terms, the tension and thruster force for the tether deployment are both limited, and the view of control theory, the phenomena usually causes the input limitation of a dynamic system.
+In simpler terms, the tension and the thruster force for the deployment are both limited, and in the view of control theory, the phenomena usually causes the input limitation of a dynamic system.
 Substituting limited inputs into unmodified conventional control scheme designed for systems with unlimited inputs results in poor performance or instability, and theoretically, such kind of implement is unreasonable.

### 2016-11-04 manuscript.tex
20161104

@@
 Substituting limited inputs into unmodified conventional control scheme designed for systems with unlimited inputs results in poor performance or instability, and theoretically, such kind of implement is unreasonable.
-Hence to cope with the issues mentioned above, many scientific researchers spent much effort on the issue about input limitation of the TSS, providing many solutions on satellite arrangements and deployments.
+Hence to cope with the issues mentioned above, many scientific researchers spent much effort on the issue about the input limitation, providing many solutions on satellite arrangements and deployments.
 Huang et al.
-proposed an adaptive postcapture backstepping control of the tethered space robot, and analyzed the effect from constrained inputs by using specific auxiliary design systems~\cite{huang2015adaptive}.
+proposed an adaptive postcapture backstepping control law for the tethered space robot, and analyzed the effect from constrained inputs by using specific auxiliary design systems~\cite{huang2015adaptive}.
 Wen et al.
-took into account the positive tension constraint by designing the feedback control with special saturation technique~\cite{wen2016constrained}, and Wen also proposed some remarkable achievements using optimal control for deployment~\cite{wen2008optimal}.
+took into account the positive tension constraint and designed the feedback control with the special saturation technique~\cite{wen2016constrained}.
+Wen also proposed some remarkable achievements about deployment dynamics using the optimal control theory~\cite{wen2008optimal}.
 Liu et al.
-reported the variable structure scheme for the deployment with thruster control, where the thruster is used to guarantee the positive tension during the mission~\cite{yingying2012variable}.
+reported the variable structure scheme for the deployment with the special structural thruster system, where the thrusters were used to ensure the positive tension during the mission~\cite{yingying2012variable}.
 In summary, existing studies deal with the major issue about the deployment with restricted tension and thruster force in two ways, accordingly, the suitable physical compensation and the elaborate design of limited input.
 In aspect of designing elaborate limited inputs, as Wen et al.
-explained, the limited terms, including the tension and the states of deployment dynamics, can be viewed as the solution of a nonlinear optimal control issue~\cite{wen2015tension}.
-\textcolor{red}{Hu reported an adaptive sliding mode control law with saturated input by using reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the TSS is studied.
-For coping with the input saturation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function.
-Based on the feature of the saturated command, an adaptive rate is introduced into the controller design to remove the effect of the input limitation theoretically.
+explained, the limited terms, including the tension and the states of deployment dynamics, can be viewed as seeking the solution of a nonlinear optimal control issue~\cite{wen2015tension}.
+\textcolor{red}{Hu reported an adaptive sliding mode control law with the input limitation by using the reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the TSS is studied.
+For coping with the input limitation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function.
+Based on the feature of the saturated command signal, an adaptive rate is introduced into the control law design to remove the negative effect of the input limitation theoretically.
 In order to improve the performance of the sliding phase, the terminal attractor is incorporated into the design of the ideal sliding surface.
-We perform numerical simulations to illustrate that the stabilization of the deployment is accomplished by the controller designed in spite of the input limitation.\par
+We perform numerical simulations to illustrate that the stabilization of the deployment is accomplished by the control law designed in spite of the input limitation.\par
 The paper is organized as follows: Section~\ref{sec:2} introduces the standard mathematical model of the deployment of the TSS.
@@
 \textcolor{red}{Figure \ref{fig:1} shows all the elements of the TSS via the geometric representation.
-In the figure, the axes of the coordinate frame of $OXYZ$ passes through the center of the earth.
+In the figure, the axes of the coordinate frame $OXYZ$ passes through the center of the earth $O$.
 $OX$ and $OY$ are mutually perpendicular axes on the equatorial plane with $OX$ pointing to the spring equinox, and $OZ$ is perpendicular to the equatorial plane, bundling the axis of the earth upwards.
@@
 Actually, the mass ratio between the subsatellite and the mother satellite is tiny, i.e., in YES2, the mother satellite mass is 6530~$kg$, and the subsatellite mass is 12~$kg$~\cite{Williams2008}.
-The deployment of the subsatellite will not affect the motion of the mother satellite due to the tiny mass ratio between the satellites and will keep the nominal orbit during the whole mission.} The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
+Owing to the tiny mass ratio between the satellites, the deployment of the subsatellite will not affect the motion of the mother satellite during the whole mission.} The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
 Symbols used in the model are defined as follows.
@@
 %\end{align}
-Based on the assumption above and Lagrangian mechanics theory, we can directly obtain the following expression for the TSS~\cite{Sun2014304,Mantellato2015}
+Based on the assumption mentioned above and Lagrangian mechanics theory, we can directly obtain the following expression for the TSS~\cite{Sun2014304,Mantellato2015}
 \begin{align}
@@
 For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
-$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster force and the out-of-plane thruster force, respectively, and $\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment/retrieval scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
+$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster force and the out-of-plane thruster force, respectively, and $\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
 \begin{align}
@@
 From~(\ref{eq:varcon0}), it is easy to find that the boundedness of $\hat{\tau}_{t0}$ is different from $\hat{\tau}_\theta$'s and $\hat{\tau}_\phi$'s, since $\hat{\tau}_{t0}$ just owns the negative boundedness due to positive $\tau_t$.
-However, this issue doesn't conform to conventional hypotheses about input saturation, i.e., for adaptive sliding mode controller design, $\hat{\tau}_{t0}$ doesn't fulfil the requirement of transformation of limited inputs, leading to the nonrigorous stability analysis~\cite{Hu2008552,6060930}.
+However, this issue doesn't conform to conventional hypotheses about input saturation, i.e., for adaptive sliding mode control law design, $\hat{\tau}_{t0}$ doesn't fulfil the requirement of transformation of limited inputs, leading to the nonrigorous stability analysis~\cite{Hu2008552,6060930}.
 To cope better with the missing positive boundedness, we initiatively introduce the dimensionless length $\lambda$ into the dimensionless tension to establish a reasonable positive boundedness, and hence general limited inputs are produced by the novel dimensionless transformations:
@@
 The obvious benefits of these transformations are that all the inputs own the positive and negative boundedness and hence satisfy the assumption about limited inputs of existing control laws~\cite{Hu2008552,6060930}.
-The obtained inputs also essentially guarantee the rigorous stability analysis of the proposed sliding mode control in this paper.
-Based on the novel dimensionless transformations, Eq.~(\ref{eq:dynamics 1}) can be converted into the dimensionless Euler-Lagrange dynamical equation described as follows:}
+Furthermore, the generalized inputs~(\ref{eq:varcon}) can be processed by the proposed Sine function in this paper to yield the strict saturated inputs, which essentially guarantee the rigorous stability analysis of the proposed adaptive sliding mode control law.}
+
+Based on the novel dimensionless transformations~(\ref{eq:varcon}), Eq.~(\ref{eq:dynamics 1}) can be converted into the dimensionless Euler-Lagrange dynamical equation described as follows:
 \begin{align}
@@
 
-For the deployment or retrieval mission, the following expression always exists,
+For the deployment mission, the following expression always exists,
 \begin{align}
@@
 \end{align}
-\textcolor{red}{In reality, once $\lambda = 0$ is satisfied, the mother satellite and subsatellite will collide with each other.
+\textcolor{red}{In reality, once $\lambda = 0$ is satisfied, the mother satellite and subsatellite will collide with each other, which is meaningless for the deployment of the TSS.
 Hence the minimum of the dimensionless length $\lambda_{min}$ is introduced to maintain the reasonably safe formation of the satellites, and also guarantees the non-singularity of the dimensionless transformation~(\ref{eq:dynamics 1}) theoretically.} $\lambda_{max}$ stands for the maximum tether length ratio.\par
 The tension acting on the space tether is a positive scalar during the deployment, since zero tension means slack, which is inconsistent with the fundamental assumption that the tether is stiff in the ``rolling ball'' model.
-$\tau_{tmax}$ denotes the maximum tensile tolerance of the tether, and $\tau_t>\tau_{tmax}$ may leads to the break of the tether.
+$\tau_{tmax}$ denotes the maximum tensile tolerance of the tether, and $\tau_t>\tau_{tmax}$ may lead to the break of the tether.
 Hence, $\tau_{tmin}$ can be a small value to guarantee the stiff tether, and reasonable $\tau_{tmax}$\ prevents the fracture of the tether.
 \end{myrem}
-This section have established the deployment dynamics with input limitation and an adaptive saturated sliding mode  control will be presented in the subsequent section.
-\section{Dynamic sliding mode control subjected to input limitation}\label{sec:3}
-Before declaring the controller design, some basic preconditions are prepared for proceeding derivation.
+This section have established the deployment dynamics with the input limitation and an adaptive saturated sliding mode control law will be presented in the subsequent section.
+\section{Dynamic sliding mode control law subjected to input limitation}\label{sec:3}
+Before declaring the control law design, some basic preconditions are prepared for proceeding derivations.
 The left side of Eq.~(\ref{eq:dynamic model}) can be denoted by the linearly parametrization $Y\Theta$, in which $Y=Y(\bm q,\dot {\bm q},\ddot {\bm q})$ consists of known nonlinear functions.
@@
 for a vector $\bm x=\left(x_1,x_2,,\cdots,x_n\right)^T$.
-$\alpha$ and $\gamma$ are controller parameters which will be discussed in the controller design.
+$\alpha$ and $\gamma$ are control law parameters which will be discussed in the control law design.
 Define the tracking error as $\Delta \bm q=\bm q-\bm q_d$, in which $\bm q_d$ is the desired trajectory with $\bm q_d(t)\in C^2$.
@@
 where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively.
-Furthermore, one can have $Y_r\bm\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta \bm q,\Delta \dot {\bm q},\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\bm\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi_0$, in which $\varphi_0$ is a positive scalar determined according to the system states.}
+Furthermore, one can have $Y_r\bm\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta \bm q,\Delta \dot {\bm q},\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\bm\Theta$ is usually thought to be a bounded function with $\vert\eta\vert\le\varphi_0$, where $\varphi_0$ is a positive scalar determined according to the system states.}
 \end{mypro}
@@
 \textcolor{red}{
-In the low orbit altitude, the external disturbance $\bm\tau_d$ contains gravity gradient torque, aerodynamic interference and solar radiation pressure torque.
-According to existing studies, the values of the solar radiation pressure and the aerodynamic torque are about $1\times10^{-5}$ Nm, and meanwhile the gradient torque is in the range of $1\times10^{-5}$ Nm.
+In the low orbit altitude, the external disturbance $\bm\tau_d$ contains the gravity gradient torque, the aerodynamic interference and the solar radiation pressure torque.
+Thanks to existing studies, the values of the solar radiation pressure and the aerodynamic torque are about $1\times10^{-5}$ Nm, and meanwhile the gradient torque is in the range of $1\times10^{-5}$ Nm.
 The space perturbation can be specifically regarded as the periodic function in this paper, and the period equals the orbital period $5000$ s~\cite{Inamori2015192}.
@@
 \end{myas}
-\subsection{Saturated sliding mode control subjected to input limitation}
-The process above can frame a conventional dynamic sliding PID control scheme, which can regulate the dynamics of n-link robotic manipulator if the dimension in the derivation above is extended~\cite{parra2003dynamic}.
+\subsection{Saturated sliding mode control law subjected to input limitation}
+The process above can frame a conventional dynamic sliding PID controller, which can regulate the dynamics of n-link robotic manipulator if the dimension in the above derivation  is extended~\cite{parra2003dynamic}.
 However, it is not possible to regulate the dynamics of the deployment as desired theoretically, because the input $\tau$ in the PID controller is not confined to the characteristics of the tension.
-To cope with the issue about bounded inputs, we develop the dynamic sliding mode control with the experience of the saturated manifold, which is also a popular technique in the control of Lagrangian system.\par
+To cope with the issue about bounded inputs, we develop the dynamic sliding mode control law with the experience of the saturated manifold, which is also a popular technique in the control of Lagrangian system.\par
 Before giving out main results, some routine lemmas emerge in advance to support proceeding derivations.
@@
 and it's notable that the function above is saturated and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$.
-The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-\Delta h,\Delta h]$ with $\vert \Delta h \vert< 1$, and once the function $y=Sine(x)+\Delta h$ settles, one can chose the function $y = x+arcsin(\Delta h)$ such that
+The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-1,1]$, and once the function $y=Sine(x)+\Delta h$ with $\vert\Delta h\vert<1$ settles, one can chose the function $y = x+arcsin(\Delta h)$ to obtain following relations:
 \begin{align}
@@
 \begin{cases}
-y' = -1,&x\ge\pi/2,x\le-\pi/2\\
-y' = \cos x - 1,&\vert x\vert<\pi/2,
+dy/dx = -1,&x\ge\pi/2,x\le-\pi/2\\
+dy/dx = \cos x - 1,&\vert x\vert<\pi/2,
 \end{cases}
 \end{align}
-where $y'<0$ means $y$ is a monotone decreasing function. As $x=-arcsin(\Delta h)$, $y=0$, according to the definition of $Sine(x)$, we proceed to get
+where $dy/dx<0$ means $y$ is a monotone decreasing function with respect to $x$. As $x=-arcsin(\Delta h)$, $y=0$, according to the definition of $Sine(x)$, we proceed to get
 $$\left.
@@
 \end{proof}
-\begin{myrem}\textcolor{red}{Moreover, we think that a quantity $y$ or vector $\bm y$ is saturated iff it is produced directly by the saturated function $y=Sine(x)$ or $\bm y=\bm{Sine(x)}$.
+\begin{myrem}\textcolor{red}{Moreover, we think that a quantity $y$ is saturated iff it is produced directly by the saturated function $y=Sine(x)$.
 Otherwise, the bounded quantity is different from the saturated one since it does not own the standard formulation like $y=Sine(x)$, i.e., a quantity can just be referred to as a bounded quantity if its boundary is $[a,b]$ with $a\neq -1$ or $b\neq 1$.}
@@
 \begin{myrem}
-As we know, \textcolor{red}{the tension, in-plane and out-of-plane thruster force are all limited during the deployment mission, and we describe these inputs by using the matrix and vector to predigest the following illation.}
+As we know, \textcolor{red}{the tension, in-plane and out-of-plane thruster forces are all limited during the deployment mission, and we describe these inputs by using the matrix and vector to predigest the following illation.}
 \begin{align}
-\bm{g}(\tau) &= \left(g(\hat\tau_t),g(\hat\tau_\theta),g(\hat\tau_\phi)\right)^T\\
-R_M(\tau) &= \begin{bmatrix}R(\hat\tau_t)&0&0\\0&R(\hat\tau_\theta)&0\\0&0&R(\hat\tau_\phi)\end{bmatrix}.
+\bm{g}(\bm\tau) &= \left(g(\hat\tau_t),g(\hat\tau_\theta),g(\hat\tau_\phi)\right)^T\\
+R_M(\bm\tau) &= \begin{bmatrix}R(\hat\tau_t)&0&0\\0&R(\hat\tau_\theta)&0\\0&0&R(\hat\tau_\phi)\end{bmatrix}.
 \end{align}
-and in order to design the saturated sliding mode  control for the dynamics of the deployment, the $Sine$ function for vectors is specified as:
+and in order to design the saturated sliding mode control law for the dynamics of the deployment, the $Sine$ function for vectors is specified as:
 \begin{align}
@@
 \end{myrem}
-The lemmas above introduce some properties about saturated functions, with which the dynamic sliding mode control subjected to input limitation for Lagrangian system~(\ref{eq:dynamic model}) can be designed by using the subsequent theorem.
-\begin{mythm}\label{thm:1}(Saturated sliding mode control)
+The above lemmas introduce some properties about saturated functions, with which the dynamic sliding mode control law subjected to the input limitation for Lagrangian system~(\ref{eq:dynamic model}) can be designed by using the subsequent theorem.
+\begin{mythm}\label{thm:1}(Saturated sliding mode control law)
 Considering a nominal Lagrangian system~(\ref{eq:dynamic model}) expressing the dynamics of the deployment of the TSS, one can construct a saturated sliding mode control law subjected to the input limitation, as follows:
@@
 for a vector $\bm x=\left(x_1,x_2,\cdots,x_n\right)^T$.
-It is obvious that $\bm S_{q_1}$ is bounded, or exactly saturated, hence $\bm S_{r_1}$ is also bounded if the dynamics can be controlled as desired.
+It is obvious that $\bm S_{q_1}$ is exactly saturated, hence $\bm S_{r_1}$ is also bounded if the dynamics can be controlled as desired.
 \textcolor{red}{In addition, for guaranteeing that $\bm x=\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma$ always falls in the field of definition of $\bm y=\bm{arcsin}(\bm x)$, $\gamma$ can be designed as a time-varying parameter
@@
     where $\gamma_0$ can be selected as $\gamma_0=0.1$.}\par
-According to Lemma~\ref{lemma:1}, it is apparent that $\bm S_{r2}$ and $\bm S_{r1}$ have the subsequent relation:
+According to Lemma~\ref{lemma:1}, it is apparent that $\bm S_{r2}$ and $\bm S_{r1}$ have the subsequent relations:
 \begin{align}
@@
 \end{align}
-Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinate change $\bm S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $\bm S_{r2}$ holds results in the following expression:
+Replacing the dynamic coordinate change $\bm S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $\bm S_{r2}$ results in the following expression:
 \begin{align}
@@
 \end{align}
-where $v=F(t)e^{K_1^{-1}F^{-1}(t)}$ and $\frac{1}{2}v^2$ is an auxiliary Lyapunov function with adaptive terms. Differentiating the Lyapunov function above gives rise to
+where $v=F(t)e^{K_1^{-1}F^{-1}(t)}$. Differentiating the Lyapunov function above gives rise to
 \begin{align}
@@
 \end{align}
-\textcolor{red}{Since the command input $ -\delta\varphi F(t) \bm {sign}(\bm{S}_{r1})$ is bounded, one can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ which satisfy $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain the diagonal matrix $K_1$ as follows:}
+\textcolor{red}{Since the command signal $ \bm\tau_c=-\delta\varphi F(t) \bm {sign}(\bm{S}_{r1})$ is bounded, we can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ which satisfy $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain the diagonal matrix $K_1$ as follows:}
 \begin{align}
@@
 \end{align}
-considering $\bm{sign}(\bm S_{r1})=\bm{sign}(\bm S_{r2})$ and $K_1$, we can proceed to rewrite Eq.~(\ref{eq:V1_1}) as:
+considering $\bm{sign}(\bm S_{r1})=\bm{sign}(\bm S_{r2})$, we can proceed to rewrite Eq.~(\ref{eq:V1_1}) as:
 \begin{align}
@@
 \begin{myrem}
-\textcolor{red}{For the adaptive sliding mode control with input limitation, the adaptive update rate $\frac{d}{dt}F(t)$ always helps to remove the side-effect of the input limitation during the stability analysis by using Lyapunov second method, and moreover, the actual examples of $F(t)$ are unhelpful to the theoretical derivation and the controller design~\cite{Hu2008552,6060930}.
+\textcolor{red}{For the adaptive sliding mode control law with input limitation, the adaptive update rate $\frac{d}{dt}F(t)$ always helps to remove the side-effect of the input limitation during the stability analysis by using Lyapunov second method, and moreover, the actual examples of $F(t)$ are unhelpful to the theoretical derivation and the control law design~\cite{Hu2008552,6060930}.
 This is because we can search the actual value of $F(t)$  by the way of state updating from the initial condition $F(0)=0$, for instance, in our simulations, we apply Ode45 technique to update states of the overall system including this adaptive update rate.}
 \end{myrem}
-\subsection{Quasi-saturated terminal sliding mode control subjected to input limitation}
-The design methodology of the saturated sliding mode control has been exhibited in last subsection, and the entire strict proof ensures that the deployment dynamics of the TSS can be regulated with the limited tension control.
+\subsection{Quasi-saturated terminal sliding mode control law subjected to input limitation}
+The design methodology of the saturated sliding mode control law has been exhibited in last subsection, and the entire strict proof ensures that the deployment dynamics of the TSS can be regulated with the limited tension control.
 If the order of the integrated error becomes a fraction, the value of which is less than one, we obtain the terminal attractor like
@@
 \textcolor{red}{where $0<\hat \alpha<1$, performs the same behavior.
-Putting the terminal attractor into the saturated sliding mode control yields a saturated slider-like scheme, and before introducing the input limitation into the system, an assumption is given firstly.}
+Putting the terminal attractor into the saturated sliding mode control law yields a saturated slider-like scheme, and before introducing the input limitation into the system, an assumption is given firstly.}
 \begin{myas}\label{as:1}
@@
 \end{myas}
-\begin{mythm}\label{thm:2}(Quasi-saturated terminal sliding mode control)
+\begin{mythm}\label{thm:2}(Quasi-saturated terminal sliding mode control law)
 Considering the deployment dynamics of the TSS as described in Eq.~(\ref{eq:dynamic model}) with limited tension control, the quasi-saturated terminal sliding mode control input can be designed as follow:
@@
 \begin{myrem}
-If the design parameter $\hat\alpha = 1$, the quasi-saturated terminal sliding mode control degenerates into the quasi-saturated sliding mode control.
-Compared with the saturated sliding mode control, $\bm S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method.
+If the design parameter $\hat\alpha = 1$, the quasi-saturated terminal sliding mode control law degenerates into the quasi-saturated sliding mode control law.
+Compared with the saturated sliding mode control law, $\bm S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method.
 This is because the establishment of the equation $\dot {\bm S}_{q3} = \gamma\vert \bm S_{q3}\vert^{\hat\alpha} \bm{ sign}(\bm S_{q3})$.
@@
 \textcolor{red}{Assumption~\ref{as:1} guarantees that the input $\tau$ is bounded in Theorem~\ref{thm:2}, accordingly, a tiny positive scalar $c$ can be found to ensure that $0<c\le R(\hat\tau_t)<1$ always exists.} Admittedly, such kind of assumption is ''skillful'', but meaningful to arbitrary controllable dynamics in reality.
-It is reasonable to propose the terminal sliding mode control for the dynamics as follows:
+It is reasonable to propose the terminal sliding mode control law for the dynamics as follows:
 \begin{align}
@@
 \section{Simulation studies}\label{sec:4}
-This section presents the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control laws, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively.
-The parameters of these controllers can be selected as follows: $\delta=1.1$, $\varphi= 4$, $\varphi_1 = 1$, $\varphi_2= 2$, $\alpha = 0.8$ and $\hat\alpha=0.6$.\par
+This section presents the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control laws, and for clarity, these control laws are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively.
+The parameters of these control laws can be selected as follows: $\delta=1.1$, $\varphi= 4$, $\varphi_1 = 1$, $\varphi_2= 2$, $\alpha = 0.8$ and $\hat\alpha=0.6$.\par
 Besides the design parameter determined, the simulation initial and desired conditions can be described as follows.
@@
 Meanwhile, the initial deployment velocity is about 3 $m/s$, and the subsatellite is going to be deployed at 3.5 $km$ vertically.
-\textcolor{red}{The pitch and roll dynamics is varying in a small range, and hence, without loss of generality, the numerical initial condition gives rise to: $\theta_0 = 0.1$, $\phi_0 = 0.1$, $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$.
-Hence the dimensionless tether length is in the range of $[0.02,1]$.}\par
+\textcolor{red}{The pitch and roll dynamics are both varying in a small range, and hence, without loss of generality, the numerical initial conditions are designed as $\theta_0 = 0.1$, $\phi_0 = 0.1$ and $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$.
+Hence the dimensionless tether length is varying in the range of $[0.02,1]$.}\par
 During the deployment, the dimensionless thruster forces which manage the in-plane angle and the out-of-plane angle are assumed to be saturated with $\vert\hat\tau_{\theta}\vert\le5 $ and $\vert\hat\tau_{\phi}\vert\le 5$.
-Also, the dimensionless tension $\hat\tau_t$ is limited, and from Eq.~(\ref{eq:varcon}), one can obtain
+Also, the dimensionless tension $\hat\tau_t$ is limited, and from Eq.~(\ref{eq:varcon}), we can obtain
 \begin{align}
@@
 Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that all the methods can realize the deployment in aspect of the tether length.} ST-SMC and QST-SMC complete the deployment at about 4 $rad$.
-\textcolor{red}{As shown in Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, indicating the curves of the tether length climb more rapidly at the beginning.} However, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$.
+\textcolor{red}{As shown in Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, indicating the curves of the tether length climb more rapidly at the beginning of the deployment.} However, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$.
 This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to the origin earlier than S-SMC and QST-SMC.\par
-\textcolor{red}{The in-plane and out-of-plane angles reflect the swing dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}.} For ST-SMC, the in-plane dynamics is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time.
-\textcolor{red}{Hence the coalition of the length and the swing dynamics implies that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC.} S-SMC makes the tether swing to the desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
-The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) is exhibited in Figure~\ref{fig:6}, in which it is obvious that the limited situations occur frequently.
+\textcolor{red}{The in-plane and out-of-plane angles reflect the swing dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}.} For ST-SMC, the in-plane dynamic motion is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time.
+\textcolor{red}{Hence the coalition of the length and the swing dynamics imply that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC.} S-SMC makes the tether swing to the desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
+The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) are exhibited in Figure~\ref{fig:6}, in which it is obvious that the limited situations occur frequently.
 Thanks to the scalable dimensionless transformation determined conservatively, the tension exerted on the tether falls in the reasonable region.\par
@@
 \includegraphics[width=0.6\textwidth]{paper4_fig5.eps}
-\caption{Angle dynamics of the deployment}
+\caption{Swing dynamics of the deployment}
 \label{fig:5}
@@
 \begin{align}\begin{split}
-\frac{1}{2}&\le\frac{\hat{\bar m}}{\bar m}\le 2\\
-\frac{1}{2}&\le\frac{\hat L}{L}\le 2\\
-\frac{1}{2}&\le\frac{\hat \Omega}{\Omega}\le 2\\
+\frac{1}{\varpi}&\le\frac{\hat{\bar m}}{\bar m}\le \varpi\\
+\frac{1}{\varpi}&\le\frac{\hat L}{L}\le \varpi\\
+\frac{1}{\varpi}&\le\frac{\hat \Omega}{\Omega}\le \varpi\\
 \bm\tau_d&=\left(0.05\sin(2\pi t/5000),0.05\sin(2\pi t/5000),0.05\sin(2\pi t/5000)\right)^T,
@@
 where $\hat\bullet$ stands for the measurement of the term $\bullet$ with uncertainties, and $\bm\tau_d$ is the external disturbance meaning  space perturbations, such as gravity gradient torque, aerodynamic interference and solar radiation pressure torque.
+$\varpi$ is the uncertainty boundary parameter, and here we select $\varpi=2$.
 In this simulation, the measured terms can be specified as: $\hat{\bar m}=1.1\bar m$ may mean some space debris affixed to the subsatellite; $\bar L=1.02L$ and $\bar \Omega=0.98\Omega$ mean some measurement errors happening to the total length and the orbital angular velocity.
-In Fig~\ref{fig:6}, although the dynamics has been already stable, the tension is switching in the high frequency.
-It is commonplace in sliding mode controller design, called chattering, since the signum function is used in the input, which may cause unmodelled high frequency dynamics, and for removing chattering, the boundary layer technique is introduced into the proposed control laws through replacing $sign(x)$ by $sat(x/\nu)$, where
+In Fig~\ref{fig:6}, although the dynamics have been already stable, the tension is switching in the high frequency.
+It is commonplace in the sliding mode control law design, called chattering, since the signum function is used in the input, which may cause unmodelled high frequency dynamics, and for reducing the chattering, we introduce the boundary layer technique into the proposed control laws through replacing $sign(x)$ by $sat(x/\nu)$, where
 \begin{align}
@@
 \end{align}
-and $\nu$ is the thickness of the boundary layer specified as a positive scalar $\nu=1\times 10^{-4}$ in this simulation.}\par
+and $\nu$ is the thickness of the boundary layer specified as a positive scalar $\nu=1\times 10^{-4}$ in this simulation~\cite{1039802}.}\par
 \textcolor{red}{
 The simulation results of the deployment dynamics subjected to uncertainties are exhibited from Fig~\ref{fig:7} to Fig~\ref{fig:10}.
-In Fig~\ref{fig:7}, although there exist parametric uncertainties compared with Figs~\ref{fig:7}-\ref{fig:9}, QST-SMC still performs the deployment with the shortest rise time and the minimum overshoot among the three methods, and the tethers are deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}.
-In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is eliminated by utilizing the boundary layer technique.
-Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to uncertainties and disturbances.}
+In Fig~\ref{fig:7}, although there exist parametric uncertainties compared with the dynamics in Figs~\ref{fig:3}-\ref{fig:6}, QST-SMC still performs the deployment with the shortest rise time and the minimum overshoot among the three methods, and the tether is deployed to the desired position at about 8 $rad$ by observing the dynamics of the in-plane and out-of-plane angles from Fig~\ref{fig:9}.
+In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is reduced by utilizing the boundary layer technique.
+Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to parametric uncertainties and external disturbances.}
 \begin{figure}
@@
 \includegraphics[width=0.6\textwidth]{paper4_fig9_20161025.eps}
-\caption{Angle dynamics of the deployment subjected to uncertainties and disturbances}
+\caption{Swing dynamics of the deployment subjected to uncertainties and disturbances}
 \label{fig:9}
@@
 \section{Conclusion}\label{sec:5}
-In this paper, the error dynamics of the deployment of the TSS provides the adaptive sliding mode control with a simplified solution for the reaching phase, which ignores the nonlinear nature of the model, and the new dimensionless transformation subjected to the limited input guarantees the effectiveness of the auxiliary Lyapunov function with adaptive terms.
+In this paper, the proposed adaptive sliding mode control laws provide the deployment dynamics of the TSS with a simplified solution for the reaching phase, which ignores the nonlinear nature of the model, and the new dimensionless transformation subjected to the limited input guarantees the effectiveness of the auxiliary Lyapunov function with adaptive terms.
 The simulation results show that the proposed methods adjust the length of the tether and the swing dynamics as desired, although there exists the input limitation during the deployment.

### 2016-11-04 manuscript.tex
20161104

@@
 However, this issue doesn't conform to conventional hypotheses about input saturation, i.e., for adaptive sliding mode control law design, $\hat{\tau}_{t0}$ doesn't fulfil the requirement of transformation of limited inputs, leading to the nonrigorous stability analysis~\cite{Hu2008552,6060930}.
-To cope better with the missing positive boundedness, we initiatively introduce the dimensionless length $\lambda$ into the dimensionless tension to establish a reasonable positive boundedness, and hence general limited inputs are produced by the novel dimensionless transformations:
+To cope better with the missing positive boundedness, we initiatively introduce the dimensionless length $\lambda$ into the dimensionless tension to establish a reasonable positive boundedness, and hence limited generalized inputs are produced by the novel dimensionless transformations:
 \begin{align}
@@
 \end{split}\end{align}
-where $\hat\bullet$ stands for the measurement of the term $\bullet$ with uncertainties, and $\bm\tau_d$ is the external disturbance meaning  space perturbations, such as gravity gradient torque, aerodynamic interference and solar radiation pressure torque.
+where $\hat\bullet$ stands for the measurement of the term $\bullet$ with uncertainties.
 $\varpi$ is the uncertainty boundary parameter, and here we select $\varpi=2$.
+$\bm\tau_d$ is the external disturbance meaning  space perturbations, such as gravity gradient torque, aerodynamic interference and solar radiation pressure torque.
 In this simulation, the measured terms can be specified as: $\hat{\bar m}=1.1\bar m$ may mean some space debris affixed to the subsatellite; $\bar L=1.02L$ and $\bar \Omega=0.98\Omega$ mean some measurement errors happening to the total length and the orbital angular velocity.

### 2016-11-06 manuscript.tex
20161106

@@
 For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
-$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster force and the out-of-plane thruster force, respectively, and $\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
+$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster force and the out-of-plane thruster force, respectively.
+$\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
 \begin{align}
@@
 \end{myrem}
-This section have established the deployment dynamics with the input limitation and an adaptive saturated sliding mode control law will be presented in the subsequent section.
+This section has established the deployment dynamics with the input limitation and an adaptive saturated sliding mode control law will be presented in the subsequent section.
 \section{Dynamic sliding mode control law subjected to input limitation}\label{sec:3}
@@
 \end{align}
-\textcolor{red}{For the system~(\ref{eq:dynamic model 2}) with ignoring the input limitation, the author in \cite{parra2003dynamic} has designed a nonlinear dynamic sliding PID controller with the zero initial condition:
+\textcolor{red}{For the system~(\ref{eq:dynamic model 2}) with the input limitation ignored, the author in \cite{parra2003dynamic} has designed a nonlinear dynamic sliding PID controller with the zero initial condition:
 \begin{align}\begin{split}
@@
 \textcolor{red}{
-In the low orbit altitude, the external disturbance $\bm\tau_d$ contains the gravity gradient torque, the aerodynamic interference and the solar radiation pressure torque.
+In low-altitude orbit , the external disturbance $\bm\tau_d$ contains the gravity gradient torque, the aerodynamic interference and the solar radiation pressure torque.
 Thanks to existing studies, the values of the solar radiation pressure and the aerodynamic torque are about $1\times10^{-5}$ Nm, and meanwhile the gradient torque is in the range of $1\times10^{-5}$ Nm.
@@
 \end{align}
-Therefore, the bounded external disturbance satisfy
+Therefore, the bounded external disturbance satisfies
 \begin{align}
@@
 and it's notable that the function above is saturated and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$.
-The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-1,1]$, and once the function $y=Sine(x)+\Delta h$ with $\vert\Delta h\vert<1$ settles, one can chose the function $y = x+arcsin(\Delta h)$ to obtain following relations:
+The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-1,1]$, and once the function $y=Sine(x)+\Delta h$ with $\vert\Delta h\vert<1$ settles, one can choose the function $y = x+arcsin(\Delta h)$ to obtain following relations:
 \begin{align}
@@
 In this simulation, the measured terms can be specified as: $\hat{\bar m}=1.1\bar m$ may mean some space debris affixed to the subsatellite; $\bar L=1.02L$ and $\bar \Omega=0.98\Omega$ mean some measurement errors happening to the total length and the orbital angular velocity.
-In Fig~\ref{fig:6}, although the dynamics have been already stable, the tension is switching in the high frequency.
+In Fig~\ref{fig:6}, although the dynamics have already been  stable, the tension is switching in the high frequency.
 It is commonplace in the sliding mode control law design, called chattering, since the signum function is used in the input, which may cause unmodelled high frequency dynamics, and for reducing the chattering, we introduce the boundary layer technique into the proposed control laws through replacing $sign(x)$ by $sat(x/\nu)$, where

### 2016-11-23 manuscript.tex
20161107
20161123

@@
 This paper presents a novel adaptive dynamic sliding mode scheme for the deployment of the tethered satellite system.
-\textcolor{red}{To overcome the limited inputs of the dynamic model, a new scalable dimensionless transformation and strictly bounded terms are designed, which guarantee the existence of the ratio between limited inputs and command signals.} The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain.
+To overcome the limited inputs of the dynamic model, a new scalable dimensionless transformation and strictly bounded terms are designed, which guarantee the existence of the ratio between limited inputs and command signals.
+The adaptive saturated sliding mode control scheme is proposed to govern the tether deployment by introducing the adaptive rate into the system gain.
 The stability analysis indicates that this measure can eliminate the uncertainty caused by the input limitation and guarantee the asymptotically stability of the deployment dynamics.
-\textcolor{red}{Finally, numerical simulations are presented to verify the effectiveness of the proposed control laws.}
+Finally, numerical simulations are presented to verify the effectiveness of the proposed control laws.
 \end{abstract}
@@
 The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space explorations and scientific researches, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}.
-\textcolor{red}{Many international space research institutes have launched orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation schemes for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
-These experimental results intensively help researchers proceed to promote advanced mechanics, kinetic and control studies, to tackle the future challenges of space activities~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.}\par
+Many international space research institutes have launched orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation schemes for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
+These experimental results intensively help researchers proceed to promote advanced mechanics, kinetic and control studies, to tackle the future challenges of space activities~\cite{yu2016nonlinear,wen2015space,aslanov2016swing,meng2016lyapunov,zhang2015line,Xu2016Hybrid}.
 
-\textcolor{red}{Recent scientific researches about deployments of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.} Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the TSS.
+Recent scientific researches about deployments of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.
+Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the TSS.
 Iki et al.
 implemented the ground deployment experiment, and utilized the thruster to conduct the deployment of a kilometers-length electrodynamic tether from a special spool-type reel~\cite{iki2014experiments}.
-\textcolor{red}{Aslanov et al.
-presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thruster force acting on the tug~\cite{aslanov2013dynamics}.} Huang~et~al.
+Aslanov et al.
+presented a novel model about the spatial motion of a large passive satellite and the tug connected by space tether, and the motion of the overall system was excited by a thruster force acting on the tug~\cite{aslanov2013dynamics}.
+Huang~et~al.
 investigated the attitude and deployment dynamics of the tethered space robot from the standpoint of thruster consumption~\cite{huang2015coupling}.
@@
 adopted the thruster scheme to achieve the ideal deployment rate during the deployment of three-body tethered satellites~\cite{jung2015nonlinear}.
-\textcolor{red}{Liu et al.
+Liu et al.
 equipped the subsatellite with the thruster system, consisting of four pairs of thrusters, in order to regulate the attitude and deployment dynamics~\cite{liu2014attitude}.
@@
 reported the thruster-aided deployment of tape tethers driven by both the tension and thruster forces~\cite{mantellato2015thrust}.
-These hybrid strategies has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, and thus is broadly utilized in engineering applications compared with other control strategies.}\par
+These hybrid strategies has several advantages, such as simplifying the input model greatly, non-environmental dependence (magnetic field dependence), easy assembly and physical implementation, and thus is broadly utilized in engineering applications compared with other control strategies.
 
@@
 explained, the limited terms, including the tension and the states of deployment dynamics, can be viewed as seeking the solution of a nonlinear optimal control issue~\cite{wen2015tension}.
-\textcolor{red}{Hu reported an adaptive sliding mode control law with the input limitation by using the reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.} In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the TSS is studied.
+Hu reported an adaptive sliding mode control law with the input limitation by using the reduced sliding dynamic design approach~\cite{Hu2009Robust}, which requires an assumption that the command signal is bounded strictly, and for actual physical systems, this assumption always exits.
+In this paper, a new dynamic adaptive saturated sliding mode  control for the deployment of the TSS is studied.
 For coping with the input limitation in the hybrid control strategy, the strictly saturated command signal is constructed with Sine saturation function.
@@
 \section{Mathematical model}\label{sec:2}
-\textcolor{red}{Figure \ref{fig:1} shows all the elements of the TSS via the geometric representation.
+Figure \ref{fig:1} shows all the elements of the TSS via the geometric representation.
 In the figure, the axes of the coordinate frame $OXYZ$ passes through the center of the earth $O$.
@@
 The orientation of $O_2xyz$ relative to the coordinate frame $O_2x'y'z'$ indicates the in-plane and out-of-plane dynamics, where $\theta$ and $\phi$ stand for the in-plane angle and out-of-plane angle, respectively.
-$\bm R_0$ denotes the position vector between $O_2$ and $O$.}\par
-\textcolor{red}{In the analysis of the deployment of the TSS, there is a primary assumption that the movement of entire system is similar to a ``rolling ball'' behavior with three DOFs modelled, and it is reasonable to invoke the spherical coordinates to describe the behavior~\cite{Williams2008}.} During space mission, the mass of the tether is much smaller than that of the mother satellite, and hence it is always ignored sufficiently.
+$\bm R_0$ denotes the position vector between $O_2$ and $O$.
+
+In the analysis of the deployment of the TSS, there is a primary assumption that the movement of entire system is similar to a ``rolling ball'' behavior with three DOFs modelled, and it is reasonable to invoke the spherical coordinates to describe the behavior~\cite{Williams2008}.
+During space mission, the mass of the tether is much smaller than that of the mother satellite, and hence it is always ignored sufficiently.
 Some other assumptions are obvious and as follows.
-\textcolor{red}{The sizes of satellites are small compared with the length of the tether, and hence a satellite can be regard as a particle if the tether is long enough.
+The sizes of satellites are small compared with the length of the tether, and hence a satellite can be regard as a particle if the tether is long enough.
 Actually, the mass ratio between the subsatellite and the mother satellite is tiny, i.e., in YES2, the mother satellite mass is 6530~$kg$, and the subsatellite mass is 12~$kg$~\cite{Williams2008}.
-Owing to the tiny mass ratio between the satellites, the deployment of the subsatellite will not affect the motion of the mother satellite during the whole mission.} The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
+Owing to the tiny mass ratio between the satellites, the deployment of the subsatellite will not affect the motion of the mother satellite during the whole mission.
+The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
 Symbols used in the model are defined as follows.
@@
 \begin{split}
-&\bar m l''-\bar m l\begin{bmatrix}\phi'^2+(\theta'+\Omega)^2\cos^2\phi\end{bmatrix}+\bar m l\Omega^2(1-3\cos^2\phi\cos^2\theta)=-\tau_t+\tau_{td}\\
+&\bar m l''-\bar m l\left\{\begin{bmatrix}\phi'^2+(\theta'+\Omega)^2\cos^2\phi\end{bmatrix}+\Omega^2(3\cos^2\phi\cos^2\theta-1)\right\}=-\tau_t+\tau_{td}\\
 &\bar m l^2\cos^2\phi\theta''+2\bar m (\theta'+\Omega)l^2\cos^2\phi(l'/l-\phi'\tan\phi)+3\bar m \Omega^2l^2\sin\theta\cos\theta\cos^2\phi=\tau_\theta+\tau_{\theta d}\\
-&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\begin{bmatrix}(\theta'+\Omega)^2+3\bar m \Omega\cos^2\theta\end{bmatrix}=\tau_\phi+\tau_{\phi d},\label{eq:dynamics 1}
+&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\left[(\theta'+\Omega)^2+3\bar m \Omega\cos^2\theta\right]=\tau_\phi+\tau_{\phi d},\label{eq:dynamics 1}
 \end{split}
 \end{align}
-\textcolor{red}{where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively.
-\textcolor{red}{$(\cdot)'$ represents a first derivative with respect to time, and $l$ means the tether length connecting the satellites.
+where, $m = m_1+m_2$ stands for the total mass of the system, $m_1$ and $m_2$ of which denote the mass of the mother satellite and of the subsatellite, respectively.
+$(\cdot)'$ represents a first derivative with respect to time, and $l$ means the tether length connecting the satellites.
 $\theta$ and $\phi$ depict the roll and pitch dynamics of the TSS.
@@
 $\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster force and the out-of-plane thruster force, respectively.
-$\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.} Typically, the dimensionless transformations simplify issues for researchers to design the deployment scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
+$\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.
+Typically, the dimensionless transformations simplify issues for researchers to design the deployment scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
 \begin{align}
@@
 &\lambda=l/L\\
-&d()/dt=\Omega d()/dv\\
+&\rm{d}\it{()}/\rm{d}\it{t}=\Omega \rm{d}\it{()}/\rm{d}\it{v}\\
 &\hat{\tau}_{t0}=-\tau_t/(\bar{m}\Omega^2L)\\
@@
 &\lambda=l/L\\
-&d()/dt=\Omega d()/dv\\
+&\rm{d}\it{()}/\rm{d}\it{t}=\Omega \rm{d}\it{()}/\rm{d}\it{v}\\
 &\hat{\tau}_t=-\tau_t/(\bar{m}\Omega^2L)+\lambda\\
@@
 The obvious benefits of these transformations are that all the inputs own the positive and negative boundedness and hence satisfy the assumption about limited inputs of existing control laws~\cite{Hu2008552,6060930}.
-Furthermore, the generalized inputs~(\ref{eq:varcon}) can be processed by the proposed Sine function in this paper to yield the strict saturated inputs, which essentially guarantee the rigorous stability analysis of the proposed adaptive sliding mode control law.}
+Furthermore, the generalized inputs~(\ref{eq:varcon}) can be processed by the proposed Sine function in this paper to yield the strict saturated inputs, which essentially guarantee the rigorous stability analysis of the proposed adaptive sliding mode control law.
 
@@
 \end{align}
-\textcolor{red}{In reality, once $\lambda = 0$ is satisfied, the mother satellite and subsatellite will collide with each other, which is meaningless for the deployment of the TSS.
-Hence the minimum of the dimensionless length $\lambda_{min}$ is introduced to maintain the reasonably safe formation of the satellites, and also guarantees the non-singularity of the dimensionless transformation~(\ref{eq:dynamics 1}) theoretically.} $\lambda_{max}$ stands for the maximum tether length ratio.\par
+In reality, once $\lambda = 0$ is satisfied, the mother satellite and subsatellite will collide with each other, which is meaningless for the deployment of the TSS.
+Hence the minimum of the dimensionless length $\lambda_{min}$ is introduced to maintain the reasonably safe formation of the satellites, and also guarantees the non-singularity of the dimensionless transformation~(\ref{eq:dynamics 1}) theoretically.
+$\lambda_{max}$ stands for the maximum tether length ratio.\par
 The tension acting on the space tether is a positive scalar during the deployment, since zero tension means slack, which is inconsistent with the fundamental assumption that the tether is stiff in the ``rolling ball'' model.
@@
 \end{align}
-\textcolor{red}{For the system~(\ref{eq:dynamic model 2}) with the input limitation ignored, the author in \cite{parra2003dynamic} has designed a nonlinear dynamic sliding PID controller with the zero initial condition:
+For the system~(\ref{eq:dynamic model 2}) with the input limitation ignored, the author in \cite{parra2003dynamic} has designed a nonlinear dynamic sliding PID controller with the zero initial condition:
 \begin{align}\begin{split}
 \dot {\bm q}_r&=\dot{\bm q}_d-\alpha\Delta\bm q-\gamma\bm\sigma\\
-\dot{\bm\sigma}&=\bm{sign}(\bm S)\\
+\dot{\bm\sigma}&=\mathbf{sign}(\bm S)\\
 \bm S&=\Delta\dot{\bm q}+\alpha\Delta\bm q\label{eq:pid controller}
@@
 \begin{align}
-\bm{sign}(\bm x) = \left(sign(x_1),sign(x_2),\cdots,sign(x_n)\right)^T
+\mathbf{sign}(\bm x) = \left(\rm{sign}(\it{x_1}),\rm{sign}(\it{x_2}),\cdots,\rm{sign}(\it{x_n})\right)^T
 \end{align}
@@
 Define the tracking error as $\Delta \bm q=\bm q-\bm q_d$, in which $\bm q_d$ is the desired trajectory with $\bm q_d(t)\in C^2$.
-However, the PID controller~(\ref{eq:pid controller}) can not be directly applied to the system~(\ref{eq:dynamic model 2}) with the input limitation, and in the subsequent section, we will utilize the saturated sliding mode technique to modify the controller~(\ref{eq:pid controller}) for the system~(\ref{eq:dynamic model 2}).} For deriving the proposed control scheme, some properties should be given out in advance.
+However, the PID controller~(\ref{eq:pid controller}) can not be directly applied to the system~(\ref{eq:dynamic model 2}) with the input limitation, and in the subsequent section, we will utilize the saturated sliding mode technique to modify the controller~(\ref{eq:pid controller}) for the system~(\ref{eq:dynamic model 2}).
+For deriving the proposed control scheme, some properties should be given out in advance.
 \begin{mypro}\cite{parra2003dynamic}\label{pro:1}
-\textcolor{red}{Positive scalars $\Xi_i(i = 0,\ldots,6)$ always exist such that
+Positive scalars $\Xi_i(i = 0,\ldots,6)$ always exist such that
 \begin{align}
@@
 where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively.
-Furthermore, one can have $Y_r\bm\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta \bm q,\Delta \dot {\bm q},\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\bm\Theta$ is usually thought to be a bounded function with $\vert\eta\vert\le\varphi_0$, where $\varphi_0$ is a positive scalar determined according to the system states.}
+Furthermore, one can have $Y_r\bm\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta \bm q,\Delta \dot {\bm q},\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\bm\Theta$ is usually thought to be a bounded function with $\vert\eta\vert\le\varphi_0$, where $\varphi_0$ is a positive scalar determined according to the system states.
 \end{mypro}
@@
 \begin{myas}
-\textcolor{red}{
 In low-altitude orbit , the external disturbance $\bm\tau_d$ contains the gravity gradient torque, the aerodynamic interference and the solar radiation pressure torque.
@@
 where $\varphi_1$ can be selected as a positive scalar $\varphi_1=1$.
-}
 \end{myas}
@@
 \begin{align}
-Sine(x) =
+\rm{Sine}\it{(x)} =
 \begin{cases}
-sign(x)&\vert x\vert\ge\pi/2\\
-sin(x)&\vert x\vert<\pi/2
+\rm{sign}\it{(x)}&\vert x\vert\ge\pi/2\\
+\sin(x)&\vert x\vert<\pi/2
 \end{cases},
 \end{align}
-and it's notable that the function above is saturated and owns an important property: $\vert Sine(x)\vert\le\vert x\vert$, $\forall x$.
-The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=Sine(x)$ along the axis $x=0$ in the range $[-1,1]$, and once the function $y=Sine(x)+\Delta h$ with $\vert\Delta h\vert<1$ settles, one can choose the function $y = x+arcsin(\Delta h)$ to obtain following relations:
+and it's notable that the function above is saturated and owns an important property: $\vert \rm{Sine}\it{(x)}\vert\le\vert x\vert$, $\forall x$.
+The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=\rm{Sine}(\it{x})$ along the axis $x=0$ in the range $[-1,1]$, and once the function $y=\rm{Sine}\it{(x)}+\Delta h$ with $\vert\Delta h\vert<1$ settles, one can choose the function $y = x+\arcsin(\Delta h)$ to obtain following relations:
 \begin{align}
-&\vert Sine(x)+\Delta h\vert\le\vert x+arcsin(\Delta h)\vert\label{eq:lem11}\\
-&sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)), \forall x, \vert\Delta h\vert<1\label{eq:lem12}.
+&\vert \rm{Sine}\it{(x)}+\Delta h\vert\le\vert x+\arcsin(\Delta h)\vert\label{eq:lem11}\\
+&\rm{sign}(\rm{Sine}\it{(x)}+\Delta h)=\rm{sign}(\it{x}+\arcsin(\Delta h)), \forall x, \vert\Delta h\vert<1\label{eq:lem12}.
 \end{align}
@@
 \begin{proof}
-For relation~(\ref{eq:lem11}), let $y=Sine(x)+\Delta h-x-arcsin(\Delta h)$, and we can get its derivative
+For relation~(\ref{eq:lem11}), let $y=\rm{Sine}\it{(x)}+\Delta h-x-\arcsin(\Delta h)$, and we can get its derivative
 \begin{align}
 \begin{cases}
-dy/dx = -1,&x\ge\pi/2,x\le-\pi/2\\
-dy/dx = \cos x - 1,&\vert x\vert<\pi/2,
+\rm{d}\it{y}/\rm{d}\it{x} = -1,&x\ge\pi/2,x\le-\pi/2\\
+\rm{d}\it{y}/\rm{d}\it{x} = \cos x - 1,&\vert x\vert<\pi/2,
 \end{cases}
 \end{align}
-where $dy/dx<0$ means $y$ is a monotone decreasing function with respect to $x$. As $x=-arcsin(\Delta h)$, $y=0$, according to the definition of $Sine(x)$, we proceed to get
+where $\rm{d}\it{y}/\rm{d}\it{x}<0$ means $y$ is a monotone decreasing function with respect to $x$.
+As $x=-\arcsin(\Delta h)$, $y=0$, according to the definition of $\rm{Sine}\it{(x)}$, we proceed to get
 $$\left.
 \begin{aligned}
-x\ge-arcsin(\Delta h), y\le0&\Rightarrow 0\le Sine(x)+\Delta h\le x+arcsin(\Delta h)\\
-x<-arcsin(\Delta h), y>0&\Rightarrow 0> Sine(x)+\Delta h>x+arcsin(\Delta h)\end{aligned}\right\}\\\\
-\Rightarrow\vert Sine(x)+\Delta h\vert\le\vert x+arcsin(\Delta h)\vert.
+x\ge-\arcsin(\Delta h), y\le0&\Rightarrow 0\le \rm{Sine}\it{(x)}+\Delta h\le x+\arcsin(\Delta h)\\
+x<-\arcsin(\Delta h), y>0&\Rightarrow 0> \rm{Sine}\it{(x)}+\Delta h>x+\arcsin(\Delta h)\end{aligned}\right\}\\\\
+\Rightarrow\vert \rm{Sine}\it{(x)}+\Delta h\vert\le\vert x+\arcsin(\Delta h)\vert.
 $$
-For Eq.~(\ref{eq:lem12}), considering the case $Sine(x)+\Delta h>0$, when $\vert x\vert<\pi/2$, $Sine(x)+\Delta h>0$ becomes
+For Eq.~(\ref{eq:lem12}), considering the case $\rm{Sine}\it{(x)}+\Delta h>0$, when $\vert x\vert<\pi/2$, $\rm{Sine}\it{(x)}+\Delta h>0$ becomes
 \begin{align}
-sin(x)+\Delta h>0&\Rightarrow x>-arcsin(\Delta h)\\
-&\Rightarrow x+arcsin(\Delta h)>0,
+\sin(x)+\Delta h>0&\Rightarrow x>-\arcsin(\Delta h)\\
+&\Rightarrow x+\arcsin(\Delta h)>0,
 \end{align}
-since $y=arcsin(x)$ is a monotone increasing function.
-We only need to consider $x\ge\pi/2$ instead of $\vert x\vert\ge\pi/2$ for $x\le-\pi/2$ is meaningless in the case $Sine(x)+\Delta h>0$.
-It is obvious that $x+arcsin(\Delta h)>0$ due to $\vert arcsin(\Delta h)\vert<\pi/2$.
+since $y=\arcsin(x)$ is a monotone increasing function.
+We only need to consider $x\ge\pi/2$ instead of $\vert x\vert\ge\pi/2$ for $x\le-\pi/2$ is meaningless in the case $\rm{Sine}\it{(x)}+\Delta h>0$.
+It is obvious that $x+\arcsin(\Delta h)>0$ due to $\vert \arcsin(\Delta h)\vert<\pi/2$.
 Therefore, we can get
 \begin{align}
-sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)),Sine(x)+\Delta h>0,
+\rm{sign}(\rm{Sine}\it{(x)}+\Delta h)=\rm{sign}\it{(x}+\arcsin(\Delta h)),\rm{Sine}\it{(x)}+\Delta h>0,
 \end{align}
@@
 \begin{align}
-sign(Sine(x)+\Delta h)=sign(x+arcsin(\Delta h)),Sine(x)+\Delta h\le0.
+\rm{sign}(\rm{Sine}\it{(x)}+\Delta h)=\rm{sign}\it{(x}+\arcsin(\Delta h)),\rm{Sine}\it{(x)}+\Delta h\le0.
 \end{align}
 \end{proof}
-\begin{myrem}\textcolor{red}{Moreover, we think that a quantity $y$ is saturated iff it is produced directly by the saturated function $y=Sine(x)$.
-Otherwise, the bounded quantity is different from the saturated one since it does not own the standard formulation like $y=Sine(x)$, i.e., a quantity can just be referred to as a bounded quantity if its boundary is $[a,b]$ with $a\neq -1$ or $b\neq 1$.}
+\begin{myrem}Moreover, we think that a quantity $y$ is saturated iff it is produced directly by the saturated function $y=\rm{Sine}\it{(x)}$.
+Otherwise, the bounded quantity is different from the saturated one since it does not own the standard formulation like $y=\rm{Sine}\it{(x)}$, i.e., a quantity can just be referred to as a bounded quantity if its boundary is $[a,b]$ with $a\neq -1$ or $b\neq 1$.
 \end{myrem}
@@
 \includegraphics[width=0.75\textwidth]{paper4_fig2.eps}
-\caption{$y =Sine(x)$ and $y=Sine(x)+\Delta h$}
+\caption{$y =\rm{Sine}\it{(x)}$ and $y=\rm{Sine}\it{(x)}+\Delta h$}
 \label{fig:2}
@@
 \begin{myrem}
-As we know, \textcolor{red}{the tension, in-plane and out-of-plane thruster forces are all limited during the deployment mission, and we describe these inputs by using the matrix and vector to predigest the following illation.}
+As we know, the tension, in-plane and out-of-plane thruster forces are all limited during the deployment mission, and we describe these inputs by using the matrix and vector to predigest the following illation.
 \begin{align}
@@
 \end{align}
-and in order to design the saturated sliding mode control law for the dynamics of the deployment, the $Sine$ function for vectors is specified as:
+and in order to design the saturated sliding mode control law for the dynamics of the deployment, the $\rm{Sine}$ function for vectors is specified as:
 \begin{align}
-\bm{Sine}(\bm x)=\begin{pmatrix}Sine(x_1),Sine(x_2),\cdots,Sine(x_n)\end{pmatrix}^T.
+\mathbf{Sine}(\bm x)=\begin{pmatrix}\rm{Sine}\it{(x_1)},\rm{Sine}\it{(x_2)},\cdots,\rm{Sine}\it{(x_n)}\end{pmatrix}^T.
 \end{align}
@@
 \begin{align}
-\bm\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1})),\label{eq:slider control}
+\bm\tau = -\bm{g}(\delta\varphi F(t) \mathbf{sign}(\bm S_{r1})),\label{eq:slider control}
 \end{align}
@@
 \bm S_{r1} &= \bm S_{q1}+\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\\
-\bm S_{q1} &= \bm{Sine}(\Delta \dot {\bm q}+\alpha\Delta\bm q),
+\bm S_{q1} &= \mathbf{Sine}(\Delta \dot {\bm q}+\alpha\Delta\bm q),
 \end{split}
@@
 \begin{align}
-\frac{d}{dt}F(t) = \delta\varphi \bm S_{r2}^T K_1e^{-2K_1^{-1}F^{-1}(t)}\bm{sign}(\bm S_{r2})
+\frac{\rm{d}}{\rm{d}\it{t}}F(t) = \delta\varphi \bm S_{r2}^T K_1\rm{e}\it{^{-2K_1^{-1}F^{-1}(t)}}\mathbf{sign}(\bm S_{r2})
 \end{align}
-\textcolor{red}{where $K_1\in R^{3\times 3}$ is a positive definite diagonal matrix, which will be given out later, and if $K\in R^{3\times 3}$, define}
+where $K_1\in R^{3\times 3}$ is a positive definite diagonal matrix, which will be given out later, and if $K\in R^{3\times 3}$, define
 \begin{align}
-e^K=
+\rm{e}\it{^K}=
 \begin{bmatrix}
-e^{K_{11}}&e^{K_{12}}&e^{K_{13}}\\
-e^{K_{21}}&e^{K_{22}}&e^{K_{23}}\\
-e^{K_{31}}&e^{K_{32}}&e^{K_{33}}
+\rm{e}\it{^{K_{11}}}&\rm{e}\it{^{K_{12}}}&\rm{e}\it{^{K_{13}}}\\
+\rm{e}\it{^{K_{21}}}&\rm{e}\it{^{K_{22}}}&\rm{e}\it{^{K_{23}}}\\
+\rm{e}\it{^{K_{31}}}&\rm{e}\it{^{K_{32}}}&\rm{e}\it{^{K_{33}}}
 \end{bmatrix}.
 \end{align}
-\textcolor{red}{$\varphi$ is the boundedness of the lumped uncertainty.
-$\gamma$ is designed as a time-varying positive scalar and $\delta>1$ is the design parameter, so that the deployment dynamics can be regulated as desired.}
+$\varphi$ is the boundedness of the lumped uncertainty.
+$\gamma$ is designed as a time-varying positive scalar and $\delta>1$ is the design parameter, so that the deployment dynamics can be regulated as desired.
 \end{mythm}
@@
 \begin{split}
-\bm S_{r2} &= \bm S_{q2}+\bm{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma)\\
+\bm S_{r2} &= \bm S_{q2}+\bm{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma})\\
 \bm S_{q2} &= \Delta \dot {\bm q}+\alpha \Delta \bm q,
@@
 \end{align}
-where $\bm y=\bm{arcsin}(\bm x)$ is the vector function with
+where $\bm y=\mathbf{arcsin}(\bm x)$ is the vector function with
 \begin{align}
-\bm{arcsin}(\bm x) = \left(arcsin(x_1),arcsin(x_2),\cdots,arcsin(x_n)\right)^T
+\mathbf{arcsin}(\bm x) = \left(\arcsin(x_1),\arcsin(x_2),\cdots,\arcsin(x_n)\right)^T
 \end{align}
 for a vector $\bm x=\left(x_1,x_2,\cdots,x_n\right)^T$.
-It is obvious that $\bm S_{q_1}$ is exactly saturated, hence $\bm S_{r_1}$ is also bounded if the dynamics can be controlled as desired.
-\textcolor{red}{In addition, for guaranteeing that $\bm x=\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma$ always falls in the field of definition of $\bm y=\bm{arcsin}(\bm x)$, $\gamma$ can be designed as a time-varying parameter
+It is obvious that $\bm S_{q1}$ is exactly saturated, hence $\bm S_{r1}$ is also bounded if the dynamics can be controlled as desired.
+In addition, for guaranteeing that $\bm x=\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma$ always falls in the field of definition of $\bm y=\mathbf{arcsin}(\bm x)$, $\gamma$ can be designed as a time-varying parameter
     \begin{align}
@@
     \end{align}
-    where $\gamma_0$ can be selected as $\gamma_0=0.1$.}\par
+    where $\gamma_0$ can be selected as $\gamma_0=0.1$.
+
 According to Lemma~\ref{lemma:1}, it is apparent that $\bm S_{r2}$ and $\bm S_{r1}$ have the subsequent relations:
 \begin{align}
-&\bm S_{r2}^T \bm{sign}(\bm S_{r2}) \ge  \bm S_{r1}^T \bm{sign}(\bm S_{r1})\\
-&\bm{sign}(\bm S_{r2})=\bm{sign}(\bm S_{r1}),
+&\bm S_{r2}^T \mathbf{sign}(\bm S_{r2}) \ge  \bm S_{r1}^T \mathbf{sign}(\bm S_{r1})\\
+&\mathbf{sign}(\bm S_{r2})=\mathbf{sign}(\bm S_{r1}),
 \end{align}
@@
 \begin{align}
-H(q)\dot {\bm S}_{r2} = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm\tau_d-C(q,\dot q)\bm S_{r2}-Y_{r2}\bm\Theta.
+H(q)\dot {\bm S}_{r2} = -\bm{g}(\delta\varphi F(t) \mathbf{sign}(\bm S_{r1}))+\bm\tau_d-C(q,\dot q)\bm S_{r2}-Y_{r2}\bm\Theta.
 \end{align}
@@
 \end{align}
-where $v=F(t)e^{K_1^{-1}F^{-1}(t)}$. Differentiating the Lyapunov function above gives rise to
+where $v=F(t)\rm{e}\it{^{K_1^{-1}F^{-1}(t)}}$. Differentiating the Lyapunov function above gives rise to
 \begin{align}
@@
 \dot V &= \bm S_{r2}^TH(q)\dot {\bm S}_{r2}+\frac{1}{2}\bm S_{r2}^T\dot H(q)\bm S_{r2}+v\dot v\\
-&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TC(q,\dot q)\bm S_{r2}+\frac{1}{2}\bm S_{r2}^T\dot H(q)\bm S_{r2}-\bm S_{r2}^TY_{r2}\bm\Theta+v\dot v\\
-&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\bm\Theta+\frac{1}{2}\bm S_{r2}^T(\dot H(q)-2C(q,\dot q))\bm S_{r2}+v\dot v\\
-&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\bm\Theta+v\dot v\\
-&= -\bm S_{r2}^TR_M(\delta\varphi F(t) \bm{sign}(\bm S_{r1}))\delta\varphi F(t) \bm{sign}(\bm S_{r1})+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{\bm r2}\bm\Theta+v\dot v.\label{eq:V1_1}
+&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \mathbf{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TC(q,\dot q)\bm S_{r2}+\frac{1}{2}\bm S_{r2}^T\dot H(q)\bm S_{r2}-\bm S_{r2}^TY_{r2}\bm\Theta+v\dot v\\
+&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \mathbf{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\bm\Theta+\frac{1}{2}\bm S_{r2}^T(\dot H(q)-2C(q,\dot q))\bm S_{r2}+v\dot v\\
+&= -\bm S_{r2}^T\bm{g}(\delta\varphi F(t) \mathbf{sign}(\bm S_{r1}))+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{r2}\bm\Theta+v\dot v\\
+&= -\bm S_{r2}^TR_M(\delta\varphi F(t) \mathbf{sign}(\bm S_{r1}))\delta\varphi F(t) \mathbf{sign}(\bm S_{r1})+\bm S_{r2}^T\bm\tau_d-\bm S_{r2}^TY_{\bm r2}\bm\Theta+v\dot v.\label{eq:V1_1}
 \end{split}
 \end{align}
-\textcolor{red}{Since the command signal $ \bm\tau_c=-\delta\varphi F(t) \bm {sign}(\bm{S}_{r1})$ is bounded, we can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ which satisfy $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain the diagonal matrix $K_1$ as follows:}
+Since the command signal $ \bm\tau_c=-\delta\varphi F(t) \mathbf {sign}(\bm{S}_{r1})$ is bounded, we can select reasonably small positive scalars $c_1$, $c_2$ and $c_3$ which satisfy $0<c_1\le R(\hat\tau_t)<1$, $0<c_2\le R(\hat\tau_\theta)<1$ and $0<c_3\le R(\hat\tau_\phi)<1$, and obtain the diagonal matrix $K_1$ as follows:
 \begin{align}
@@
 \end{align}
-\textcolor{red}{$v\dot v$ can be derived as follows:
+$v\dot v$ can be derived as follows:
 \begin{align}
-v\dot v =\varphi\delta \bm S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(\bm S_{r2}),
+v\dot v =\varphi\delta \bm S_{r2}^T K_1(F(t)-K_1^{-1})\mathbf{sign}(\bm S_{r2}),
 \end{align}
-considering $\bm{sign}(\bm S_{r1})=\bm{sign}(\bm S_{r2})$, we can proceed to rewrite Eq.~(\ref{eq:V1_1}) as:
+considering $\mathbf{sign}(\bm S_{r1})=\mathbf{sign}(\bm S_{r2})$, we can proceed to rewrite Eq.~(\ref{eq:V1_1}) as:
 \begin{align}
 \begin{split}\label{eq:V1_2}
-\dot V&\le -\bm S_{r2}^T\delta\varphi  K_1F(t)\bm{sign}(\bm S_{r2})+\bm S_{r2}^T(\varphi_1+\varphi_2) \bm{sign}(\bm S_{r2})+\varphi\delta \bm S_{r2}^T K_1(F(t)-K_1^{-1})\bm{sign}(\bm S_{r2})\\
-&\le \varphi \bm S_{r2}^T\bm{sign}(\bm S_{r2})-\varphi\delta \bm S_{r2}^T \bm{sign}(\bm S_{r2})\\
-&\le\varphi(1-\delta)\bm S_{r2}^T\bm{sign}(\bm S_{r2})\le 0
+\dot V&\le -\bm S_{r2}^T\delta\varphi  K_1F(t)\mathbf{sign}(\bm S_{r2})+\bm S_{r2}^T(\varphi_1+\varphi_2) \mathbf{sign}(\bm S_{r2})+\varphi\delta \bm S_{r2}^T K_1(F(t)-K_1^{-1})\mathbf{sign}(\bm S_{r2})\\
+&\le \varphi \bm S_{r2}^T\mathbf{sign}(\bm S_{r2})-\varphi\delta \bm S_{r2}^T \mathbf{sign}(\bm S_{r2})\\
+&\le\varphi(1-\delta)\bm S_{r2}^T\mathbf{sign}(\bm S_{r2})\le 0
 \end{split}
-\end{align}}
-\textcolor{red}{
+\end{align}
 where a large enough $\delta>1$ can be selected to satisfy $\dot V \le 0$.
 According to the description of Barbalat's lemmas, we can conclude  that $\bm S_{r2}$ asymptotically converges to the origin.
-Also, the finite reaching time can be calculated by referring to~\cite{Ma201667}.}\par
-\textcolor{red}{Utilizing $\bm S_{r2}=0$ leads to the equation
+Also, the finite reaching time can be calculated by referring to~\cite{Ma201667}.
+
+Utilizing $\bm S_{r2}=0$ leads to the equation
 \begin{align}
-\bm S_{q2}=-\bm{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma),\label{eq:eqSq2}
+\bm S_{q2}=-\mathbf{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma}),\label{eq:eqSq2}
 \end{align}
@@
 \begin{align}
-V_1 = \frac{1}{2}\bm S_{q2}^T\bm S_{q_2},
+V_1 = \frac{1}{2}\bm S_{q2}^T\bm S_{q2},
 \end{align}
@@
 \begin{split}
-\dot V_1 &= \bm S_{q2}^T\dot {\bm S}_{q_2}\\
-&=-\frac{\gamma \bm S_{q2}^TS_{q1}}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert^2}}\\
-&\le -\frac{\gamma \Vert \bm S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert^2}}\le 0,
+\dot V_1 &= \bm S_{q2}^T\dot {\bm S}_{q2}\\
+&=-\frac{\gamma \bm S_{q2}^T\bm S_{q1}}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma\Vert^2}}}\\
+&\le -\frac{\gamma \Vert \bm S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma\Vert^2}}}\le 0,
 \end{split}
@@
 Hence asymptotically convergence of $\Delta \bm q$ has been explained, namely, $\Delta \bm q\rightarrow 0$ as $t\rightarrow \infty$.
-To conclude, the error state $\Delta \bm q$ of the system~(\ref{eq:dynamics 1}) asymptotically converges to the origin with the limited input~(\ref{eq:slider control})}.
+To conclude, the error state $\Delta \bm q$ of the system~(\ref{eq:dynamics 1}) asymptotically converges to the origin with the limited input~(\ref{eq:slider control}).
 This completes the proof.
@@
 \begin{myrem}
-\textcolor{red}{For the adaptive sliding mode control law with input limitation, the adaptive update rate $\frac{d}{dt}F(t)$ always helps to remove the side-effect of the input limitation during the stability analysis by using Lyapunov second method, and moreover, the actual examples of $F(t)$ are unhelpful to the theoretical derivation and the control law design~\cite{Hu2008552,6060930}.
-This is because we can search the actual value of $F(t)$  by the way of state updating from the initial condition $F(0)=0$, for instance, in our simulations, we apply Ode45 technique to update states of the overall system including this adaptive update rate.}
+For the adaptive sliding mode control law with input limitation, the adaptive update rate $\frac{\rm{d}}{\rm{d}\it{t}}F(t)$ always helps to remove the side-effect of the input limitation during the stability analysis by using Lyapunov second method, and moreover, the actual examples of $F(t)$ are unhelpful to the theoretical derivation and the control law design~\cite{Hu2008552,6060930}.
+This is because we can search the actual value of $F(t)$  by the way of state updating from the initial condition $F(0)=0$, for instance, in our simulations, we apply Ode45 technique to update states of the overall system including this adaptive update rate.
 \end{myrem}
+In the aforementioned controller design, signum functions in inputs lead to chattering phenomena, which may cause adverse unmodeled dynamics to ruin the control system.
+Herein, we adopt the boundary layer technique to reduce chattering through replacing $\rm{sign}\it{(x)}$ by $\rm{sat}\it{(x/\nu)}$, where
+\begin{align}
+\rm{sat}\it{(x/\nu)}=
+\begin{cases}
+x,&\vert x\vert <\nu\\
+\rm{sign}\it{(x)},&\vert x\vert\ge\nu
+\end{cases}
+\end{align}
+and $\nu$ is the boundary layer thickness.
+However, the cost of using boundary layer in sliding mode controller is that the asymptotic stability of proposed method can not be guaranteed, and we proceed to analyze the convergence precision in the following theorem.
+\begin{mythm}
+Considering the controller in Theorem~\ref{thm:1}, we replace $\mathbf{sign}{(\bm{x})}$ in Eq.~(\ref{eq:slider control}) by $\mathbf{sat}{(\boldsymbol {x/\nu})}$, where $\mathbf{sat}{(\boldsymbol{x}/\boldsymbol{\nu})}=\left(\rm{sat}\it{(x_1/\nu_1)},\rm{sat}\it{(x_2/\nu_2)},\cdots,\rm{sat}\it{(x_n/\nu_n)}\right)^T$, to remove the chattering caused by the signum function, and the modified controller can guarantee the precisions of system states $\Delta\bm q$ that satisfy
+\begin{align}
+  \Vert\Delta\bm q\Vert\le\frac{\Vert\boldsymbol{arcsin}(\bm \nu)\Vert}{\alpha}.
+\end{align}
+$\bm z$ is the position vector that describes the distances of system states in the boundary layer from the sliding mode surface, and $\dot{\bm z}$ is the velocity vector correspondingly.
+It is obvious that $\bm z$ is bounded and has $\Vert\bm z\Vert\le\Vert\bm\nu\Vert$, where $\bm\nu=(\nu_1,\nu_2,\nu_3)^T,\nu_1=\nu_2=\nu_3\ll 1$ is a constant vector denoting the boundary layer thicknesses for the three channels.
+Since all the inputs are bounded, it is evident to assume that $\dot{\bm z}$ is bounded with $\Vert\dot{\bm z}\Vert\le \bar z\le 2\Vert\bm\nu\Vert/\rm{d}\it{t}$.
+\end{mythm}
+\begin{proof}
+Referring to the derivation in Theorem~\ref{thm:1}, we can guarantee the system states reach and enter the boundary layer $\Vert\bm{ S}_{r2}\Vert \le \Vert\bm\nu\Vert$ such that
+\begin{align}
+\bm S_{q2}=\bm z-\mathbf{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma}).
+\end{align}
+The selected Lyapunov function $V_3=\frac{1}{2}\bm{ S}_{q2}^T\bm{ S}_{q2}$ gives rise to
+\begin{align}\begin{split}
+\dot V_3&=\bm{ S}_{q2}^T\dot{\bm{S}}_{q2}\\
+&=-\frac{\gamma \bm S_{q2}^T\bm S_{q1}}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma\Vert^2}}}+\bm{ S}_{q2}^T\dot{\bm z}\\
+&\le -\frac{\gamma \Vert \bm S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma\Vert^2}}}+\Vert\dot{\bm{z}}\Vert(\Vert\bm z\Vert+\Vert\mathbf{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma})\Vert)\\
+&\le -\frac{\gamma \Vert \bm S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma\Vert^2}}}+\bar z(\Vert\bm{\nu}\Vert+\pi/2)\\
+\end{split}\end{align}
+Based on the Lyapunove stability theory, the above expression implies that $\bm S_{q2} = \Delta \dot {\bm q}+\alpha \Delta \bm q=0$ can attract the system states under the condition
+\begin{align}
+  \Vert \bm S_{q1}\Vert\ge\sqrt{\frac{\bar z(\Vert\bm{\nu}\Vert+\pi/2)}{\gamma}}
+\end{align} Rephrasing that, the controller in Theorem~\ref{thm:1} with boundary layer technique can guarantee $\bm S_{q1}$ to converge to $\Vert\bm S_{q1}\Vert\le\sqrt{\frac{\bar z(\Vert\bm{\nu}\Vert+\pi/2)}{\gamma}}$, and once the states reach the boundary layer, since $\bm S_{q1}=\mathbf{Sine}(\Delta\dot{\bm q}+\alpha\Delta\bm q)$ we can combine
+\begin{align}
+  \mathbf{Sine}(\Delta\dot{\bm q}+\alpha\Delta\bm q)=\bm\nu
+\end{align}
+with the Lyapunov function $V_4=\frac{1}{2}\Delta\bm q^T\Delta\bm q$ to obtain
+\begin{align}\begin{split}
+\dot V_4 &= \Delta\bm q\Delta\dot{\bm q}\\
+&=\Delta\bm q^T(-\alpha\Delta\bm q+\boldsymbol{arcsin}(\bm \nu))\\
+&\le-\alpha\Vert\Delta\bm q\Vert^2+\Vert\Delta\bm q\Vert\Vert\boldsymbol{arcsin}(\bm \nu)\Vert\\
+&\le-(\alpha\Vert\Delta\bm q\Vert-\Vert\boldsymbol{arcsin}(\bm \nu)\Vert)\Vert\Delta\bm q\Vert,
+\end{split}\end{align}
+which indicates that $\Vert\Delta\bm q\Vert=\frac{\Vert\boldsymbol{arcsin}(\bm \nu)\Vert}{\alpha}$ is an attractor, and hence, the ultimately system state precision of the controller with boundary layer technique is
+\begin{align}
+  \Vert\Delta\bm q\Vert\le\frac{\Vert\boldsymbol{arcsin}(\bm \nu)\Vert}{\alpha}.
+\end{align}
+This completes the proof.
+\end{proof}
 \subsection{Quasi-saturated terminal sliding mode control law subjected to input limitation}
@@
 \end{align}
-\textcolor{red}{where $0<p/q<1$ while $p$ and $q$ are both positive odd, and a equivalent formula}
+where $0<p/q<1$ while $p$ and $q$ are both positive odd, and a equivalent formula
 \begin{align}
-\dot Z = \vert Z\vert^{\hat\alpha} {sign}(Z),
+\dot Z = \vert Z\vert^{\hat\alpha} {\rm{sign}}\it{(Z)},
 \end{align}
-\textcolor{red}{where $0<\hat \alpha<1$, performs the same behavior.
-Putting the terminal attractor into the saturated sliding mode control law yields a saturated slider-like scheme, and before introducing the input limitation into the system, an assumption is given firstly.}
+where $0<\hat \alpha<1$, performs the same behavior.
+Putting the terminal attractor into the saturated sliding mode control law yields a saturated slider-like scheme, and before introducing the input limitation into the system, an assumption is given firstly.
 \begin{myas}\label{as:1}
@@
 \begin{align}
-\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r3}))
+\tau = -\bm{g}(\delta\varphi F(t) \mathbf{sign}(\bm S_{r3}))
 \end{align}
@@
 \begin{align}
-\bm S_{r3} &= \bm S_{q3}+\gamma\int^t_{t_0}\vert \bm S_{q3}(\varsigma)\vert^{\hat\alpha}  \bm{sign}(\bm S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
-\bm S_{q3} &= \Delta \dot {\bm q}+\alpha \bm{Sine}(\xi\Delta \bm q),\label{eq:Sq3}
+\bm S_{r3} &= \bm S_{q3}+\gamma\int^t_{t_0}\vert \bm S_{q3}(\varsigma)\vert^{\hat\alpha}  \mathbf{sign}(\bm S_{q3}(\varsigma))\rm{d}\it{\varsigma}\label{eq:Sr3}\\
+\bm S_{q3} &= \Delta \dot {\bm q}+\alpha \mathbf{Sine}(\xi\Delta \bm q),\label{eq:Sq3}
 \end{align}
@@
 Compared with the saturated sliding mode control law, $\bm S_{q3}$ converges to the origin in finite time in the quasi-saturated terminal method.
-This is because the establishment of the equation $\dot {\bm S}_{q3} = \gamma\vert \bm S_{q3}\vert^{\hat\alpha} \bm{ sign}(\bm S_{q3})$.
+This is because the establishment of the equation $\dot {\bm S}_{q3} = \gamma\vert \bm S_{q3}\vert^{\hat\alpha} \mathbf{ sign}(\bm S_{q3})$.
 \end{myrem}
 \begin{myrem}
-\textcolor{red}{Assumption~\ref{as:1} guarantees that the input $\tau$ is bounded in Theorem~\ref{thm:2}, accordingly, a tiny positive scalar $c$ can be found to ensure that $0<c\le R(\hat\tau_t)<1$ always exists.} Admittedly, such kind of assumption is ''skillful'', but meaningful to arbitrary controllable dynamics in reality.
+Assumption~\ref{as:1} guarantees that the input $\tau$ is bounded in Theorem~\ref{thm:2}, accordingly, a tiny positive scalar $c$ can be found to ensure that $0<c\le R(\hat\tau_t)<1$ always exists.
+Admittedly, such kind of assumption is skillful, but meaningful to arbitrary controllable dynamics in reality.
 It is reasonable to propose the terminal sliding mode control law for the dynamics as follows:
 \begin{align}
-\tau = -\bm{g}(\delta\varphi F(t) \bm{sign}(\bm S_{r4})),
+\tau = -\bm{g}(\delta\varphi F(t) \mathbf{sign}(\bm S_{r4})),
 \end{align}
@@
 \begin{split}
-\bm S_{r4} &= \bm S_{q4}+\gamma\int^t_{t_0}\bm S_{q4}(\varsigma) d\varsigma\\
-\bm S_{q4} &= \bm{Sine}(\Delta \dot {\bm q}+\alpha\xi\vert\Delta \bm q\vert^{\hat\alpha}\bm{sign}(\Delta \bm q)),\label{eq:Sr4}
+\bm S_{r4} &= \bm S_{q4}+\gamma\int^t_{t_0}\bm S_{q4}(\varsigma) \rm{d}\it{\varsigma}\\
+\bm S_{q4} &= \mathbf{Sine}(\Delta \dot {\bm q}+\alpha\xi\vert\Delta \bm q\vert^{\hat\alpha}\mathbf{sign}(\Delta \bm q)),\label{eq:Sr4}
 \end{split}
@@
 Meanwhile, the initial deployment velocity is about 3 $m/s$, and the subsatellite is going to be deployed at 3.5 $km$ vertically.
-\textcolor{red}{The pitch and roll dynamics are both varying in a small range, and hence, without loss of generality, the numerical initial conditions are designed as $\theta_0 = 0.1$, $\phi_0 = 0.1$ and $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$.
-Hence the dimensionless tether length is varying in the range of $[0.02,1]$.}\par
+The pitch and roll dynamics are both varying in a small range, and hence, without loss of generality, the numerical initial conditions are designed as $\theta_0 = 0.1$, $\phi_0 = 0.1$ and $\lambda_0 = 0.02$; the desired condition is set to be $\theta_d = 0$, $\phi_d = 0$ and $\lambda_d = 1$, accordingly, $\lambda(t_0)\rightarrow\lambda_d$, $t\rightarrow\infty$ with $\theta(t_0)\rightarrow\theta_d$, $\phi(t_0)\rightarrow\phi_d$, $t\rightarrow\infty$.
+Hence the dimensionless tether length is varying in the range of $[0.02,1]$.
+
 During the deployment, the dimensionless thruster forces which manage the in-plane angle and the out-of-plane angle are assumed to be saturated with $\vert\hat\tau_{\theta}\vert\le5 $ and $\vert\hat\tau_{\phi}\vert\le 5$.
@@
 At this point, the simulations of the deployment dynamics of the TSS can be carried on.
-\textcolor{red}{We firstly conduct the simulation about the pure deployment dynamics without any uncertainties to verify the effectiveness of the proposed control laws, and the results are illustrated in Figure~\ref{fig:3} to~\ref{fig:6}.
-Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that all the methods can realize the deployment in aspect of the tether length.} ST-SMC and QST-SMC complete the deployment at about 4 $rad$.
-\textcolor{red}{As shown in Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, indicating the curves of the tether length climb more rapidly at the beginning of the deployment.} However, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$.
+We firstly conduct the simulation about the pure deployment dynamics without any uncertainties to verify the effectiveness of the proposed control laws, and the results are illustrated in Figure~\ref{fig:3} to~\ref{fig:6}.
+Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that all the methods can realize the deployment in aspect of the tether length.
+ST-SMC and QST-SMC complete the deployment at about 4 $rad$.
+As shown in Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, indicating the curves of the tether length climb more rapidly at the beginning of the deployment.
+However, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$.
 This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to the origin earlier than S-SMC and QST-SMC.\par
-\textcolor{red}{The in-plane and out-of-plane angles reflect the swing dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}.} For ST-SMC, the in-plane dynamic motion is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time.
-\textcolor{red}{Hence the coalition of the length and the swing dynamics imply that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC.} S-SMC makes the tether swing to the desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
+The in-plane and out-of-plane angles reflect the swing dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}.
+For ST-SMC, the in-plane dynamic motion is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time.
+Hence the coalition of the length and the swing dynamics imply that the whole deployment mission is completed at about 4 $rad$ by utilizing ST-SMC.
+S-SMC makes the tether swing to the desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
 The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) are exhibited in Figure~\ref{fig:6}, in which it is obvious that the limited situations occur frequently.
@@
 \end{figure}
-\textcolor{red}{So far, the proposed control laws have been verified in the undisturbed environment.
+So far, the proposed control laws have been verified in the undisturbed environment.
 However, space perturbations and parametric uncertainties usually occur during the deployment of the TSS in engineering application.
@@
 In Fig~\ref{fig:6}, although the dynamics have already been  stable, the tension is switching in the high frequency.
-It is commonplace in the sliding mode control law design, called chattering, since the signum function is used in the input, which may cause unmodelled high frequency dynamics, and for reducing the chattering, we introduce the boundary layer technique into the proposed control laws through replacing $sign(x)$ by $sat(x/\nu)$, where
-\begin{align}
-sat(x/\nu)=
-\begin{cases}
-x,&\vert x\vert <\nu\\
-sign(x),&\vert x\vert\ge\nu
-\end{cases}
-\end{align}
-and $\nu$ is the thickness of the boundary layer specified as a positive scalar $\nu=1\times 10^{-4}$ in this simulation~\cite{1039802}.}\par
-\textcolor{red}{
+It is commonplace in the sliding mode control law design, called chattering, since the signum function is used in the input, which may cause unmodeled high frequency dynamics, and for reducing the chattering, we introduce the boundary layer technique into the proposed control laws with the thickness of the boundary layer specified as a positive scalar $\nu=1\times 10^{-4}$ in this simulation~\cite{1039802}.
+
 The simulation results of the deployment dynamics subjected to uncertainties are exhibited from Fig~\ref{fig:7} to Fig~\ref{fig:10}.
@@
 In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is reduced by utilizing the boundary layer technique.
-Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to parametric uncertainties and external disturbances.}
+Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to parametric uncertainties and external disturbances.
 \begin{figure}
@@
 \section{Acknowledgment}
-This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503101).
+This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61673009, 61503101, 91438202).
 \section{References}

### 2016-11-24 manuscript.tex
20161124

@@
 \section{Introduction}
-The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space explorations and scientific researches, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,huang2014optimal,Huang2016Impact,Huang201637,Huang2016}.
+The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space explorations and scientific researches, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,Huang2016Impact,Huang2016,Huang2016416,Huang2016171,Huang20161985}.
 Many international space research institutes have launched orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation schemes for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
@@
 $\alpha$ and $\gamma$ are control law parameters which will be discussed in the control law design.
-Define the tracking error as $\Delta \bm q=\bm q-\bm q_d$, in which $\bm q_d$ is the desired trajectory with $\bm q_d(t)\in C^2$.
+Define the system states error as $\Delta \bm q=\bm q-\bm q_d$, in which $\bm q_d$ is the desired trajectory with $\bm q_d(t)\in C^2$.
 However, the PID controller~(\ref{eq:pid controller}) can not be directly applied to the system~(\ref{eq:dynamic model 2}) with the input limitation, and in the subsequent section, we will utilize the saturated sliding mode technique to modify the controller~(\ref{eq:pid controller}) for the system~(\ref{eq:dynamic model 2}).
@@
 \bm S_{r1} &= \bm S_{q1}+\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\\
-\bm S_{q1} &= \mathbf{Sine}(\Delta \dot {\bm q}+\alpha\Delta\bm q),
+\bm S_{q1} &= \mathbf{Sine}(\Delta \dot {\bm q}+\alpha\Delta\bm q),\label{eq:sq1}
 \end{split}
@@
 \bm S_{r2} &= \bm S_{q2}+\bm{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma})\\
-\bm S_{q2} &= \Delta \dot {\bm q}+\alpha \Delta \bm q,
+\bm S_{q2} &= \Delta \dot {\bm q}+\alpha \Delta \bm q,\label{eq:sq2}
 \end{split}
@@
     \gamma_0\Vert\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert^{-1}&\Vert\int^t_{t_0}\bm S_{q1}(\varsigma) d\varsigma\Vert> 1,
-    \end{cases}
+  \end{cases}\label{eq:gamma}
     \end{align}
@@
 \end{myrem}
-In the aforementioned controller design, signum functions in inputs lead to chattering phenomena, which may cause adverse unmodeled dynamics to ruin the control system.
+\textcolor{red}{In the aforementioned controller design, signum functions in inputs lead to chattering phenomena, which may cause adverse unmodeled dynamics to ruin the control system.
 Herein, we adopt the boundary layer technique to reduce chattering through replacing $\rm{sign}\it{(x)}$ by $\rm{sat}\it{(x/\nu)}$, where
@@
 However, the cost of using boundary layer in sliding mode controller is that the asymptotic stability of proposed method can not be guaranteed, and we proceed to analyze the convergence precision in the following theorem.
-\begin{mythm}
-Considering the controller in Theorem~\ref{thm:1}, we replace $\mathbf{sign}{(\bm{x})}$ in Eq.~(\ref{eq:slider control}) by $\mathbf{sat}{(\boldsymbol {x/\nu})}$, where $\mathbf{sat}{(\boldsymbol{x}/\boldsymbol{\nu})}=\left(\rm{sat}\it{(x_1/\nu_1)},\rm{sat}\it{(x_2/\nu_2)},\cdots,\rm{sat}\it{(x_n/\nu_n)}\right)^T$, to remove the chattering caused by the signum function, and the modified controller can guarantee the precisions of system states $\Delta\bm q$ that satisfy
+\begin{mythm}\label{thm:boundary}
+Considering the controller in Theorem~\ref{thm:1}, we replace $\mathbf{sign}{(\bm{x})}$ in Eq.~(\ref{eq:slider control}) by $\mathbf{sat}{(\boldsymbol {x/\nu})}$, where $\mathbf{sat}{(\boldsymbol{x}/\boldsymbol{\nu})}=\left(\rm{sat}\it{(x_1/\nu_1)},\rm{sat}\it{(x_2/\nu_2)},\cdots,\rm{sat}\it{(x_n/\nu_n)}\right)^T$, to remove the chattering caused by the signum function, and the modified controller can guarantee that the system state error $\Delta\bm q$ is bounded on the boundary of the set $D_1^c$, which is the complement of $D_1$ defined as
 \begin{align}
-  \Vert\Delta\bm q\Vert\le\frac{\Vert\boldsymbol{arcsin}(\bm \nu)\Vert}{\alpha}.
+  D_1\triangleq\left\{\left(\Delta\bm q,\bar z,\gamma,\eta,\alpha\right)\Big\vert\Vert\Delta\bm q\Vert-\frac{\bar z}{\alpha\gamma\eta^2}\le 0\right\}.
 \end{align}
@@
 Since all the inputs are bounded, it is evident to assume that $\dot{\bm z}$ is bounded with $\Vert\dot{\bm z}\Vert\le \bar z\le 2\Vert\bm\nu\Vert/\rm{d}\it{t}$.
+$\eta$ is defined as a time dependent positive ratio $\eta$ that depicts the relation $\Vert\bm S_{q1}\Vert=\eta\Vert\bm S_{q2}\Vert$, for all $\Vert\bm S_{q1}\Vert\neq 0$, $0<\eta<1$, when $\Vert\bm S_{q1}\Vert= 0$, $\eta$ especially values as $\eta = 1$.
 \end{mythm}
@@
 \end{align}
-The selected Lyapunov function $V_3=\frac{1}{2}\bm{ S}_{q2}^T\bm{ S}_{q2}$ gives rise to
+Choosing Lyapunov function $V_3=\frac{1}{2}\bm{ S}_{q2}^T\bm{ S}_{q2}$, its time derivative is given by
 \begin{align}\begin{split}
@@
 &=-\frac{\gamma \bm S_{q2}^T\bm S_{q1}}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma\Vert^2}}}+\bm{ S}_{q2}^T\dot{\bm z}\\
-&\le -\frac{\gamma \Vert \bm S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma\Vert^2}}}+\Vert\dot{\bm{z}}\Vert(\Vert\bm z\Vert+\Vert\mathbf{arcsin}(\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma})\Vert)\\
-&\le -\frac{\gamma \Vert \bm S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma\Vert^2}}}+\bar z(\Vert\bm{\nu}\Vert+\pi/2)\\
+&\le -\frac{\gamma \Vert \bm S_{q1}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma\Vert^2}}}+\Vert\dot{\bm{z}}\Vert\Vert\bm{ S}_{q2}\Vert.\label{eq:v3}
 \end{split}\end{align}
-Based on the Lyapunove stability theory, the above expression implies that $\bm S_{q2} = \Delta \dot {\bm q}+\alpha \Delta \bm q=0$ can attract the system states under the condition
+Reviewing Eq.~(\ref{eq:sq1}) and Eq.~(\ref{eq:sq2}), we get
 \begin{align}
-  \Vert \bm S_{q1}\Vert\ge\sqrt{\frac{\bar z(\Vert\bm{\nu}\Vert+\pi/2)}{\gamma}}
-\end{align} Rephrasing that, the controller in Theorem~\ref{thm:1} with boundary layer technique can guarantee $\bm S_{q1}$ to converge to $\Vert\bm S_{q1}\Vert\le\sqrt{\frac{\bar z(\Vert\bm{\nu}\Vert+\pi/2)}{\gamma}}$, and once the states reach the boundary layer, since $\bm S_{q1}=\mathbf{Sine}(\Delta\dot{\bm q}+\alpha\Delta\bm q)$ we can combine
+\bm S_{q1}=\mathbf{Sine}(\bm S_{q2})=\mathbf{Sine}(\Delta\dot{\bm q}+\alpha\Delta\bm q)
+\end{align}
+and since $\Vert\bm S_{q1}\Vert=\eta\Vert\bm S_{q2}\Vert$, Eq.~(\ref{eq:v3}) can be rewritten as
 \begin{align}
-  \mathbf{Sine}(\Delta\dot{\bm q}+\alpha\Delta\bm q)=\bm\nu
+  \dot V_3\le -\frac{\gamma\eta^2 \Vert \bm S_{q2}\Vert^2}{\sqrt{1-\Vert\gamma\int^t_{t_0}\bm S_{q1}(\varsigma) \rm{d}\it{\varsigma\Vert^2}}}+\bar{z}\Vert\bm{ S}_{q2}\Vert
 \end{align}
-with the Lyapunov function $V_4=\frac{1}{2}\Delta\bm q^T\Delta\bm q$ to obtain
+Based on LaSalle theorem~\cite{lasalle1960some}, the above expression implies that $\bm S_{q2}$ can be attracted to the boundary of $D_2^c$, which is the complement of the set $D_2$ defined as
+\begin{align}
+  D_2\triangleq\left\{(\bm S_{q2},\bar z,\gamma,\eta)\Big\vert \frac{\bar z}{\gamma\eta^2}-\Vert \bm S_{q2}\Vert\ge 0\right\}
+\end{align}
+Rephrasing that, the controller in Theorem~\ref{thm:1} with boundary layer technique can drive $\bm S_{q2}$ to the boundary of $D_2^c$.
+Considering the situation that the system state error maintains on the boundary of $D_2^c$, we can accordingly analyze the ultimate precision of system state error $\Delta\bm q$ by
+\begin{align}
+&\Delta \dot {\bm q}+\alpha\Delta\bm q=\hat{\bm z}\\
+&\Vert\hat{\bm z}\Vert=\frac{\bar z}{\gamma\eta^2}.
+\end{align}
+Choosing the Lyapunov function $V_4=\frac{1}{2}\Delta\bm q^T\Delta\bm q$, its time derivative is given by
 \begin{align}\begin{split}
 \dot V_4 &= \Delta\bm q\Delta\dot{\bm q}\\
-&=\Delta\bm q^T(-\alpha\Delta\bm q+\boldsymbol{arcsin}(\bm \nu))\\
-&\le-\alpha\Vert\Delta\bm q\Vert^2+\Vert\Delta\bm q\Vert\Vert\boldsymbol{arcsin}(\bm \nu)\Vert\\
-&\le-(\alpha\Vert\Delta\bm q\Vert-\Vert\boldsymbol{arcsin}(\bm \nu)\Vert)\Vert\Delta\bm q\Vert,
+&=\Delta\bm q^T(-\alpha\Delta\bm q+\hat{\bm z})\\
+&\le-\alpha\Vert\Delta\bm q\Vert^2+\Vert\Delta\bm q\Vert\Vert\hat{\bm z}\Vert\\
+&\le-(\alpha\Vert\Delta\bm q\Vert-\Vert\hat{\bm z}\Vert)\Vert\Delta\bm q\Vert,
 \end{split}\end{align}
-which indicates that $\Vert\Delta\bm q\Vert=\frac{\Vert\boldsymbol{arcsin}(\bm \nu)\Vert}{\alpha}$ is an attractor, and hence, the ultimately system state precision of the controller with boundary layer technique is
-\begin{align}
-  \Vert\Delta\bm q\Vert\le\frac{\Vert\boldsymbol{arcsin}(\bm \nu)\Vert}{\alpha}.
-\end{align}
-This completes the proof.
+Hence, by LaSalle theorem~\cite{lasalle1960some}, it follows that $\Delta\bm q$ is bounded on the boundary of the set $D_1^c$, which is the complement of $D_1$. This completes the proof.
 \end{proof}
+}
+\begin{myrem}
+Particularly, in this work, the boundary layer is always attractive and is designed to be very thin.
+Moreover, by utilizing the proposed controller, the bounded inputs ensure that the dynamics in boundary layer are windless, which means that the change of $\bm z$ is not drastic and makes $\dot{\bm z}$ keep in a low level.
+We thus reasonably assume that $\bar z$ is a tiny positive scalar to ensure that $D_1$ is a small vicinity of origin.
+The proposed controller works to decrease the system state errors $\Delta\bm q$ and $\Delta\dot{\bm q}$, and this decreasing process tends to increasing $\eta$ contrarily.
+Hence, we can conclude that the system state error can maintain in a low level after reaching the boundary layer.
+\end{myrem}
 \subsection{Quasi-saturated terminal sliding mode control law subjected to input limitation}
@@
 In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is reduced by utilizing the boundary layer technique.
-Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to parametric uncertainties and external disturbances.
+\textcolor{red}{The control precisions in Figs~\ref{fig:7}-\ref{fig:9} are almost same to Figs~\ref{fig:3}-\ref{fig:6}, which means the loss of precision caused by the boundary layer technique is limited.
+Moreover, the simulation results show that the good performance of proposed controller and the suitable boundary layer thickness guarantee that the system state error converges to the small vicinity of origin, which is consistent with the analyses in Theorem~\ref{thm:boundary}.} Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to parametric uncertainties and external disturbances.
 \begin{figure}

### 2016-11-25 manuscript.tex
20161125

@@
 \textcolor{red}{In the aforementioned controller design, signum functions in inputs lead to chattering phenomena, which may cause adverse unmodeled dynamics to ruin the control system.
-Herein, we adopt the boundary layer technique to reduce chattering through replacing $\rm{sign}\it{(x)}$ by $\rm{sat}\it{(x/\nu)}$, where
+Herein, we adopt the boundary layer technique, which has been widely used in engineering applications~\cite{Hwang1996sliding,In2000Robust,Chen2005}, to reduce chattering through replacing $\rm{sign}\it{(x)}$ by $\rm{sat}\it{(x/\nu)}$, where
 \begin{align}
@@
 and $\nu$ is the boundary layer thickness.
-However, the cost of using boundary layer in sliding mode controller is that the asymptotic stability of proposed method can not be guaranteed, and we proceed to analyze the convergence precision in the following theorem.
+However, the cost of using boundary layer in sliding mode controller is that the asymptotic stability of proposed method can not be guaranteed.
+Hence we proceed to analyze the bounded stability in the following theorem.
 \begin{mythm}\label{thm:boundary}
@@
 \end{align}
-$\bm z$ is the position vector that describes the distances of system states in the boundary layer from the sliding mode surface, and $\dot{\bm z}$ is the velocity vector correspondingly.
+$\bm z$ is the position vector that describes the distances of system states in the boundary layer from $\bm S_{r2}=0$, and $\dot{\bm z}$ is the velocity vector correspondingly.
 It is obvious that $\bm z$ is bounded and has $\Vert\bm z\Vert\le\Vert\bm\nu\Vert$, where $\bm\nu=(\nu_1,\nu_2,\nu_3)^T,\nu_1=\nu_2=\nu_3\ll 1$ is a constant vector denoting the boundary layer thicknesses for the three channels.
-Since all the inputs are bounded, it is evident to assume that $\dot{\bm z}$ is bounded with $\Vert\dot{\bm z}\Vert\le \bar z\le 2\Vert\bm\nu\Vert/\rm{d}\it{t}$.
-$\eta$ is defined as a time dependent positive ratio $\eta$ that depicts the relation $\Vert\bm S_{q1}\Vert=\eta\Vert\bm S_{q2}\Vert$, for all $\Vert\bm S_{q1}\Vert\neq 0$, $0<\eta<1$, when $\Vert\bm S_{q1}\Vert= 0$, $\eta$ especially values as $\eta = 1$.
+Since all the inputs are bounded, it is reasonable to assume that $\dot{\bm z}$ is bounded with $\Vert\dot{\bm z}\Vert\le \bar z$.
+$\eta$ is defined as a state dependent positive parameter that depicts the relation $\Vert\bm S_{q1}\Vert=\eta\Vert\bm S_{q2}\Vert$, for all $\Vert\bm S_{q1}\Vert\neq 0$, $0<\eta<1$, when $\Vert\bm S_{q1}\Vert= 0$, $\eta$ especially values as $\eta = 1$.
 \end{mythm}
 \begin{proof}
-Referring to the derivation in Theorem~\ref{thm:1}, we can guarantee the system states reach and enter the boundary layer $\Vert\bm{ S}_{r2}\Vert \le \Vert\bm\nu\Vert$ such that
+Referring to the derivation (\ref{eq:sq2})-(\ref{eq:V1_2}) in Theorem~\ref{thm:1}, we can guarantee that the system states reach and enter the boundary layer $\Vert\bm{ S}_{r2}\Vert \le \Vert\bm\nu\Vert$ such that
 \begin{align}
@@
 Rephrasing that, the controller in Theorem~\ref{thm:1} with boundary layer technique can drive $\bm S_{q2}$ to the boundary of $D_2^c$.
-Considering the situation that the system state error maintains on the boundary of $D_2^c$, we can accordingly analyze the ultimate precision of system state error $\Delta\bm q$ by
+Considering the situation that the system state error reaches the boundary of $D_2^c$, we can accordingly analyze the ultimate precision of system state error $\Delta\bm q$ by
 \begin{align}
@@
 \end{proof}
-}
 \begin{myrem}
@@
 We thus reasonably assume that $\bar z$ is a tiny positive scalar to ensure that $D_1$ is a small vicinity of origin.
-The proposed controller works to decrease the system state errors $\Delta\bm q$ and $\Delta\dot{\bm q}$, and this decreasing process tends to increasing $\eta$ contrarily.
-Hence, we can conclude that the system state error can maintain in a low level after reaching the boundary layer.
+The proposed controller works to decrease the system state errors $\Delta\bm q$ and $\Delta\dot{\bm q}$, and this decreasing process tends to increase $\eta$ contrarily.
+Hence, we can conclude that the system state error can keep in a low level after reaching the boundary layer.
 \end{myrem}
+}
 \subsection{Quasi-saturated terminal sliding mode control law subjected to input limitation}

### 2016-11-26 manuscript.tex
20161126

@@
 \textcolor{red}{In the aforementioned controller design, signum functions in inputs lead to chattering phenomena, which may cause adverse unmodeled dynamics to ruin the control system.
-Herein, we adopt the boundary layer technique, which has been widely used in engineering applications~\cite{Hwang1996sliding,In2000Robust,Chen2005}, to reduce chattering through replacing $\rm{sign}\it{(x)}$ by $\rm{sat}\it{(x/\nu)}$, where
+Herein, we adopt the boundary layer technique, which has been widely used in engineering applications~\cite{Youndg1999A,Hwang1996sliding,In2000Robust,Chen2005,Yu2009sliding,Jin2009Practical,Al2004sliding}, to reduce chattering through replacing $\rm{sign}\it{(x)}$ by $\rm{sat}\it{(x/\nu)}$, where
 \begin{align}
@@
 \end{align}
-and $\nu$ is the boundary layer thickness.
+and $2\nu$ is the boundary layer thickness.
 However, the cost of using boundary layer in sliding mode controller is that the asymptotic stability of proposed method can not be guaranteed.
@@
 $\bm z$ is the position vector that describes the distances of system states in the boundary layer from $\bm S_{r2}=0$, and $\dot{\bm z}$ is the velocity vector correspondingly.
-It is obvious that $\bm z$ is bounded and has $\Vert\bm z\Vert\le\Vert\bm\nu\Vert$, where $\bm\nu=(\nu_1,\nu_2,\nu_3)^T,\nu_1=\nu_2=\nu_3\ll 1$ is a constant vector denoting the boundary layer thicknesses for the three channels.
+It is obvious that $\bm z$ is bounded and has $\Vert\bm z\Vert\le\Vert\bm\nu\Vert$, where $\bm\nu$ is a constant vector denoting the boundary layer thicknesses.
 Since all the inputs are bounded, it is reasonable to assume that $\dot{\bm z}$ is bounded with $\Vert\dot{\bm z}\Vert\le \bar z$.

### 2016-12-02 manuscript.tex
20161202

@@
 &\bar m l^2\cos^2\phi\theta''+2\bar m (\theta'+\Omega)l^2\cos^2\phi(l'/l-\phi'\tan\phi)+3\bar m \Omega^2l^2\sin\theta\cos\theta\cos^2\phi=\tau_\theta+\tau_{\theta d}\\
-&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\left[(\theta'+\Omega)^2+3\bar m \Omega\cos^2\theta\right]=\tau_\phi+\tau_{\phi d},\label{eq:dynamics 1}
+&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\left[(\theta'+\Omega)^2+3\bar m \Omega^2\cos^2\theta\right]=\tau_\phi+\tau_{\phi d},\label{eq:dynamics 1}
 \end{split}
@@
 C(\bm q,\dot{\bm q}) &=\begin{bmatrix}0 &-(\lambda\dot \theta+2\lambda)\cos^2\phi&-\lambda\dot\phi\\(2\lambda+\lambda\dot \theta)\cos^2\phi&\lambda\dot \lambda\cos^2\phi-\lambda^2\dot\phi\sin\phi\cos\phi&-(\dot\theta+2)\lambda^2\sin\phi\cos\phi\\ \lambda\dot\phi&\lambda^2(\dot\theta+2)\sin\phi\cos\phi&\lambda\dot \lambda\end{bmatrix}\\
-G(\bm q) &=\begin{bmatrix}-\lambda\cos^2\phi+2\lambda+3\lambda\cos ^2\theta\cos^2\phi\\3\lambda^2\cos\theta\sin\theta\cos^2\phi\\\lambda^2+3\lambda^2\cos^2\theta\sin\phi\cos\phi\end{bmatrix}.
+G(\bm q) &=\begin{bmatrix}-\lambda\cos^2\phi+2\lambda+3\lambda\cos ^2\theta\cos^2\phi\\3\lambda^2\cos\theta\sin\theta\cos^2\phi\\(1+3\cos^2\theta)\lambda^2\sin\phi\cos\phi\end{bmatrix}.
 \end{split}

### 2016-12-30 manuscript.tex
20161230

@@
 Owing to the tiny mass ratio between the satellites, the deployment of the subsatellite will not affect the motion of the mother satellite during the whole mission.
-The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.\par
+The deployment is regulated by the tension and thrusters, and to guarantee the establishment of the ``rolling ball'' model, the tether remains inextensible, straight and stiff all the time.
+\textcolor{red}{Moreover, for enhancing the control performance of in-plane and out-of-plane dynamics, the thrusters are equipped on the subsatellite to generate thruster forces along the tangent directions of the circle generated by in-plane and out-of-plane angles swing, respectively~\cite{liu2014attitude}}.\par
 Symbols used in the model are defined as follows.
@@
 &\bar m l^2\cos^2\phi\theta''+2\bar m (\theta'+\Omega)l^2\cos^2\phi(l'/l-\phi'\tan\phi)+3\bar m \Omega^2l^2\sin\theta\cos\theta\cos^2\phi=\tau_\theta+\tau_{\theta d}\\
-&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\left[(\theta'+\Omega)^2+3\bar m \Omega^2\cos^2\theta\right]=\tau_\phi+\tau_{\phi d},\label{eq:dynamics 1}
+&\bar m l^2\phi''+2\bar m \phi'l'l+\bar m l^2\sin\phi\cos\phi\left[(\theta'+\Omega)^2+3 \Omega^2\cos^2\theta\right]=\tau_\phi+\tau_{\phi d},\label{eq:dynamics 1}
 \end{split}
@@
 For clarity, $m_1m_2/m$ is rewritten as $\bar m$.
-$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster force and the out-of-plane thruster force, respectively.
-$\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.
+\textcolor{red}{$\tau_t$, $\tau_\theta$ and $\tau_\phi$ are the tension, the in-plane thruster torque and the out-of-plane thruster torque, respectively.} $\tau_{t d}$, $\tau_{\theta d}$ and $\tau_{\phi d}$ stand for the bounded external disturbances correspondingly.
 Typically, the dimensionless transformations simplify issues for researchers to design the deployment scheme, and the conventional transformations are represented as shown below~\cite{williams2009yes2,wen2015space,wen2016constrained}:
@@
 C(\bm q,\dot{\bm q}) &=\begin{bmatrix}0 &-(\lambda\dot \theta+2\lambda)\cos^2\phi&-\lambda\dot\phi\\(2\lambda+\lambda\dot \theta)\cos^2\phi&\lambda\dot \lambda\cos^2\phi-\lambda^2\dot\phi\sin\phi\cos\phi&-(\dot\theta+2)\lambda^2\sin\phi\cos\phi\\ \lambda\dot\phi&\lambda^2(\dot\theta+2)\sin\phi\cos\phi&\lambda\dot \lambda\end{bmatrix}\\
-G(\bm q) &=\begin{bmatrix}-\lambda\cos^2\phi+2\lambda+3\lambda\cos ^2\theta\cos^2\phi\\3\lambda^2\cos\theta\sin\theta\cos^2\phi\\(1+3\cos^2\theta)\lambda^2\sin\phi\cos\phi\end{bmatrix}.
+G(\bm q) &=\begin{bmatrix}-\lambda\cos^2\phi+2\lambda-3\lambda\cos ^2\theta\cos^2\phi\\3\lambda^2\cos\theta\sin\theta\cos^2\phi\\(1+3\cos^2\theta)\lambda^2\sin\phi\cos\phi\end{bmatrix}.
 \end{split}
@@
 \begin{myas}
-In low-altitude orbit , the external disturbance $\bm\tau_d$ contains the gravity gradient torque, the aerodynamic interference and the solar radiation pressure torque.
-Thanks to existing studies, the values of the solar radiation pressure and the aerodynamic torque are about $1\times10^{-5}$ Nm, and meanwhile the gradient torque is in the range of $1\times10^{-5}$ Nm.
-The space perturbation can be specifically regarded as the periodic function in this paper, and the period equals the orbital period $5000$ s~\cite{Inamori2015192}.
-Hence, the external disturbance can be described by the following expression
+\textcolor{red}{In low-altitude orbit , the external disturbance $\bm\tau_d$ contains the gravity gradient torque, the aerodynamic interference and the solar radiation pressure torque.
+Thanks to existing studies, the magnitudes of the solar radiation pressure, the aerodynamic torque and the gradient torque are in the range of $1\times10^{-5}$.
+The space perturbation can be specifically regarded as the periodic function in this paper, and the period equals the orbital period $T_o$ that can be calculated by~\cite{Inamori2015192}
+\begin{align}\begin{split}
+  T_o &= 2\pi/\Omega\\
+  \Omega &= \sqrt{\mu_e/R_0^3}\notag
+\end{split}\end{align}
+where $\mu_e=3.986\times 10^{14}m^3/s^2$.
+$R_0$ is related to the orbital altitude and the earth's radius, and in this work, we assume that the tethered satellite system orbits at $260km$ such that $R_0=6.631\times 10^6m$.
+Using dimensionless transformations~(\ref{eq:varcon}) with $L=3.5km$, the dimensionless disturbance can be described by
 \begin{align}
-\bm\tau_d=\left(0.05\sin(2\pi t/5000),0.05\sin(2\pi t/5000),0.05\sin(2\pi t/5000)\right)^T.
+\bm\tau_d=\left[1.745\times 10^{-4}\sin(\it{v}),\rm 4.985\times \rm 10^{-8}\sin(\it{v}), \rm 4.985\times 10^{-8}\sin(\it{v})\right]^T.
 \end{align}
+However, the magnitude of the disturbance is too little to examine the controller performance, hence we intentionally heighten the amplitude in the above expression to obtain the following disturbance formulation, which may express some severe uncertainties or disturbance.
+\begin{align}
+\bm\tau_d=\left[5\times 10^{-2}\sin(\it{v}),\rm 5\times \rm 10^{-2}\sin(\it{v}), \rm 5\times 10^{-2}\sin(\it{v})\right]^T.\notag
+\end{align}
+where $\it v$ is the dimensionless time.
 Therefore, the bounded external disturbance satisfies
@@
 \end{align}
-where $\varphi_1$ can be selected as a positive scalar $\varphi_1=1$.
+where $\varphi_1$ can be selected as a positive scalar $\varphi_1=1$.}
 \end{myas}
@@
 \end{myrem}
-\textcolor{red}{In the aforementioned controller design, signum functions in inputs lead to chattering phenomena, which may cause adverse unmodeled dynamics to ruin the control system.
+In the aforementioned controller design, signum functions in inputs lead to chattering phenomena, which may cause adverse unmodeled dynamics to ruin the control system.
 Herein, we adopt the boundary layer technique, which has been widely used in engineering applications~\cite{Youndg1999A,Hwang1996sliding,In2000Robust,Chen2005,Yu2009sliding,Jin2009Practical,Al2004sliding}, to reduce chattering through replacing $\rm{sign}\it{(x)}$ by $\rm{sat}\it{(x/\nu)}$, where
@@
 \end{myrem}
-}
 \subsection{Quasi-saturated terminal sliding mode control law subjected to input limitation}
@@
 $\varpi$ is the uncertainty boundary parameter, and here we select $\varpi=2$.
-$\bm\tau_d$ is the external disturbance meaning  space perturbations, such as gravity gradient torque, aerodynamic interference and solar radiation pressure torque.
+$\bm\tau_d$ is the external disturbance meaning  space perturbations, such as gravity gradient effect, aerodynamic interference and solar radiation pressure torque.
 In this simulation, the measured terms can be specified as: $\hat{\bar m}=1.1\bar m$ may mean some space debris affixed to the subsatellite; $\bar L=1.02L$ and $\bar \Omega=0.98\Omega$ mean some measurement errors happening to the total length and the orbital angular velocity.
@@
 In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is reduced by utilizing the boundary layer technique.
-\textcolor{red}{The control precisions in Figs~\ref{fig:7}-\ref{fig:9} are almost same to Figs~\ref{fig:3}-\ref{fig:6}, which means the loss of precision caused by the boundary layer technique is limited.
-Moreover, the simulation results show that the good performance of proposed controller and the suitable boundary layer thickness guarantee that the system state error converges to the small vicinity of origin, which is consistent with the analyses in Theorem~\ref{thm:boundary}.} Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to parametric uncertainties and external disturbances.
+\textcolor{red}{Fig.~\ref{fig:11} shows the in-plane and out-of-plane thruster forces.
+From the results, we can find that all the forces are reasonable and limited in the boundary, and have less chattering by using the boundary layer technique.
+The in-plane thruster force has the similar results like the tension, the chattering of which is almost eliminated in the final stage.
+The boundary layer doesn't work well on the out-of-plane thruster force, and it is easy to see that the crossing boundary layer happens a lot, which may be caused by the external disturbance and uncertainties.
+However the technique still represses the chattering to some extents.
+Hence we can say that the boundary layer technique can indeed improve the inputs and repress the chattering.} The control precisions in Figs~\ref{fig:7}-\ref{fig:9} are almost same to Figs~\ref{fig:3}-\ref{fig:6}, which means the loss of precision caused by the boundary layer technique is limited.
+Moreover, the simulation results show that the good performance of proposed controller and the suitable boundary layer thickness guarantee that the system state error converges to the small vicinity of origin, which is consistent with the analyses in Theorem~\ref{thm:boundary}.
+Hence, the robustness of the proposed control laws can guarantee the stability of the deployment subjected to parametric uncertainties and external disturbances.
 \begin{figure}
@@
 \end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{paper4_response_20161230.eps}
+\caption{Thruster force}
+\label{fig:11}
+\end{figure}
 \section{Conclusion}\label{sec:5}

### 2016-12-31 manuscript.tex
20161231

@@
 \section{Introduction}
-The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space explorations and scientific researches, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,Huang2016Impact,Huang2016,Huang2016416,Huang2016171,Huang20161985}.
+The deployment is the key technology of the space tethered satellite system (TSS)~\cite{wen2008advances,yousefian2015anti}, which supports various applications for space explorations and scientific researches, such as space debris removals, space elevators, satellite de-orbits and the tethered space robots~\cite{zhao2014thrust,kojima2015mission,zhong2013dynamics,zhong2013long,Huang2016Impact,Huang2016,Huang2016416}, and involves control theory, communication science and mechanical science~\cite{Li2014,Huang2016171,Huang20161985}.
 Many international space research institutes have launched orbital, suborbital and ground experiments, such as TSS-1R, SEDS, MAST and YES2, in an effort to verify the feasibility of the proposed theoretical and simulation schemes for the deployment of the TSS~\cite{williams2012review,robitaille2006interpreting,stone1998tss,williams2009yes2}.
@@
 \begin{align}
-\frac{\rm{d}}{\rm{d}\it{t}}F(t) = \delta\varphi \bm S_{r2}^T K_1\rm{e}\it{^{-2K_1^{-1}F^{-1}(t)}}\mathbf{sign}(\bm S_{r2})
+\frac{\rm{d}}{\rm{d}\it{t}}F(t) = \delta\varphi \bm S_{r2}^T K_1\rm{e}\it{^{-2K_1^{-1}F^{-1}(t)}}\mathbf{sign}(\bm {S}_{r2})
 \end{align}
@@
 From the results, we can find that all the forces are reasonable and limited in the boundary, and have less chattering by using the boundary layer technique.
-The in-plane thruster force has the similar results like the tension, the chattering of which is almost eliminated in the final stage.
-The boundary layer doesn't work well on the out-of-plane thruster force, and it is easy to see that the crossing boundary layer happens a lot, which may be caused by the external disturbance and uncertainties.
-However the technique still represses the chattering to some extents.
+The thruster forces have the similar behaviors like the tension, and the chattering is almost eliminated in the final stage.
 Hence we can say that the boundary layer technique can indeed improve the inputs and repress the chattering.} The control precisions in Figs~\ref{fig:7}-\ref{fig:9} are almost same to Figs~\ref{fig:3}-\ref{fig:6}, which means the loss of precision caused by the boundary layer technique is limited.

### 2016-12-31 manuscript.tex
20161231

@@
 
-Recent scientific researches about deployments of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{kojima2015stabilisation,qi2016dynamics,zhong2016research}.
+Recent scientific researches about deployments of the TSS focus on the stabilization of the dynamics, and have provided different kinds of control schemes, including tension, thruster, electrodynamic and Coulomb approaches~\cite{zhu2008,kojima2015stabilisation,qi2016dynamics,zhong2016research,sun2013}.
 Among these stabilization strategies, the hybrid tension and thruster control technique has been a great boost to new developments of the deployment of the TSS.

### 2017-01-01 manuscript.tex
20170101

@@
 \section{Mathematical model}\label{sec:2}
-Figure \ref{fig:1} shows all the elements of the TSS via the geometric representation.
+Fig~\ref{fig:1} shows all the elements of the TSS via the geometric representation.
 In the figure, the axes of the coordinate frame $OXYZ$ passes through the center of the earth $O$.
@@
 and it's notable that the function above is saturated and owns an important property: $\vert \rm{Sine}\it{(x)}\vert\le\vert x\vert$, $\forall x$.
-The geometric illustration is shown in Figure~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=\rm{Sine}(\it{x})$ along the axis $x=0$ in the range $[-1,1]$, and once the function $y=\rm{Sine}\it{(x)}+\Delta h$ with $\vert\Delta h\vert<1$ settles, one can choose the function $y = x+\arcsin(\Delta h)$ to obtain following relations:
+The geometric illustration is shown in Fig~\ref{fig:2}, from which an interesting property can be found by sliding the curve $y=\rm{Sine}(\it{x})$ along the axis $x=0$ in the range $[-1,1]$, and once the function $y=\rm{Sine}\it{(x)}+\Delta h$ with $\vert\Delta h\vert<1$ settles, one can choose the function $y = x+\arcsin(\Delta h)$ to obtain following relations:
 \begin{align}
@@
 \end{align}
-Based on the expression above, one can obtain $\bar{m}\Omega^2L\approx 4.79\times 10^{-3}$, and suitable boundary values $\hat\tau_{tmin}$ and $\hat\tau_{tmax}$ can be chosen to make the dimensionless tension $\hat\tau_t$ fall in the region $[-3,0.01]$.\par
+Based on the expression above, one can obtain $\bar{m}\Omega^2L\approx 0.0573N$, and suitable boundary values $\hat\tau_{tmin}$ and $\hat\tau_{tmax}$ can be chosen to make the dimensionless tension $\hat\tau_t$ fall in the region $[-3,0.01]$.\par
 At this point, the simulations of the deployment dynamics of the TSS can be carried on.
-We firstly conduct the simulation about the pure deployment dynamics without any uncertainties to verify the effectiveness of the proposed control laws, and the results are illustrated in Figure~\ref{fig:3} to~\ref{fig:6}.
-Figure~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that all the methods can realize the deployment in aspect of the tether length.
+We firstly conduct the simulation about the pure deployment dynamics without any uncertainties to verify the effectiveness of the proposed control laws, and the results are illustrated in Fig~\ref{fig:3} to~\ref{fig:6}.
+Fig~\ref{fig:3} shows the dynamics of the length in different control laws, and it is obvious that all the methods can realize the deployment in aspect of the tether length.
 ST-SMC and QST-SMC complete the deployment at about 4 $rad$.
-As shown in Figure~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, indicating the curves of the tether length climb more rapidly at the beginning of the deployment.
+As shown in Fig~\ref{fig:4}, S-SMC and QST-SMC have bigger length rate than ST-SMC before 1.2 $rad$, indicating the curves of the tether length climb more rapidly at the beginning of the deployment.
 However, the length rate of ST-SMC doesn't decline dramatically like the other two methods after 1.2 $rad$.
-This slowly varying length rate yields a smooth trajectory of the deployment shown in Figure~\ref{fig:3}, and meanwhile the length rate converges to the origin earlier than S-SMC and QST-SMC.\par
-The in-plane and out-of-plane angles reflect the swing dynamics of the tether during the deployment, the details of which are drawn in Figue~\ref{fig:5}.
+This slowly varying length rate yields a smooth trajectory of the deployment shown in Fig~\ref{fig:3}, and meanwhile the length rate converges to the origin earlier than S-SMC and QST-SMC.\par
+The in-plane and out-of-plane angles reflect the swing dynamics of the tether during the deployment, the details of which are drawn in Fig~\ref{fig:5}.
 For ST-SMC, the in-plane dynamic motion is regulated to vertical status at 4 $rad$, and the in-plane angle converges to the origin in the subsequent time.
@@
 S-SMC makes the tether swing to the desired position at a low convergent speed near the vertical direction during 2 $rad$ to 4 $rad$.\par
-The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) are exhibited in Figure~\ref{fig:6}, in which it is obvious that the limited situations occur frequently.
-Thanks to the scalable dimensionless transformation determined conservatively, the tension exerted on the tether falls in the reasonable region.\par
+The inputs in S-SMC for dynamic model~(\ref{eq:dynamic model}) are exhibited in Fig~\ref{fig:6}, in which it is obvious that the limited situations occur frequently.
+Thanks to the scalable dimensionless transformation determined conservatively, the tension exerted on the tether falls in the reasonable region.
+In addition, combining with the results in Figs~\ref{fig:3}-\ref{fig:6},\ref{fig:11}, the system sates converge to desired values as the inputs are frequently switching, implying that the dynamic stability can be guaranteed by the proposed approach.\par
 \begin{figure}
@@
 \frac{1}{\varpi}&\le\frac{\hat \Omega}{\Omega}\le \varpi\\
-\bm\tau_d&=\left(0.05\sin(2\pi t/5000),0.05\sin(2\pi t/5000),0.05\sin(2\pi t/5000)\right)^T,
+\bm\tau_d&=\left[5\times 10^{-2}\sin(\it{v}),\rm 5\times \rm 10^{-2}\sin(\it{v}), \rm 5\times 10^{-2}\sin(\it{v})\right]^T,
 \end{split}\end{align}
@@
 In Fig~\ref{fig:6}, although the dynamics have already been  stable, the tension is switching in the high frequency.
-It is commonplace in the sliding mode control law design, called chattering, since the signum function is used in the input, which may cause unmodeled high frequency dynamics, and for reducing the chattering, we introduce the boundary layer technique into the proposed control laws with the thickness of the boundary layer specified as a positive scalar $\nu=1\times 10^{-4}$ in this simulation~\cite{1039802}.
+It is commonplace in the sliding mode control law design, called chattering, since the signum function is used in the input, which may cause unmodeled high frequency dynamics, and for reducing the chattering, we introduce the boundary layer technique into the proposed control laws with the thickness of the boundary layer specified as a positive scalar $\nu=2.5\times 10^{-3}$ in this simulation~\cite{1039802}.
 
@@
 In addition, the result in Fig~\ref{fig:10} shows that the tension falls in the reasonable region, and meanwhile the chattering of the input in the stable status is reduced by utilizing the boundary layer technique.
-\textcolor{red}{Fig.~\ref{fig:11} shows the in-plane and out-of-plane thruster forces.
+The boundary layer works at about 6 rad as the error enters the specified boundary.
+Moreover, compared with the results in Fig~\ref{fig:6}, it is evident that the final value of the tension is consistent with the result of article~\cite{Ma201667}, since the discontinuous switching input is replaced by continuous input by the means of boundary layer.
+\textcolor{red}{Fig~\ref{fig:11} shows the in-plane and out-of-plane dimensionless thruster forces.
 From the results, we can find that all the forces are reasonable and limited in the boundary, and have less chattering by using the boundary layer technique.
@@
 \includegraphics[width=0.6\textwidth]{paper4_response_20161230.eps}
-\caption{Thruster force}
+\caption{Dimensionless thruster force}
 \label{fig:11}
